---
title: "calculateCV_saliva"
author: "Nandi"
date: "25 September 2018"
output: html_document
---

```{r, include=FALSE}
#LOAD PACKAGES AND SET DIRECTORIES

packages <- c("ggplot2","tidyr","stringr","knitr","corrplot","data.table","readxl","gridExtra","dplyr", "psych","kableExtra","lavaan","xlsx","DescTools")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}
lapply(packages, library, character.only = TRUE)

cas_dir <- 'Z:/dsnlab/TAG/'
saliva_dir <- paste0(cas_dir,'behavior/Puberty/Saliva/Wave1')
options(digits=3)
```

###IMPORT TAG OVERVIEW DOC FROM CAS
```{r, include = F}
#import "overview" document so that we can filter analyses to subjects that were not excluded

overview <- read.xlsx(paste0(cas_dir,'behavior/Overview/Overview_Withdrawn_Completed/TAG_Overview_Doc.xlsx'),1)
overview <- overview[,c("TAG_ID","W1S2_Completed","Withdrawn_W1","Exclusionary_Withdrawl")]

#removing everyone who withdrew at W1 (exclusionary withdrawals & Withdrawn_W1)
overview <- overview %>% 
  rename(SID = TAG_ID) %>%
  replace_na(list(Withdrawn_W1 = 0)) %>%
  replace_na(list(Exclusionary_Withdrawl = 0)) %>% 
  arrange(Exclusionary_Withdrawl) %>% 
  mutate(SID=gsub("[^0-9\\.]", "", SID)) %>%
  filter(Exclusionary_Withdrawl==0) %>%
  filter(Withdrawn_W1==0)
```

###CALCULATE INTRA-ASSAY CVS. Note (MLB) - these are the variation between the indvidual duplicate samples. Concentration and optical density CVs are calculated here but we use and report OD CVs.
```{r}

#batch 1
#import files
Saliva_DHEA_CV_1 <- read_xlsx(paste0(saliva_dir,'/Raw_conc/TAG_SALIVA_Master_File.xlsx'), sheet=1)
Saliva_TEST_CV_1 <- read_xlsx(paste0(saliva_dir,'/Raw_conc/TAG_SALIVA_Master_File.xlsx'), sheet=5)
Saliva_EST_CV_1 <- read_xlsx(paste0(saliva_dir,'/Raw_conc/TAG_SALIVA_Master_File.xlsx'), sheet=9)

#clean and calculate intra-assay CV for concentrations and optical densities
Saliva_DHEA_CV_1 <- Saliva_DHEA_CV_1 %>%
  rename(WellID = `Well ID`,
         ID = Name,
         Conc = `[Concentration]`,
         OD = `450`) %>%
  filter(!(WellID=="SPL37" & ID=="28.1")) %>%
  filter(!(WellID=="SPL38" & ID=="28.2")) %>%
  mutate(Conc = as.numeric(Conc),
         OD = as.numeric(OD),
         Conc_2 = lead(Conc),
         OD_2 = lead(OD)) %>% 
  select(ID,Conc,Conc_2,OD,OD_2) %>%
  filter(!is.na(ID)) %>%
  rowwise() %>%
  mutate(Conc_mean = mean(c(Conc,Conc_2),na.rm=T),
         Conc_sd = sd(c(Conc,Conc_2),na.rm=T),
         OD_mean = mean(c(OD,OD_2),na.rm=T),
         OD_sd = sd(c(OD,OD_2),na.rm=T)) %>%
  mutate(DHEA_Conc_CV = 100*(Conc_sd/Conc_mean),
         DHEA_Conc_CV = round(as.numeric(DHEA_Conc_CV),3),
         DHEA_OD_CV = 100*(OD_sd/OD_mean),
         DHEA_OD_CV = round(as.numeric(DHEA_OD_CV),3),
         SID = as.factor(round(as.numeric(ID),2))) %>%
  select(SID,DHEA_Conc_CV,DHEA_OD_CV) %>%
  filter(!is.na(SID)) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID)) %>%
  arrange(SID) 

Saliva_TEST_CV_1 <- Saliva_TEST_CV_1 %>% 
  rename(WellID = `Well ID`,
         ID = Name,
         Conc = `[Concentration]`,
         OD = `450`) %>%
  filter(!(WellID=="SPL20" & ID=="44.1")) %>%
  mutate(Conc = as.numeric(Conc),
         OD = as.numeric(OD),
         Conc_2 = lead(Conc),
         OD_2 = lead(OD)) %>% 
  select(ID,Conc,Conc_2,OD,OD_2) %>%
  filter(!is.na(ID)) %>%
  rowwise() %>%
  mutate(Conc_mean = mean(c(Conc,Conc_2),na.rm=T),
         Conc_sd = sd(c(Conc,Conc_2),na.rm=T),
         OD_mean = mean(c(OD,OD_2),na.rm=T),
         OD_sd = sd(c(OD,OD_2),na.rm=T)) %>%
  mutate(TEST_Conc_CV = 100*(Conc_sd/Conc_mean),
         TEST_Conc_CV = round(as.numeric(TEST_Conc_CV),3),
         TEST_OD_CV = 100*(OD_sd/OD_mean),
         TEST_OD_CV = round(as.numeric(TEST_OD_CV),3),
         SID = as.factor(round(as.numeric(ID),2))) %>%
  select(SID,TEST_Conc_CV,TEST_OD_CV) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID)) %>%
  filter(!is.na(SID)) %>%
  arrange(SID) 

Saliva_EST_CV_1 <- Saliva_EST_CV_1 %>% 
  rename(ID = Name,
         Conc = `[Concentration]`,
         OD = `450`) %>%
  mutate(Conc = as.numeric(Conc),
         OD = as.numeric(OD),
         Conc_2 = lead(Conc),
         OD_2 = lead(OD)) %>% 
  select(ID,Conc,Conc_2,OD,OD_2) %>%
  filter(!is.na(ID)) %>%
  rowwise() %>%
  mutate(Conc_mean = mean(c(Conc,Conc_2),na.rm=T),
         Conc_sd = sd(c(Conc,Conc_2),na.rm=T),
         OD_mean = mean(c(OD,OD_2),na.rm=T),
         OD_sd = sd(c(OD,OD_2),na.rm=T)) %>%
  mutate(EST_Conc_CV = 100*(Conc_sd/Conc_mean),
         EST_Conc_CV = round(as.numeric(EST_Conc_CV),3),
         EST_OD_CV = 100*(OD_sd/OD_mean),
         EST_OD_CV = round(as.numeric(EST_OD_CV),3),
         SID = as.factor(round(as.numeric(ID),2))) %>%
  select(SID,EST_Conc_CV,EST_OD_CV) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID)) %>%
  filter(!is.na(SID)) %>%
  arrange(SID) 

#batch 2
#import files
Saliva_DHEA_CV_2 <- read_xlsx(paste0(saliva_dir,'/Raw_conc/TAG_MasterSheet_Saliva_2ndRun.xlsx'), sheet=5)
Saliva_TEST_CV_2 <- read_xlsx(paste0(saliva_dir,'/Raw_conc/TAG_MasterSheet_Saliva_2ndRun.xlsx'), sheet=3)
Saliva_EST_CV_2 <- read_xlsx(paste0(saliva_dir,'/Raw_conc/TAG_MasterSheet_Saliva_2ndRun.xlsx'), sheet=1)

#clean and calculate interassay CV for concentrations and optical densities
Saliva_DHEA_CV_2 <- Saliva_DHEA_CV_2 %>%
  rename(ID = Name,
         Conc = `[Concentration]`,
         OD = `450`) %>%
  filter(!(rerun=="R" & ID=="200.1")) %>%
  filter(!(rerun=="R" & ID=="207.4")) %>% 
  mutate(Conc = as.numeric(Conc),
         OD = as.numeric(OD),
         Conc_2 = lead(Conc),
         OD_2 = lead(OD)) %>% 
  select(ID,Conc,Conc_2,OD,OD_2) %>%
  filter(!is.na(ID)) %>%
  rowwise() %>%
  mutate(Conc_mean = mean(c(Conc,Conc_2),na.rm=T),
         Conc_sd = sd(c(Conc,Conc_2),na.rm=T),
         OD_mean = mean(c(OD,OD_2),na.rm=T),
         OD_sd = sd(c(OD,OD_2),na.rm=T)) %>%
  mutate(DHEA_Conc_CV = 100*(Conc_sd/Conc_mean),
         DHEA_Conc_CV = round(as.numeric(DHEA_Conc_CV),3),
         DHEA_OD_CV = 100*(OD_sd/OD_mean),
         DHEA_OD_CV = round(as.numeric(DHEA_OD_CV),3),
         SID = as.factor(round(as.numeric(ID),2))) %>%
  select(SID,DHEA_Conc_CV,DHEA_OD_CV) %>%
  filter(!is.na(SID)) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID)) %>%
  arrange(SID) 

Saliva_TEST_CV_2 <- Saliva_TEST_CV_2 %>% 
  rename(ID = Name,
         Conc = `[Concentration]`,
         OD = `450`) %>%
  mutate(Conc = as.numeric(Conc),
         OD = as.numeric(OD),
         Conc_2 = lead(Conc),
         OD_2 = lead(OD)) %>% 
  select(ID,Conc,Conc_2,OD,OD_2) %>%
  filter(!is.na(ID)) %>%
  rowwise() %>%
  mutate(Conc_mean = mean(c(Conc,Conc_2),na.rm=T),
         Conc_sd = sd(c(Conc,Conc_2),na.rm=T),
         OD_mean = mean(c(OD,OD_2),na.rm=T),
         OD_sd = sd(c(OD,OD_2),na.rm=T)) %>%
  mutate(TEST_Conc_CV = 100*(Conc_sd/Conc_mean),
         TEST_Conc_CV = round(as.numeric(TEST_Conc_CV),3),
         TEST_OD_CV = 100*(OD_sd/OD_mean),
         TEST_OD_CV = round(as.numeric(TEST_OD_CV),3),
         SID = as.factor(round(as.numeric(ID),2))) %>%
  select(SID,TEST_Conc_CV,TEST_OD_CV) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID)) %>%
  filter(!is.na(SID)) %>%
  arrange(SID) 

Saliva_EST_CV_2 <- Saliva_EST_CV_2 %>% 
  rename(ID = Name,
         Conc = `[Concentration]`,
         OD = `450`) %>%
  mutate(Conc = as.numeric(Conc),
         OD = as.numeric(OD),
         Conc_2 = lead(Conc),
         OD_2 = lead(OD)) %>% 
  select(ID,Conc,Conc_2,OD,OD_2) %>%
  filter(!is.na(ID)) %>%
  rowwise() %>%
  mutate(Conc_mean = mean(c(Conc,Conc_2),na.rm=T),
         Conc_sd = sd(c(Conc,Conc_2),na.rm=T),
         OD_mean = mean(c(OD,OD_2),na.rm=T),
         OD_sd = sd(c(OD,OD_2),na.rm=T)) %>%
  mutate(EST_Conc_CV = 100*(Conc_sd/Conc_mean),
         EST_Conc_CV = round(as.numeric(EST_Conc_CV),3),
         EST_OD_CV = 100*(OD_sd/OD_mean),
         EST_OD_CV = round(as.numeric(EST_OD_CV),3),
         SID = as.factor(round(as.numeric(ID),2))) %>%
  select(SID,EST_Conc_CV,EST_OD_CV) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID)) %>%
  filter(!is.na(SID)) %>%
  arrange(SID) 

#combine two batches and create master df
Saliva_DHEA_CV <- rbind(Saliva_DHEA_CV_1,Saliva_DHEA_CV_2)
Saliva_TEST_CV <- rbind(Saliva_TEST_CV_1,Saliva_TEST_CV_2)
Saliva_EST_CV <- rbind(Saliva_EST_CV_1,Saliva_EST_CV_2)

#deal with reruns
DHEA_reruns <- read_xlsx(paste0(saliva_dir,'/Raw_conc/Saliva_repeats.xlsx'), sheet=1)
TEST_reruns <- read_xlsx(paste0(saliva_dir,'/Raw_conc/Saliva_repeats.xlsx'), sheet=2)
EST_reruns <- read_xlsx(paste0(saliva_dir,'/Raw_conc/Saliva_repeats.xlsx'), sheet=3)

DHEA_reruns <- DHEA_reruns %>% 
  separate(ID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID)) %>%
  arrange(SID) %>%
  filter(!is.na(SID)) %>%
  select(SID,week,Notes,finalConc_CV,finalOD_CV) %>%
  mutate(rerun=as.numeric(1))

TEST_reruns <- TEST_reruns %>% 
  separate(ID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID)) %>%
  arrange(SID) %>%
  filter(!is.na(SID)) %>%
  select(SID,week,Notes,finalConc_CV,finalOD_CV) %>%
  mutate(rerun=as.numeric(1))

EST_reruns <- EST_reruns %>% 
  separate(ID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID)) %>%
  arrange(SID) %>%
  filter(!is.na(SID)) %>%
  select(SID,week,Notes,finalConc_CV,finalOD_CV) %>%
  mutate(rerun=as.numeric(1))

Saliva_DHEA_CV <- Saliva_DHEA_CV %>%
  left_join(., DHEA_reruns, by=c("SID","week")) %>%
  mutate(DHEA_Conc_CV = ifelse(!is.na(rerun),finalConc_CV,DHEA_Conc_CV),
         DHEA_OD_CV = ifelse(!is.na(rerun),finalOD_CV,DHEA_OD_CV)) %>%
  select(SID,week,DHEA_Conc_CV,DHEA_OD_CV)

Saliva_TEST_CV <- Saliva_TEST_CV %>%
  left_join(., TEST_reruns, by=c("SID","week")) %>%
  mutate(TEST_Conc_CV = ifelse(!is.na(rerun),finalConc_CV,TEST_Conc_CV),
         TEST_OD_CV = ifelse(!is.na(rerun),finalOD_CV,TEST_OD_CV)) %>%
  select(SID,week,TEST_Conc_CV,TEST_OD_CV)

Saliva_EST_CV <- Saliva_EST_CV %>%
  left_join(., EST_reruns, by=c("SID","week")) %>%
  mutate(EST_Conc_CV = ifelse(!is.na(rerun),finalConc_CV,EST_Conc_CV),
         EST_OD_CV = ifelse(!is.na(rerun),finalOD_CV,EST_OD_CV)) %>%
  select(SID,week,EST_Conc_CV,EST_OD_CV)

#creater master df
Saliva_CV <- Saliva_DHEA_CV %>% full_join(.,Saliva_TEST_CV) %>% 
  full_join(.,Saliva_EST_CV) %>% arrange(SID) %>% 
  filter(SID %in% overview$SID) %>%
  mutate(ID = paste0(SID,'_',week))

#identify any further problematic IDs (i.e. appear twice in dataframe)
probIDs <- Saliva_CV$ID[duplicated(Saliva_CV$ID)]
probDF <- Saliva_CV %>% filter(ID %in% probIDs) %>% arrange(ID)

#make sure that all duplicated rows are identical
check <- duplicated(probDF) | duplicated(probDF[nrow(probDF):1, ])[nrow(probDF):1]

#remove duplicated rows
Saliva_CV <- Saliva_CV[!duplicated(Saliva_CV$ID),]

#create long format master df
Saliva_CV_long <- Saliva_CV %>%
  gather(variable,value,DHEA_Conc_CV:EST_OD_CV,-SID,-week) %>%
  separate(variable, into=c("hormone","variable"), by="_") %>%
  spread(variable, value) %>%
  mutate(Conc = as.numeric(Conc),
         OD = as.numeric(OD))

#summarise intra-assay CVs
Saliva_CV_summary <- Saliva_CV_long %>% 
  group_by(hormone) %>%
  summarise(mean_ConcCV = mean(Conc,na.rm=T),
            sd_ConcCV = sd(Conc,na.rm=T),
            min_ConcCV = min(Conc,na.rm=T),
            max_ConcCV = max(Conc,na.rm=T),
            mean_odCV = mean(OD,na.rm=T),
            sd_odCV = sd(OD,na.rm=T),
            min_odCV = min(OD,na.rm=T),
            max_odCV = max(OD,na.rm=T))

#plot distribution of intra-assay CVs
ConcCV_plot <- Saliva_CV_long %>% 
  ggplot(aes(x = Conc)) +
  geom_histogram(color="black",fill="white") +
  facet_wrap(~ hormone, scales="free")

ConcCV_plot

odCV_plot <- Saliva_CV_long %>% filter(OD < 100) %>%
  ggplot(aes(x = OD)) +
  geom_histogram(color="black",fill="white") +
  facet_wrap(~ hormone, scales="free")

odCV_plot
```

###CALCULATE INTER-ASSAY CVS. Note (MLB) - these are the variation in the controls (high and low), which is a measure of the variation of the plates/kits. As above, we calculate both concentrations and OD but use the OD.
```{r}

#import file of highs and lows
Saliva_DHEA_interCV <- read_xlsx(paste0(saliva_dir,'/Raw_conc/TAG_W1_Saliva_HighsLows_interassayCV.xlsx'), sheet=1)
Saliva_TEST_interCV <- read_xlsx(paste0(saliva_dir,'/Raw_conc/TAG_W1_Saliva_HighsLows_interassayCV.xlsx'), sheet=2)
Saliva_EST_interCV <- read_xlsx(paste0(saliva_dir,'/Raw_conc/TAG_W1_Saliva_HighsLows_interassayCV.xlsx'), sheet=3)

#clean and calculate interassay CV for concentrations and optical densities

# NOTE - I have commented out the below because I think this version is just averaging ALL the controls (highs and lows) and then taking the SD of all of them over the mean of all of them. Instead, a % CV should be calculated for all the highs, and then another % CV for all the lows - and then take an average of that. Also, the standard deviation should be of the means across plates, instead of the individual high/low control samples. See:
# https://salimetrics.com/calculating-inter-and-intra-assay-coefficients-of-variability/
#Scroll down to see the new code. I have also separated out by batch in case we want to report that way. - MLB

# Saliva_DHEA_interCV <- Saliva_DHEA_interCV %>%
#  rename(ID = `Well_ID`,
#          Conc = `[Concentration]`,
#          OD = `OD_450`) %>%
#   mutate(Conc = as.numeric(Conc),
#          OD = as.numeric(OD),
#          Conc_2 = lead(Conc),
#          OD_2 = lead(OD)) %>%
#   filter(!is.na(ID)) %>%
#   select(ID,Conc,Conc_2,OD,OD_2) %>%
#   rowwise() %>%
#   mutate(Conc_mean = mean(c(Conc,Conc_2),na.rm=T),
#          OD_mean = mean(c(OD,OD_2),na.rm=T)) %>%
#   group_by(ID) %>%
#   summarise(ConcCV_mean = mean(Conc_mean),
#             ConcCV_sd = sd(Conc_mean),
#             ConcCV = 100*(ConcCV_sd/ConcCV_mean),
#             odCV_mean = mean(OD_mean),
#             odCV_sd = sd(OD_mean),
#             odCV = 100*(odCV_sd/odCV_mean)) %>%
#   group_by() %>%
#   summarise(ConcCV = mean(ConcCV),
#             odCV = mean(odCV))
# 
# Saliva_TEST_interCV <- Saliva_TEST_interCV %>%
#   rename(ID = `Well_ID`,
#          Conc = `[Concentration]`,
#          OD = `OD_450`) %>%
#   mutate(Conc = as.numeric(Conc),
#          OD = as.numeric(OD),
#          Conc_2 = lead(Conc),
#          OD_2 = lead(OD)) %>%
#   filter(!is.na(ID)) %>%
#   select(ID,Conc,Conc_2,OD,OD_2) %>%
#   rowwise() %>%
#   mutate(Conc_mean = mean(c(Conc,Conc_2),na.rm=T),
#          OD_mean = mean(c(OD,OD_2),na.rm=T)) %>%
#   group_by(ID) %>%
#   summarise(ConcCV_mean = mean(Conc_mean),
#             ConcCV_sd = sd(Conc_mean),
#             ConcCV = 100*(ConcCV_sd/ConcCV_mean),
#             odCV_mean = mean(OD_mean),
#             odCV_sd = sd(OD_mean),
#             odCV = 100*(odCV_sd/odCV_mean)) %>%
#   group_by() %>%
#   summarise(ConcCV = mean(ConcCV),
#             odCV = mean(odCV))
# 
# Saliva_EST_interCV <- Saliva_EST_interCV %>%
#   rename(ID = `Well_ID`,
#          Conc = `[Concentration]`,
#          OD = `OD_450`) %>%
#   mutate(Conc = as.numeric(Conc),
#          OD = as.numeric(OD),
#          Conc_2 = lead(Conc),
#          OD_2 = lead(OD)) %>%
#   filter(!is.na(ID)) %>%
#   select(ID,Conc,Conc_2,OD,OD_2) %>%
#   rowwise() %>%
#   mutate(Conc_mean = mean(c(Conc,Conc_2),na.rm=T),
#          OD_mean = mean(c(OD,OD_2),na.rm=T)) %>%
#   group_by(ID) %>%
#   summarise(ConcCV_mean = mean(Conc_mean,na.rm=T),
#             ConcCV_sd = sd(Conc_mean,na.rm=T),
#             ConcCV = 100*(ConcCV_sd/ConcCV_mean),
#             odCV_mean = mean(OD_mean),
#             odCV_sd = sd(OD_mean),
#             odCV = 100*(odCV_sd/odCV_mean)) %>%
#   group_by() %>%
#   summarise(ConcCV = mean(ConcCV),
#             odCV = mean(odCV))

#-----------------------------
# NEW INTRA ASSAYS (ODs only) (MLB added later)

# --- DHEA ---
# Mean of high controls within plates:
dhea_high_mean1 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlH"&Saliva_DHEA_interCV$plate=="1","OD_450"]))
dhea_high_mean2 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlH"&Saliva_DHEA_interCV$plate=="2","OD_450"]))
dhea_high_mean3 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlH"&Saliva_DHEA_interCV$plate=="3","OD_450"]))
dhea_high_mean4 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlH"&Saliva_DHEA_interCV$plate=="4","OD_450"]))
dhea_high_mean5 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlH"&Saliva_DHEA_interCV$plate=="5","OD_450"]))
dhea_high_mean6 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlH"&Saliva_DHEA_interCV$plate=="6","OD_450"]))
dhea_high_mean7 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlH"&Saliva_DHEA_interCV$plate=="7","OD_450"]))
dhea_high_mean8 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlH"&Saliva_DHEA_interCV$plate=="8","OD_450"]))
dhea_high_mean9 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlH"&Saliva_DHEA_interCV$plate=="9","OD_450"]))
dhea_high_mean10 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlH"&Saliva_DHEA_interCV$plate=="10","OD_450"]))
dhea_high_mean11 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlH"&Saliva_DHEA_interCV$plate=="11","OD_450"]))
dhea_high_mean12 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlH"&Saliva_DHEA_interCV$plate=="12","OD_450"]))
dhea_high_mean13 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlH"&Saliva_DHEA_interCV$plate=="13","OD_450"]))
dhea_high_mean14 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlH"&Saliva_DHEA_interCV$plate=="14","OD_450"]))
dhea_high_mean15 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlH"&Saliva_DHEA_interCV$plate=="15","OD_450"]))
dhea_high_mean16 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlH"&Saliva_DHEA_interCV$plate=="16","OD_450"]))
dhea_high_mean17 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlH"&Saliva_DHEA_interCV$plate=="17","OD_450"]))
dhea_high_mean18 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlH"&Saliva_DHEA_interCV$plate=="18","OD_450"]))
dhea_high_mean19 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlH"&Saliva_DHEA_interCV$plate=="19","OD_450"]))
dhea_high_mean20 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlH"&Saliva_DHEA_interCV$plate=="20","OD_450"]))

# High controls mean of means:
dhea_high_mean <- mean(c(dhea_high_mean1, dhea_high_mean2, dhea_high_mean3, dhea_high_mean4, dhea_high_mean5, dhea_high_mean6, dhea_high_mean7, dhea_high_mean8, dhea_high_mean9, dhea_high_mean10, dhea_high_mean11, dhea_high_mean12, dhea_high_mean13, dhea_high_mean14, dhea_high_mean15, dhea_high_mean16, dhea_high_mean17, dhea_high_mean18, dhea_high_mean19, dhea_high_mean20))

# Separate by batch
# batch 1
dhea_high_mean_b1 <- mean(c(dhea_high_mean8, dhea_high_mean9, dhea_high_mean10, dhea_high_mean11, dhea_high_mean12, dhea_high_mean13, dhea_high_mean14, dhea_high_mean15, dhea_high_mean16, dhea_high_mean17, dhea_high_mean18, dhea_high_mean19, dhea_high_mean20))
# batch 2
dhea_high_mean_b2 <- mean(c(dhea_high_mean1, dhea_high_mean2, dhea_high_mean3, dhea_high_mean4, dhea_high_mean5, dhea_high_mean6, dhea_high_mean7))

# High controls SD of means:
dhea_high_sd <- sd(c(dhea_high_mean1, dhea_high_mean2, dhea_high_mean3, dhea_high_mean4, dhea_high_mean5, dhea_high_mean6, dhea_high_mean7, dhea_high_mean8, dhea_high_mean9, dhea_high_mean10, dhea_high_mean11, dhea_high_mean12, dhea_high_mean13, dhea_high_mean14, dhea_high_mean15, dhea_high_mean16, dhea_high_mean17, dhea_high_mean18, dhea_high_mean19, dhea_high_mean20))

# batch 1
dhea_high_sd_b1 <- sd(c(dhea_high_mean8, dhea_high_mean9, dhea_high_mean10, dhea_high_mean11, dhea_high_mean12, dhea_high_mean13, dhea_high_mean14, dhea_high_mean15, dhea_high_mean16, dhea_high_mean17, dhea_high_mean18, dhea_high_mean19, dhea_high_mean20))
# batch 2
dhea_high_sd_b2 <- sd(c(dhea_high_mean1, dhea_high_mean2, dhea_high_mean3, dhea_high_mean4, dhea_high_mean5, dhea_high_mean6, dhea_high_mean7))

# % CV high across plates. Note this is NOT the same as just averaging each of the individual CVs for the result 1 and 2 of each high and low control (i.e., we don't want to just average the "OD_450_CV_perc" column from the HighsLows sheet):
dhea_high_cv <- (dhea_high_sd/dhea_high_mean)*100

#batch 1
dhea_high_cv_b1 <- (dhea_high_sd_b1/dhea_high_mean_b1)*100
#batch 2
dhea_high_cv_b2 <- (dhea_high_sd_b2/dhea_high_mean_b2)*100

# Mean of low controls within plates:
dhea_low_mean1 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlL"&Saliva_DHEA_interCV$plate=="1","OD_450"]))
dhea_low_mean2 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlL"&Saliva_DHEA_interCV$plate=="2","OD_450"]))
dhea_low_mean3 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlL"&Saliva_DHEA_interCV$plate=="3","OD_450"]))
dhea_low_mean4 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlL"&Saliva_DHEA_interCV$plate=="4","OD_450"]))
dhea_low_mean5 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlL"&Saliva_DHEA_interCV$plate=="5","OD_450"]))
dhea_low_mean6 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlL"&Saliva_DHEA_interCV$plate=="6","OD_450"]))
dhea_low_mean7 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlL"&Saliva_DHEA_interCV$plate=="7","OD_450"]))
dhea_low_mean8 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlL"&Saliva_DHEA_interCV$plate=="8","OD_450"]))
dhea_low_mean9 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlL"&Saliva_DHEA_interCV$plate=="9","OD_450"]))
dhea_low_mean10 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlL"&Saliva_DHEA_interCV$plate=="10","OD_450"]))
dhea_low_mean11 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlL"&Saliva_DHEA_interCV$plate=="11","OD_450"]))
dhea_low_mean12 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlL"&Saliva_DHEA_interCV$plate=="12","OD_450"]))
dhea_low_mean13 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlL"&Saliva_DHEA_interCV$plate=="13","OD_450"]))
dhea_low_mean14 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlL"&Saliva_DHEA_interCV$plate=="14","OD_450"]))
dhea_low_mean15 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlL"&Saliva_DHEA_interCV$plate=="15","OD_450"]))
dhea_low_mean16 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlL"&Saliva_DHEA_interCV$plate=="16","OD_450"]))
dhea_low_mean17 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlL"&Saliva_DHEA_interCV$plate=="17","OD_450"]))
dhea_low_mean18 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlL"&Saliva_DHEA_interCV$plate=="18","OD_450"]))
dhea_low_mean19 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlL"&Saliva_DHEA_interCV$plate=="19","OD_450"]))
dhea_low_mean20 <- mean(data.matrix(Saliva_DHEA_interCV[Saliva_DHEA_interCV$Well_ID=="CtrlL"&Saliva_DHEA_interCV$plate=="20","OD_450"]))

# low controls mean of means:
dhea_low_mean <- mean(c(dhea_low_mean1, dhea_low_mean2, dhea_low_mean3, dhea_low_mean4, dhea_low_mean5, dhea_low_mean6, dhea_low_mean7, dhea_low_mean8, dhea_low_mean9, dhea_low_mean10, dhea_low_mean11, dhea_low_mean12, dhea_low_mean13, dhea_low_mean14, dhea_low_mean15, dhea_low_mean16, dhea_low_mean17, dhea_low_mean18, dhea_low_mean19, dhea_low_mean20))

# batch 1
dhea_low_mean_b1 <- mean(c(dhea_low_mean8, dhea_low_mean9, dhea_low_mean10, dhea_low_mean11, dhea_low_mean12, dhea_low_mean13, dhea_low_mean14, dhea_low_mean15, dhea_low_mean16, dhea_low_mean17, dhea_low_mean18, dhea_low_mean19, dhea_low_mean20))

#batch 2
dhea_low_mean_b2 <- mean(c(dhea_low_mean1, dhea_low_mean2, dhea_low_mean3, dhea_low_mean4, dhea_low_mean5, dhea_low_mean6, dhea_low_mean7))

# low controls SD of means:
dhea_low_sd <- sd(c(dhea_low_mean1, dhea_low_mean2, dhea_low_mean3, dhea_low_mean4, dhea_low_mean5, dhea_low_mean6, dhea_low_mean7, dhea_low_mean8, dhea_low_mean9, dhea_low_mean10, dhea_low_mean11, dhea_low_mean12, dhea_low_mean13, dhea_low_mean14, dhea_low_mean15, dhea_low_mean16, dhea_low_mean17, dhea_low_mean18, dhea_low_mean19, dhea_low_mean20))

# batch 1
dhea_low_sd_b1 <- sd(c(dhea_low_mean8, dhea_low_mean9, dhea_low_mean10, dhea_low_mean11, dhea_low_mean12, dhea_low_mean13, dhea_low_mean14, dhea_low_mean15, dhea_low_mean16, dhea_low_mean17, dhea_low_mean18, dhea_low_mean19, dhea_low_mean20))

#batch 2
dhea_low_sd_b2 <- sd(c(dhea_low_mean1, dhea_low_mean2, dhea_low_mean3, dhea_low_mean4, dhea_low_mean5, dhea_low_mean6, dhea_low_mean7))

# % CV low across plates:
dhea_low_cv <- (dhea_low_sd/dhea_low_mean)*100

#batch 1
dhea_low_cv_b1 <- (dhea_low_sd_b1/dhea_low_mean_b1)*100
#batch 2
dhea_low_cv_b2 <- (dhea_low_sd_b2/dhea_low_mean_b2)*100

# AVERAGE DHEA % CV:
dhea_inter_cv <- (dhea_high_cv + dhea_low_cv)/2

#batch 1
dhea_inter_cv_b1 <- (dhea_high_cv_b1 + dhea_low_cv_b1)/2
# batch 2
dhea_inter_cv_b2 <- (dhea_high_cv_b2 + dhea_low_cv_b2)/2

# --- TEST ---
# Mean of high controls within plates:
test_high_mean1 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlH"&Saliva_TEST_interCV$plate=="1","OD_450"]))
test_high_mean2 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlH"&Saliva_TEST_interCV$plate=="2","OD_450"]))
test_high_mean3 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlH"&Saliva_TEST_interCV$plate=="3","OD_450"]))
test_high_mean4 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlH"&Saliva_TEST_interCV$plate=="4","OD_450"]))
test_high_mean5 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlH"&Saliva_TEST_interCV$plate=="5","OD_450"]))
test_high_mean6 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlH"&Saliva_TEST_interCV$plate=="6","OD_450"]))
test_high_mean7 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlH"&Saliva_TEST_interCV$plate=="7","OD_450"]))
test_high_mean8 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlH"&Saliva_TEST_interCV$plate=="8","OD_450"]))
test_high_mean9 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlH"&Saliva_TEST_interCV$plate=="9","OD_450"]))
test_high_mean10 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlH"&Saliva_TEST_interCV$plate=="10","OD_450"]))
test_high_mean11 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlH"&Saliva_TEST_interCV$plate=="11","OD_450"]))
test_high_mean12 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlH"&Saliva_TEST_interCV$plate=="12","OD_450"]))
test_high_mean13 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlH"&Saliva_TEST_interCV$plate=="13","OD_450"]))
test_high_mean14 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlH"&Saliva_TEST_interCV$plate=="14","OD_450"]))
test_high_mean15 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlH"&Saliva_TEST_interCV$plate=="15","OD_450"]))
test_high_mean16 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlH"&Saliva_TEST_interCV$plate=="16","OD_450"]))
test_high_mean17 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlH"&Saliva_TEST_interCV$plate=="17","OD_450"]))
test_high_mean18 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlH"&Saliva_TEST_interCV$plate=="18","OD_450"]))
test_high_mean19 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlH"&Saliva_TEST_interCV$plate=="19","OD_450"]))
test_high_mean20 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlH"&Saliva_TEST_interCV$plate=="20","OD_450"]))

# High controls mean of means:
test_high_mean <- mean(c(test_high_mean1, test_high_mean2, test_high_mean3, test_high_mean4, test_high_mean5, test_high_mean6, test_high_mean7, test_high_mean8, test_high_mean9, test_high_mean10, test_high_mean11, test_high_mean12, test_high_mean13, test_high_mean14, test_high_mean15, test_high_mean16, test_high_mean17, test_high_mean18, test_high_mean19, test_high_mean20))

#batch 1:
test_high_mean_b1 <- mean(c(test_high_mean8, test_high_mean9, test_high_mean10, test_high_mean11, test_high_mean12, test_high_mean13, test_high_mean14, test_high_mean15, test_high_mean16, test_high_mean17, test_high_mean18, test_high_mean19, test_high_mean20))
#batch 2:
test_high_mean_b2 <- mean(c(test_high_mean1, test_high_mean2, test_high_mean3, test_high_mean4, test_high_mean5, test_high_mean6, test_high_mean7))

# High controls SD of means:
test_high_sd <- sd(c(test_high_mean1, test_high_mean2, test_high_mean3, test_high_mean4, test_high_mean5, test_high_mean6, test_high_mean7, test_high_mean8, test_high_mean9, test_high_mean10, test_high_mean11, test_high_mean12, test_high_mean13, test_high_mean14, test_high_mean15, test_high_mean16, test_high_mean17, test_high_mean18, test_high_mean19, test_high_mean20))

#batch 1:
test_high_sd_b1 <- sd(c(test_high_mean8, test_high_mean9, test_high_mean10, test_high_mean11, test_high_mean12, test_high_mean13, test_high_mean14, test_high_mean15, test_high_mean16, test_high_mean17, test_high_mean18, test_high_mean19, test_high_mean20))
#batch 2:
test_high_sd_b2 <- sd(c(test_high_mean1, test_high_mean2, test_high_mean3, test_high_mean4, test_high_mean5, test_high_mean6, test_high_mean7))

# % CV high across plates
test_high_cv <- (test_high_sd/test_high_mean)*100

#batch 1:
test_high_cv_b1 <- (test_high_sd_b1/test_high_mean_b1)*100

#batch 2:
test_high_cv_b2 <- (test_high_sd_b2/test_high_mean_b2)*100

# Mean of low controls within plates:
test_low_mean1 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlL"&Saliva_TEST_interCV$plate=="1","OD_450"]))
test_low_mean2 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlL"&Saliva_TEST_interCV$plate=="2","OD_450"]))
test_low_mean3 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlL"&Saliva_TEST_interCV$plate=="3","OD_450"]))
test_low_mean4 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlL"&Saliva_TEST_interCV$plate=="4","OD_450"]))
test_low_mean5 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlL"&Saliva_TEST_interCV$plate=="5","OD_450"]))
test_low_mean6 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlL"&Saliva_TEST_interCV$plate=="6","OD_450"]))
test_low_mean7 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlL"&Saliva_TEST_interCV$plate=="7","OD_450"]))
test_low_mean8 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlL"&Saliva_TEST_interCV$plate=="8","OD_450"]))
test_low_mean9 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlL"&Saliva_TEST_interCV$plate=="9","OD_450"]))
test_low_mean10 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlL"&Saliva_TEST_interCV$plate=="10","OD_450"]))
test_low_mean11 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlL"&Saliva_TEST_interCV$plate=="11","OD_450"]))
test_low_mean12 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlL"&Saliva_TEST_interCV$plate=="12","OD_450"]))
test_low_mean13 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlL"&Saliva_TEST_interCV$plate=="13","OD_450"]))
test_low_mean14 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlL"&Saliva_TEST_interCV$plate=="14","OD_450"]))
test_low_mean15 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlL"&Saliva_TEST_interCV$plate=="15","OD_450"]))
test_low_mean16 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlL"&Saliva_TEST_interCV$plate=="16","OD_450"]))
test_low_mean17 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlL"&Saliva_TEST_interCV$plate=="17","OD_450"]))
test_low_mean18 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlL"&Saliva_TEST_interCV$plate=="18","OD_450"]))
test_low_mean19 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlL"&Saliva_TEST_interCV$plate=="19","OD_450"]))
test_low_mean20 <- mean(data.matrix(Saliva_TEST_interCV[Saliva_TEST_interCV$Well_ID=="CtrlL"&Saliva_TEST_interCV$plate=="20","OD_450"]))

# low controls mean of means:
test_low_mean <- mean(c(test_low_mean1, test_low_mean2, test_low_mean3, test_low_mean4, test_low_mean5, test_low_mean6, test_low_mean7, test_low_mean8, test_low_mean9, test_low_mean10, test_low_mean11, test_low_mean12, test_low_mean13, test_low_mean14, test_low_mean15, test_low_mean16, test_low_mean17, test_low_mean18, test_low_mean19, test_low_mean20))

#batch 1:
test_low_mean_b1 <- mean(c(test_low_mean8, test_low_mean9, test_low_mean10, test_low_mean11, test_low_mean12, test_low_mean13, test_low_mean14, test_low_mean15, test_low_mean16, test_low_mean17, test_low_mean18, test_low_mean19, test_low_mean20))

#batch 2:
test_low_mean_b2 <- mean(c(test_low_mean1, test_low_mean2, test_low_mean3, test_low_mean4, test_low_mean5, test_low_mean6, test_low_mean7))

# low controls SD of means:
test_low_sd <- sd(c(test_low_mean1, test_low_mean2, test_low_mean3, test_low_mean4, test_low_mean5, test_low_mean6, test_low_mean7, test_low_mean8, test_low_mean9, test_low_mean10, test_low_mean11, test_low_mean12, test_low_mean13, test_low_mean14, test_low_mean15, test_low_mean16, test_low_mean17, test_low_mean18, test_low_mean19, test_low_mean20))

#batch 1:
test_low_sd_b1 <- sd(c(test_low_mean8, test_low_mean9, test_low_mean10, test_low_mean11, test_low_mean12, test_low_mean13, test_low_mean14, test_low_mean15, test_low_mean16, test_low_mean17, test_low_mean18, test_low_mean19, test_low_mean20))

#batch 2:
test_low_sd_b2 <- sd(c(test_low_mean1, test_low_mean2, test_low_mean3, test_low_mean4, test_low_mean5, test_low_mean6, test_low_mean7))

# % CV low across plates:
test_low_cv <- (test_low_sd/test_low_mean)*100

#batch 1:
test_low_cv_b1 <- (test_low_sd_b1/test_low_mean_b1)*100

#batch 2:
test_low_cv_b2 <- (test_low_sd_b2/test_low_mean_b2)*100

# AVERAGE TEST % CV:
test_inter_cv <- (test_high_cv + test_low_cv)/2

#batch 1:
test_inter_cv_b1 <- (test_high_cv_b1 + test_low_cv_b1)/2

#batch 2:
test_inter_cv_b2 <- (test_high_cv_b2 + test_low_cv_b2)/2


# --- EST ---
# Mean of high controls within plates:
est_high_mean1 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlH"&Saliva_EST_interCV$plate=="1","OD_450"]))
est_high_mean2 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlH"&Saliva_EST_interCV$plate=="2","OD_450"]))
est_high_mean3 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlH"&Saliva_EST_interCV$plate=="3","OD_450"]))
est_high_mean4 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlH"&Saliva_EST_interCV$plate=="4","OD_450"]))
est_high_mean5 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlH"&Saliva_EST_interCV$plate=="5","OD_450"]))
est_high_mean6 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlH"&Saliva_EST_interCV$plate=="6","OD_450"]))
est_high_mean7 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlH"&Saliva_EST_interCV$plate=="7","OD_450"]))
est_high_mean8 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlH"&Saliva_EST_interCV$plate=="8","OD_450"]))
est_high_mean9 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlH"&Saliva_EST_interCV$plate=="9","OD_450"]))
est_high_mean10 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlH"&Saliva_EST_interCV$plate=="10","OD_450"]))
est_high_mean11 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlH"&Saliva_EST_interCV$plate=="11","OD_450"]))
est_high_mean12 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlH"&Saliva_EST_interCV$plate=="12","OD_450"]))
est_high_mean13 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlH"&Saliva_EST_interCV$plate=="13","OD_450"]))
est_high_mean14 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlH"&Saliva_EST_interCV$plate=="14","OD_450"]))
est_high_mean15 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlH"&Saliva_EST_interCV$plate=="15","OD_450"]))
est_high_mean16 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlH"&Saliva_EST_interCV$plate=="16","OD_450"]))
est_high_mean17 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlH"&Saliva_EST_interCV$plate=="17","OD_450"]))
est_high_mean18 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlH"&Saliva_EST_interCV$plate=="18","OD_450"]))
est_high_mean19 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlH"&Saliva_EST_interCV$plate=="19","OD_450"]))
est_high_mean20 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlH"&Saliva_EST_interCV$plate=="20","OD_450"]))
est_high_mean21 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlH"&Saliva_EST_interCV$plate=="21","OD_450"]))

# High controls mean of means:
est_high_mean <- mean(c(est_high_mean1, est_high_mean2, est_high_mean3, est_high_mean4, est_high_mean5, est_high_mean6, est_high_mean7, est_high_mean8, est_high_mean9, est_high_mean10, est_high_mean11, est_high_mean12, est_high_mean13, est_high_mean14, est_high_mean15, est_high_mean16, est_high_mean17, est_high_mean18, est_high_mean19, est_high_mean20, est_high_mean21))

#batch 1:
est_high_mean_b1 <- mean(c(est_high_mean8, est_high_mean9, est_high_mean10, est_high_mean11, est_high_mean12, est_high_mean13, est_high_mean14, est_high_mean15, est_high_mean16, est_high_mean17, est_high_mean18, est_high_mean19, est_high_mean20, est_high_mean21))

#batch 2:
est_high_mean_b2 <- mean(c(est_high_mean1, est_high_mean2, est_high_mean3, est_high_mean4, est_high_mean5, est_high_mean6, est_high_mean7))

# High controls SD of means:
est_high_sd <- sd(c(est_high_mean1, est_high_mean2, est_high_mean3, est_high_mean4, est_high_mean5, est_high_mean6, est_high_mean7, est_high_mean8, est_high_mean9, est_high_mean10, est_high_mean11, est_high_mean12, est_high_mean13, est_high_mean14, est_high_mean15, est_high_mean16, est_high_mean17, est_high_mean18, est_high_mean19, est_high_mean20, est_high_mean21))

#batch 1:
est_high_sd_b1 <- sd(c(est_high_mean8, est_high_mean9, est_high_mean10, est_high_mean11, est_high_mean12, est_high_mean13, est_high_mean14, est_high_mean15, est_high_mean16, est_high_mean17, est_high_mean18, est_high_mean19, est_high_mean20, est_high_mean21))

#batch 2:
est_high_sd_b2 <- sd(c(est_high_mean1, est_high_mean2, est_high_mean3, est_high_mean4, est_high_mean5, est_high_mean6, est_high_mean7))

# % CV high across plates
est_high_cv <- (est_high_sd/est_high_mean)*100

#batch 1:
est_high_cv_b1 <- (est_high_sd_b1/est_high_mean_b1)*100

#batch 2:
est_high_cv_b2 <- (est_high_sd_b2/est_high_mean_b2)*100

# Mean of low controls within plates:
est_low_mean1 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlL"&Saliva_EST_interCV$plate=="1","OD_450"]))
est_low_mean2 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlL"&Saliva_EST_interCV$plate=="2","OD_450"]))
est_low_mean3 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlL"&Saliva_EST_interCV$plate=="3","OD_450"]))
est_low_mean4 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlL"&Saliva_EST_interCV$plate=="4","OD_450"]))
est_low_mean5 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlL"&Saliva_EST_interCV$plate=="5","OD_450"]))
est_low_mean6 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlL"&Saliva_EST_interCV$plate=="6","OD_450"]))
est_low_mean7 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlL"&Saliva_EST_interCV$plate=="7","OD_450"]))
est_low_mean8 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlL"&Saliva_EST_interCV$plate=="8","OD_450"]))
est_low_mean9 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlL"&Saliva_EST_interCV$plate=="9","OD_450"]))
est_low_mean10 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlL"&Saliva_EST_interCV$plate=="10","OD_450"]))
est_low_mean11 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlL"&Saliva_EST_interCV$plate=="11","OD_450"]))
est_low_mean12 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlL"&Saliva_EST_interCV$plate=="12","OD_450"]))
est_low_mean13 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlL"&Saliva_EST_interCV$plate=="13","OD_450"]))
est_low_mean14 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlL"&Saliva_EST_interCV$plate=="14","OD_450"]))
est_low_mean15 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlL"&Saliva_EST_interCV$plate=="15","OD_450"]))
est_low_mean16 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlL"&Saliva_EST_interCV$plate=="16","OD_450"]))
est_low_mean17 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlL"&Saliva_EST_interCV$plate=="17","OD_450"]))
est_low_mean18 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlL"&Saliva_EST_interCV$plate=="18","OD_450"]))
est_low_mean19 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlL"&Saliva_EST_interCV$plate=="19","OD_450"]))
est_low_mean20 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlL"&Saliva_EST_interCV$plate=="20","OD_450"]))
est_low_mean21 <- mean(data.matrix(Saliva_EST_interCV[Saliva_EST_interCV$Well_ID=="CtrlL"&Saliva_EST_interCV$plate=="21","OD_450"]))

# low controls mean of means:
est_low_mean <- mean(c(est_low_mean1, est_low_mean2, est_low_mean3, est_low_mean4, est_low_mean5, est_low_mean6, est_low_mean7, est_low_mean8, est_low_mean9, est_low_mean10, est_low_mean11, est_low_mean12, est_low_mean13, est_low_mean14, est_low_mean15, est_low_mean16, est_low_mean17, est_low_mean18, est_low_mean19, est_low_mean20, est_low_mean21))

#batch 1:
est_low_mean_b1 <- mean(c(est_low_mean8, est_low_mean9, est_low_mean10, est_low_mean11, est_low_mean12, est_low_mean13, est_low_mean14, est_low_mean15, est_low_mean16, est_low_mean17, est_low_mean18, est_low_mean19, est_low_mean20, est_low_mean21))

#batch 2:
est_low_mean_b2 <- mean(c(est_low_mean1, est_low_mean2, est_low_mean3, est_low_mean4, est_low_mean5, est_low_mean6, est_low_mean7))

# low controls SD of means:
est_low_sd <- sd(c(est_low_mean1, est_low_mean2, est_low_mean3, est_low_mean4, est_low_mean5, est_low_mean6, est_low_mean7, est_low_mean8, est_low_mean9, est_low_mean10, est_low_mean11, est_low_mean12, est_low_mean13, est_low_mean14, est_low_mean15, est_low_mean16, est_low_mean17, est_low_mean18, est_low_mean19, est_low_mean20, est_low_mean21))

#batch 1:
est_low_sd_b1 <- sd(c(est_low_mean8, est_low_mean9, est_low_mean10, est_low_mean11, est_low_mean12, est_low_mean13, est_low_mean14, est_low_mean15, est_low_mean16, est_low_mean17, est_low_mean18, est_low_mean19, est_low_mean20, est_low_mean21))

#batch 2:
est_low_sd_b2 <- sd(c(est_low_mean1, est_low_mean2, est_low_mean3, est_low_mean4, est_low_mean5, est_low_mean6, est_low_mean7))

# % CV low across plates:
est_low_cv <- (est_low_sd/est_low_mean)*100

#batch 1:
est_low_cv_b1 <- (est_low_sd_b1/est_low_mean_b1)*100

#batch 2:
est_low_cv_b2 <- (est_low_sd_b2/est_low_mean_b2)*100

# AVERAGE EST % CV:
est_inter_cv <- (est_high_cv + est_low_cv)/2

#batch 1:
est_inter_cv_b1 <- (est_high_cv_b1 + est_low_cv_b1)/2

#batch 2:
est_inter_cv_b2 <- (est_high_cv_b2 + est_low_cv_b2)/2


```
