---
title: "calculateCV_saliva_W2"
author: "Michelle Byrne based on Nandi's W1 file"
date: "25 July 2020"
output: html_document
---

```{r, include=FALSE}
#LOAD PACKAGES AND SET DIRECTORIES

packages <- c("ggplot2","tidyr","stringr","knitr","corrplot","data.table","readxl","gridExtra","dplyr", "psych","kableExtra","lavaan","xlsx","DescTools")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}
lapply(packages, library, character.only = TRUE)

cas_dir <- 'Z:/TAG/'
saliva_dir <- paste0(cas_dir,'behavior/Puberty/Saliva/Wave2')
options(digits=3)
```

###IMPORT TAG OVERVIEW DOC FROM CAS
```{r, include = F}
#import "overview" document so that we can filter analyses to subjects that were not excluded

overview <- read.xlsx(paste0(cas_dir,'behavior/Overview/Overview_Withdrawn_Completed/TAG_Overview_Doc.xlsx'),1)
overview <- overview[,c("TAG_ID","W2S2_Completed","Withdrawn_W2","Exclusionary_Withdrawl")]

#removing everyone who withdrew at W2 (exclusionary withdrawals & Withdrawn_W2) - includes withdrawn at W1
overview <- overview %>% 
  rename(SID = TAG_ID) %>%
  replace_na(list(Withdrawn_W1 = 0)) %>%
  replace_na(list(Exclusionary_Withdrawl = 0)) %>% 
  arrange(Exclusionary_Withdrawl) %>% 
  mutate(SID=gsub("[^0-9\\.]", "", SID)) %>%
  filter(Exclusionary_Withdrawl==0) %>%
  filter(Withdrawn_W2==0) # there is also code 2 = eligible for recontact at W3 but didn't participate at W2 but didn't want to include these people, wouldn't have saliva anyway.
```

###CALCULATE INTRA-ASSAY CVS. Note (MLB) - these are the variation between the indvidual duplicate samples. Concentration and optical density CVs are calculated here but we use and report OD CVs.
```{r}

#batch 1
#import files -- -note these sheets should only include the redos (and no originals that needed to be redone)
Saliva_DHEA_CV_1 <- read_xlsx(paste0(saliva_dir,'/Raw_conc/TAG_SALIVA_W2_Master_File_Batch1.xlsx'), sheet='DHEA final')
Saliva_TEST_CV_1 <- read_xlsx(paste0(saliva_dir,'/Raw_conc/TAG_SALIVA_W2_Master_File_Batch1.xlsx'), sheet='Testo final')
Saliva_EST_CV_1 <- read_xlsx(paste0(saliva_dir,'/Raw_conc/TAG_SALIVA_W2_Master_File_Batch1.xlsx'), sheet='Estradiol final')

#clean and calculate intra-assay CV for concentrations and optical densities
# Note that although the raw assay files include CVs as a column, these are based on rounded values, so we recalculate the CVs here based on the rawest data to be more accurate.
Saliva_DHEA_CV_1 <- Saliva_DHEA_CV_1 %>%
  rename(WellID = `Well ID`,
         ID = Name,
         Conc = `[Concentration]`,
         OD = `450`) %>%
  mutate(Conc = as.numeric(Conc),
         OD = as.numeric(OD),
         Conc_2 = lead(Conc),
         OD_2 = lead(OD)) %>% 
  select(ID,Conc,Conc_2,OD,OD_2) %>%
  filter(!is.na(ID)) %>%
  rowwise() %>%
  mutate(Conc_mean = mean(c(Conc,Conc_2),na.rm=T),
         Conc_sd = sd(c(Conc,Conc_2),na.rm=T),
         OD_mean = mean(c(OD,OD_2),na.rm=T),
         OD_sd = sd(c(OD,OD_2),na.rm=T)) %>%
  mutate(DHEA_Conc_CV = 100*(Conc_sd/Conc_mean),
         DHEA_Conc_CV = round(as.numeric(DHEA_Conc_CV),3),
         DHEA_OD_CV = 100*(OD_sd/OD_mean),
         DHEA_OD_CV = round(as.numeric(DHEA_OD_CV),3),
         SID = as.factor(round(as.numeric(ID),2))) %>%
  select(SID,DHEA_Conc_CV,DHEA_OD_CV) %>%
  filter(!is.na(SID)) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID)) %>%
  arrange(SID) 

Saliva_TEST_CV_1 <- Saliva_TEST_CV_1 %>% 
  rename(WellID = `Well ID`,
         ID = Name,
         Conc = `[Concentration]`,
         OD = `450`) %>%
  mutate(Conc = as.numeric(Conc),
         OD = as.numeric(OD),
         Conc_2 = lead(Conc),
         OD_2 = lead(OD)) %>% 
  select(ID,Conc,Conc_2,OD,OD_2) %>%
  filter(!is.na(ID)) %>%
  rowwise() %>%
  mutate(Conc_mean = mean(c(Conc,Conc_2),na.rm=T),
         Conc_sd = sd(c(Conc,Conc_2),na.rm=T),
         OD_mean = mean(c(OD,OD_2),na.rm=T),
         OD_sd = sd(c(OD,OD_2),na.rm=T)) %>%
  mutate(TEST_Conc_CV = 100*(Conc_sd/Conc_mean),
         TEST_Conc_CV = round(as.numeric(TEST_Conc_CV),3),
         TEST_OD_CV = 100*(OD_sd/OD_mean),
         TEST_OD_CV = round(as.numeric(TEST_OD_CV),3),
         SID = as.factor(round(as.numeric(ID),2))) %>%
  select(SID,TEST_Conc_CV,TEST_OD_CV) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID)) %>%
  filter(!is.na(SID)) %>%
  arrange(SID) 

Saliva_EST_CV_1 <- Saliva_EST_CV_1 %>% 
  rename(ID = Name,
         Conc = `[Concentration]`,
         OD = `450`) %>%
  mutate(Conc = as.numeric(Conc),
         OD = as.numeric(OD),
         Conc_2 = lead(Conc),
         OD_2 = lead(OD)) %>% 
  select(ID,Conc,Conc_2,OD,OD_2) %>%
  filter(!is.na(ID)) %>%
  rowwise() %>%
  mutate(Conc_mean = mean(c(Conc,Conc_2),na.rm=T),
         Conc_sd = sd(c(Conc,Conc_2),na.rm=T),
         OD_mean = mean(c(OD,OD_2),na.rm=T),
         OD_sd = sd(c(OD,OD_2),na.rm=T)) %>%
  mutate(EST_Conc_CV = 100*(Conc_sd/Conc_mean),
         EST_Conc_CV = round(as.numeric(EST_Conc_CV),3),
         EST_OD_CV = 100*(OD_sd/OD_mean),
         EST_OD_CV = round(as.numeric(EST_OD_CV),3),
         SID = as.factor(round(as.numeric(ID),2))) %>%
  select(SID,EST_Conc_CV,EST_OD_CV) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID)) %>%
  filter(!is.na(SID)) %>%
  arrange(SID) 

#batch 2
#import files
Saliva_DHEA_CV_2 <- read_xlsx(paste0(saliva_dir,'/Raw_conc/Masterfile_TAG_Wave2dec2019batch_2019Dec26_LvD.xlsx'), sheet='DHEA final')
Saliva_TEST_CV_2 <- read_xlsx(paste0(saliva_dir,'/Raw_conc/Masterfile_TAG_Wave2dec2019batch_2019Dec26_LvD.xlsx'), sheet='Testo final')
Saliva_EST_CV_2 <- read_xlsx(paste0(saliva_dir,'/Raw_conc/Masterfile_TAG_Wave2dec2019batch_2019Dec26_LvD.xlsx'), sheet='Estradiol final')

#clean and calculate intra-assay CV for concentrations and optical densities
Saliva_DHEA_CV_2 <- Saliva_DHEA_CV_2 %>%
  rename(ID = Name,
         Conc = `[Concentration]`,
         OD = `450`) %>%
  mutate(Conc = as.numeric(Conc),
         OD = as.numeric(OD),
         Conc_2 = lead(Conc),
         OD_2 = lead(OD)) %>% 
  select(ID,Conc,Conc_2,OD,OD_2) %>%
  filter(!is.na(ID)) %>%
  rowwise() %>%
  mutate(Conc_mean = mean(c(Conc,Conc_2),na.rm=T),
         Conc_sd = sd(c(Conc,Conc_2),na.rm=T),
         OD_mean = mean(c(OD,OD_2),na.rm=T),
         OD_sd = sd(c(OD,OD_2),na.rm=T)) %>%
  mutate(DHEA_Conc_CV = 100*(Conc_sd/Conc_mean),
         DHEA_Conc_CV = round(as.numeric(DHEA_Conc_CV),3),
         DHEA_OD_CV = 100*(OD_sd/OD_mean),
         DHEA_OD_CV = round(as.numeric(DHEA_OD_CV),3),
         SID = as.factor(round(as.numeric(ID),2))) %>%
  select(SID,DHEA_Conc_CV,DHEA_OD_CV) %>%
  filter(!is.na(SID)) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID)) %>%
  arrange(SID) 

Saliva_TEST_CV_2 <- Saliva_TEST_CV_2 %>% 
  rename(ID = Name,
         Conc = `[Concentration]`,
         OD = `450`) %>%
  mutate(Conc = as.numeric(Conc),
         OD = as.numeric(OD),
         Conc_2 = lead(Conc),
         OD_2 = lead(OD)) %>% 
  select(ID,Conc,Conc_2,OD,OD_2) %>%
  filter(!is.na(ID)) %>%
  rowwise() %>%
  mutate(Conc_mean = mean(c(Conc,Conc_2),na.rm=T),
         Conc_sd = sd(c(Conc,Conc_2),na.rm=T),
         OD_mean = mean(c(OD,OD_2),na.rm=T),
         OD_sd = sd(c(OD,OD_2),na.rm=T)) %>%
  mutate(TEST_Conc_CV = 100*(Conc_sd/Conc_mean),
         TEST_Conc_CV = round(as.numeric(TEST_Conc_CV),3),
         TEST_OD_CV = 100*(OD_sd/OD_mean),
         TEST_OD_CV = round(as.numeric(TEST_OD_CV),3),
         SID = as.factor(round(as.numeric(ID),2))) %>%
  select(SID,TEST_Conc_CV,TEST_OD_CV) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID)) %>%
  filter(!is.na(SID)) %>%
  arrange(SID) 

Saliva_EST_CV_2 <- Saliva_EST_CV_2 %>% 
  rename(ID = Name,
         Conc = `[Concentration]`,
         OD = `450`) %>%
  mutate(Conc = as.numeric(Conc),
         OD = as.numeric(OD),
         Conc_2 = lead(Conc),
         OD_2 = lead(OD)) %>% 
  select(ID,Conc,Conc_2,OD,OD_2) %>%
  filter(!is.na(ID)) %>%
  rowwise() %>%
  mutate(Conc_mean = mean(c(Conc,Conc_2),na.rm=T),
         Conc_sd = sd(c(Conc,Conc_2),na.rm=T),
         OD_mean = mean(c(OD,OD_2),na.rm=T),
         OD_sd = sd(c(OD,OD_2),na.rm=T)) %>%
  mutate(EST_Conc_CV = 100*(Conc_sd/Conc_mean),
         EST_Conc_CV = round(as.numeric(EST_Conc_CV),3),
         EST_OD_CV = 100*(OD_sd/OD_mean),
         EST_OD_CV = round(as.numeric(EST_OD_CV),3),
         SID = as.factor(round(as.numeric(ID),2))) %>%
  select(SID,EST_Conc_CV,EST_OD_CV) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID)) %>%
  filter(!is.na(SID)) %>%
  arrange(SID) 

#combine two batches and create master df
Saliva_DHEA_CV <- rbind(Saliva_DHEA_CV_1,Saliva_DHEA_CV_2)
Saliva_TEST_CV <- rbind(Saliva_TEST_CV_1,Saliva_TEST_CV_2)
Saliva_EST_CV <- rbind(Saliva_EST_CV_1,Saliva_EST_CV_2)


#creater master df
Saliva_CV <- Saliva_DHEA_CV %>% full_join(.,Saliva_TEST_CV) %>% 
  full_join(.,Saliva_EST_CV) %>% arrange(SID) %>% 
  filter(SID %in% overview$SID) %>%
  mutate(ID = paste0(SID,'_',week))

#identify any further problematic IDs (i.e. appear twice in dataframe)
probIDs <- Saliva_CV$ID[duplicated(Saliva_CV$ID)]
probDF <- Saliva_CV %>% filter(ID %in% probIDs) %>% arrange(ID)

#make sure that all duplicated rows are identical
check <- duplicated(probDF) | duplicated(probDF[nrow(probDF):1, ])[nrow(probDF):1]

#remove duplicated rows
Saliva_CV <- Saliva_CV[!duplicated(Saliva_CV$ID),]

Saliva_CV_summary <- Saliva_CV %>%
  summarise(mean_DHEA_ConcCV = mean(DHEA_Conc_CV,na.rm=T),
            sd_DHEA_ConcCV = sd(DHEA_Conc_CV,na.rm=T),
            min_DHEA_ConcCV = min(DHEA_Conc_CV,na.rm=T),
            max_DHEA_ConcCV = max(DHEA_Conc_CV,na.rm=T),
            mean_DHEA_odCV = mean(DHEA_OD_CV,na.rm=T),
            sd_DHEA_odCV = sd(DHEA_OD_CV,na.rm=T),
            min_DHEA_odCV = min(DHEA_OD_CV,na.rm=T),
            max_DHEA_odCV = max(DHEA_OD_CV,na.rm=T),
            mean_TEST_ConcCV = mean(TEST_Conc_CV,na.rm=T),
            sd_TEST_ConcCV = sd(TEST_Conc_CV,na.rm=T),
            min_TEST_ConcCV = min(TEST_Conc_CV,na.rm=T),
            max_TEST_ConcCV = max(TEST_Conc_CV,na.rm=T),
            mean_TEST_odCV = mean(TEST_OD_CV,na.rm=T),
            sd_TEST_odCV = sd(TEST_OD_CV,na.rm=T),
            min_TEST_odCV = min(TEST_OD_CV,na.rm=T),
            max_TEST_odCV = max(TEST_OD_CV,na.rm=T),
            mean_EST_ConcCV = mean(EST_Conc_CV,na.rm=T),
            sd_EST_ConcCV = sd(EST_Conc_CV,na.rm=T),
            min_EST_ConcCV = min(EST_Conc_CV,na.rm=T),
            max_EST_ConcCV = max(EST_Conc_CV,na.rm=T),
            mean_EST_odCV = mean(EST_OD_CV,na.rm=T),
            sd_EST_odCV = sd(EST_OD_CV,na.rm=T),
            min_EST_odCV = min(EST_OD_CV,na.rm=T),
            max_EST_odCV = max(EST_OD_CV,na.rm=T))
```

###CALCULATE INTER-ASSAY CVS. Note (MLB) - these are the variation in the controls (high and low), which is a measure of the variation of the plates. As above, we calculate both concentrations and OD but use the OD. We report batches separately because they were run with different kits.
```{r}


#import file of highs and lows
# Batch 1
Saliva_DHEA_interCV_1 <- read_xlsx(paste0(saliva_dir,'/Raw_conc/TAG_SALIVA_W2_Master_File_Batch1.xlsx'), sheet='Control HL-D')
Saliva_TEST_interCV_1 <- read_xlsx(paste0(saliva_dir,'/Raw_conc/TAG_SALIVA_W2_Master_File_Batch1.xlsx'), sheet='Control HL-T')
Saliva_EST_interCV_1 <- read_xlsx(paste0(saliva_dir,'/Raw_conc/TAG_SALIVA_W2_Master_File_Batch1.xlsx'), sheet='Control HL-E2')
# Batch 2
Saliva_DHEA_interCV_2 <- read_xlsx(paste0(saliva_dir,'/Raw_conc/Masterfile_TAG_Wave2dec2019batch_2019Dec26_LvD.xlsx'), sheet='DHEA controls')
Saliva_TEST_interCV_2 <- read_xlsx(paste0(saliva_dir,'/Raw_conc/Masterfile_TAG_Wave2dec2019batch_2019Dec26_LvD.xlsx'), sheet='Testo controls')
Saliva_EST_interCV_2 <- read_xlsx(paste0(saliva_dir,'/Raw_conc/Masterfile_TAG_Wave2dec2019batch_2019Dec26_LvD.xlsx'), sheet='Estradiol controls')

# --- DHEA ---
# Mean of high controls within plates:
# Batch 1
dhea_high_mean1_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlH"&Saliva_DHEA_interCV_1$Plate=="1","450"]))
dhea_high_mean2_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlH"&Saliva_DHEA_interCV_1$Plate=="2","450"]))
dhea_high_mean3_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlH"&Saliva_DHEA_interCV_1$Plate=="3","450"]))
dhea_high_mean4_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlH"&Saliva_DHEA_interCV_1$Plate=="4","450"]))
dhea_high_mean5_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlH"&Saliva_DHEA_interCV_1$Plate=="5","450"]))
dhea_high_mean6_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlH"&Saliva_DHEA_interCV_1$Plate=="6","450"]))
dhea_high_mean7_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlH"&Saliva_DHEA_interCV_1$Plate=="7","450"]))
dhea_high_mean8_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlH"&Saliva_DHEA_interCV_1$Plate=="8","450"]))
dhea_high_mean9_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlH"&Saliva_DHEA_interCV_1$Plate=="9","450"]))
dhea_high_mean10_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlH"&Saliva_DHEA_interCV_1$Plate=="10","450"]))
dhea_high_mean11_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlH"&Saliva_DHEA_interCV_1$Plate=="11","450"]))
dhea_high_mean12_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlH"&Saliva_DHEA_interCV_1$Plate=="12","450"]))
dhea_high_mean13_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlH"&Saliva_DHEA_interCV_1$Plate=="13","450"]))
dhea_high_mean14_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlH"&Saliva_DHEA_interCV_1$Plate=="14","450"]))
dhea_high_mean15_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlH"&Saliva_DHEA_interCV_1$Plate=="15","450"]))
# Batch 2
dhea_high_mean1_2 <- mean(data.matrix(Saliva_DHEA_interCV_2[Saliva_DHEA_interCV_2$Well_ID=="CtrlH"&Saliva_DHEA_interCV_2$Plate=="1","450"]))
dhea_high_mean2_2 <- mean(data.matrix(Saliva_DHEA_interCV_2[Saliva_DHEA_interCV_2$Well_ID=="CtrlH"&Saliva_DHEA_interCV_2$Plate=="2","450"]))

# High controls mean of means:
# Batch 1
dhea_high_mean_1 <- mean(c(dhea_high_mean1_1, dhea_high_mean2_1, dhea_high_mean3_1, dhea_high_mean4_1, dhea_high_mean5_1, dhea_high_mean6_1, dhea_high_mean7_1, dhea_high_mean8_1, dhea_high_mean9_1, dhea_high_mean10_1, dhea_high_mean11_1, dhea_high_mean12_1, dhea_high_mean13_1, dhea_high_mean14_1, dhea_high_mean15_1))
# Batch 2
dhea_high_mean_2 <- mean(c(dhea_high_mean1_2, dhea_high_mean2_2))

# High controls SD of means:
# Batch 1
dhea_high_sd_1 <- sd(c(dhea_high_mean1_1, dhea_high_mean2_1, dhea_high_mean3_1, dhea_high_mean4_1, dhea_high_mean5_1, dhea_high_mean6_1, dhea_high_mean7_1, dhea_high_mean8_1, dhea_high_mean9_1, dhea_high_mean10_1, dhea_high_mean11_1, dhea_high_mean12_1, dhea_high_mean13_1, dhea_high_mean14_1, dhea_high_mean15_1))
# Batch 2
dhea_high_sd_2 <- sd(c(dhea_high_mean1_2, dhea_high_mean2_2))

# % CV high across plates. Note this is NOT the same as just averaging each of the individual CVs for the result 1 and 2 of each high and low control (i.e., we don't want to just average the "450 CV (%)" column from the HighsLows sheet):
# Batch 1
dhea_high_cv_1 <- (dhea_high_sd_1/dhea_high_mean_1)*100
# Batch 2
dhea_high_cv_2 <- (dhea_high_sd_2/dhea_high_mean_2)*100

# Mean of low controls within plates:
# Batch 1
dhea_low_mean1_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlL"&Saliva_DHEA_interCV_1$Plate=="1","450"]))
dhea_low_mean2_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlL"&Saliva_DHEA_interCV_1$Plate=="2","450"]))
dhea_low_mean3_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlL"&Saliva_DHEA_interCV_1$Plate=="3","450"]))
dhea_low_mean4_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlL"&Saliva_DHEA_interCV_1$Plate=="4","450"]))
dhea_low_mean5_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlL"&Saliva_DHEA_interCV_1$Plate=="5","450"]))
dhea_low_mean6_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlL"&Saliva_DHEA_interCV_1$Plate=="6","450"]))
dhea_low_mean7_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlL"&Saliva_DHEA_interCV_1$Plate=="7","450"]))
dhea_low_mean8_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlL"&Saliva_DHEA_interCV_1$Plate=="8","450"]))
dhea_low_mean9_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlL"&Saliva_DHEA_interCV_1$Plate=="9","450"]))
dhea_low_mean10_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlL"&Saliva_DHEA_interCV_1$Plate=="10","450"]))
dhea_low_mean11_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlL"&Saliva_DHEA_interCV_1$Plate=="11","450"]))
dhea_low_mean12_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlL"&Saliva_DHEA_interCV_1$Plate=="12","450"]))
dhea_low_mean13_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlL"&Saliva_DHEA_interCV_1$Plate=="13","450"]))
dhea_low_mean14_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlL"&Saliva_DHEA_interCV_1$Plate=="14","450"]))
dhea_low_mean15_1 <- mean(data.matrix(Saliva_DHEA_interCV_1[Saliva_DHEA_interCV_1$Well_ID=="CtrlL"&Saliva_DHEA_interCV_1$Plate=="15","450"]))
# Batch 2
dhea_low_mean1_2 <- mean(data.matrix(Saliva_DHEA_interCV_2[Saliva_DHEA_interCV_2$Well_ID=="CtrlL"&Saliva_DHEA_interCV_2$Plate=="1","450"]))
dhea_low_mean2_2 <- mean(data.matrix(Saliva_DHEA_interCV_2[Saliva_DHEA_interCV_2$Well_ID=="CtrlL"&Saliva_DHEA_interCV_2$Plate=="2","450"]))

# low controls mean of means:
# Batch 1
dhea_low_mean_1 <- mean(c(dhea_low_mean1_1, dhea_low_mean2_1, dhea_low_mean3_1, dhea_low_mean4_1, dhea_low_mean5_1, dhea_low_mean6_1, dhea_low_mean7_1, dhea_low_mean8_1, dhea_low_mean9_1, dhea_low_mean10_1, dhea_low_mean11_1, dhea_low_mean12_1, dhea_low_mean13_1, dhea_low_mean14_1, dhea_low_mean15_1))
#batch 2
dhea_low_mean_2 <- mean(c(dhea_low_mean1_2, dhea_low_mean2_2))

# low controls SD of means:
# Batch 1
dhea_low_sd_1 <- sd(c(dhea_low_mean1_1, dhea_low_mean2_1, dhea_low_mean3_1, dhea_low_mean4_1, dhea_low_mean5_1, dhea_low_mean6_1, dhea_low_mean7_1, dhea_low_mean8_1, dhea_low_mean9_1, dhea_low_mean10_1, dhea_low_mean11_1, dhea_low_mean12_1, dhea_low_mean13_1, dhea_low_mean14_1, dhea_low_mean15_1))
# Batch 2
dhea_low_sd_2 <- sd(c(dhea_low_mean1_2, dhea_low_mean2_2))

# % CV low across plates:
#batch 1
dhea_low_cv_1 <- (dhea_low_sd_1/dhea_low_mean_1)*100
#batch 2
dhea_low_cv_2 <- (dhea_low_sd_2/dhea_low_mean_2)*100

# AVERAGE DHEA % CV:
#batch 1
dhea_inter_cv_1 <- (dhea_high_cv_1 + dhea_low_cv_1)/2
# batch 2
dhea_inter_cv_2 <- (dhea_high_cv_2 + dhea_low_cv_2)/2

# --- TEST ---
# Mean of high controls within plates:
# Batch 1
test_high_mean1_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlH"&Saliva_TEST_interCV_1$Plate=="1","450"]))
test_high_mean2_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlH"&Saliva_TEST_interCV_1$Plate=="2","450"]))
test_high_mean3_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlH"&Saliva_TEST_interCV_1$Plate=="3","450"]))
test_high_mean4_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlH"&Saliva_TEST_interCV_1$Plate=="4","450"]))
test_high_mean5_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlH"&Saliva_TEST_interCV_1$Plate=="5","450"]))
test_high_mean6_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlH"&Saliva_TEST_interCV_1$Plate=="6","450"]))
test_high_mean7_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlH"&Saliva_TEST_interCV_1$Plate=="7","450"]))
test_high_mean8_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlH"&Saliva_TEST_interCV_1$Plate=="8","450"]))
test_high_mean9_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlH"&Saliva_TEST_interCV_1$Plate=="9","450"]))
test_high_mean10_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlH"&Saliva_TEST_interCV_1$Plate=="10","450"]))
test_high_mean11_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlH"&Saliva_TEST_interCV_1$Plate=="11","450"]))
test_high_mean12_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlH"&Saliva_TEST_interCV_1$Plate=="12","450"]))
test_high_mean13_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlH"&Saliva_TEST_interCV_1$Plate=="13","450"]))
test_high_mean14_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlH"&Saliva_TEST_interCV_1$Plate=="14","450"]))
test_high_mean15_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlH"&Saliva_TEST_interCV_1$Plate=="15","450"]))
# Batch 2
test_high_mean1_2 <- mean(data.matrix(Saliva_TEST_interCV_2[Saliva_TEST_interCV_2$Well_ID=="CtrlH"&Saliva_TEST_interCV_2$Plate=="1","450"]))
test_high_mean2_2 <- mean(data.matrix(Saliva_TEST_interCV_2[Saliva_TEST_interCV_2$Well_ID=="CtrlH"&Saliva_TEST_interCV_2$Plate=="2","450"]))

# High controls mean of means:
# Batch 1
test_high_mean_1 <- mean(c(test_high_mean1_1, test_high_mean2_1, test_high_mean3_1, test_high_mean4_1, test_high_mean5_1, test_high_mean6_1, test_high_mean7_1, test_high_mean8_1, test_high_mean9_1, test_high_mean10_1, test_high_mean11_1, test_high_mean12_1, test_high_mean13_1, test_high_mean14_1, test_high_mean15_1))
# Batch 2
test_high_mean_2 <- mean(c(test_high_mean1_2, test_high_mean2_2))

# High controls SD of means:
# Batch 1
test_high_sd_1 <- sd(c(test_high_mean1_1, test_high_mean2_1, test_high_mean3_1, test_high_mean4_1, test_high_mean5_1, test_high_mean6_1, test_high_mean7_1, test_high_mean8_1, test_high_mean9_1, test_high_mean10_1, test_high_mean11_1, test_high_mean12_1, test_high_mean13_1, test_high_mean14_1, test_high_mean15_1))
# Batch 2
test_high_sd_2 <- sd(c(test_high_mean1_2, test_high_mean2_2))

# % CV high across plates. Note this is NOT the same as just averaging each of the individual CVs for the result 1 and 2 of each high and low control (i.e., we don't want to just average the "450 CV (%)" column from the HighsLows sheet):
# Batch 1
test_high_cv_1 <- (test_high_sd_1/test_high_mean_1)*100
# Batch 2
test_high_cv_2 <- (test_high_sd_2/test_high_mean_2)*100

# Mean of low controls within plates:
# Batch 1
test_low_mean1_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlL"&Saliva_TEST_interCV_1$Plate=="1","450"]))
test_low_mean2_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlL"&Saliva_TEST_interCV_1$Plate=="2","450"]))
test_low_mean3_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlL"&Saliva_TEST_interCV_1$Plate=="3","450"]))
test_low_mean4_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlL"&Saliva_TEST_interCV_1$Plate=="4","450"]))
test_low_mean5_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlL"&Saliva_TEST_interCV_1$Plate=="5","450"]))
test_low_mean6_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlL"&Saliva_TEST_interCV_1$Plate=="6","450"]))
test_low_mean7_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlL"&Saliva_TEST_interCV_1$Plate=="7","450"]))
test_low_mean8_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlL"&Saliva_TEST_interCV_1$Plate=="8","450"]))
test_low_mean9_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlL"&Saliva_TEST_interCV_1$Plate=="9","450"]))
test_low_mean10_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlL"&Saliva_TEST_interCV_1$Plate=="10","450"]))
test_low_mean11_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlL"&Saliva_TEST_interCV_1$Plate=="11","450"]))
test_low_mean12_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlL"&Saliva_TEST_interCV_1$Plate=="12","450"]))
test_low_mean13_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlL"&Saliva_TEST_interCV_1$Plate=="13","450"]))
test_low_mean14_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlL"&Saliva_TEST_interCV_1$Plate=="14","450"]))
test_low_mean15_1 <- mean(data.matrix(Saliva_TEST_interCV_1[Saliva_TEST_interCV_1$Well_ID=="CtrlL"&Saliva_TEST_interCV_1$Plate=="15","450"]))
# Batch 2
test_low_mean1_2 <- mean(data.matrix(Saliva_TEST_interCV_2[Saliva_TEST_interCV_2$Well_ID=="CtrlL"&Saliva_TEST_interCV_2$Plate=="1","450"]))
test_low_mean2_2 <- mean(data.matrix(Saliva_TEST_interCV_2[Saliva_TEST_interCV_2$Well_ID=="CtrlL"&Saliva_TEST_interCV_2$Plate=="2","450"]))

# low controls mean of means:
# Batch 1
test_low_mean_1 <- mean(c(test_low_mean1_1, test_low_mean2_1, test_low_mean3_1, test_low_mean4_1, test_low_mean5_1, test_low_mean6_1, test_low_mean7_1, test_low_mean8_1, test_low_mean9_1, test_low_mean10_1, test_low_mean11_1, test_low_mean12_1, test_low_mean13_1, test_low_mean14_1, test_low_mean15_1))
#batch 2
test_low_mean_2 <- mean(c(test_low_mean1_2, test_low_mean2_2))

# low controls SD of means:
# Batch 1
test_low_sd_1 <- sd(c(test_low_mean1_1, test_low_mean2_1, test_low_mean3_1, test_low_mean4_1, test_low_mean5_1, test_low_mean6_1, test_low_mean7_1, test_low_mean8_1, test_low_mean9_1, test_low_mean10_1, test_low_mean11_1, test_low_mean12_1, test_low_mean13_1, test_low_mean14_1, test_low_mean15_1))
# Batch 2
test_low_sd_2 <- sd(c(test_low_mean1_2, test_low_mean2_2))

# % CV low across plates:
#batch 1
test_low_cv_1 <- (test_low_sd_1/test_low_mean_1)*100
#batch 2
test_low_cv_2 <- (test_low_sd_2/test_low_mean_2)*100

# AVERAGE DHEA % CV:
#batch 1
test_inter_cv_1 <- (test_high_cv_1 + test_low_cv_1)/2
# batch 2
test_inter_cv_2 <- (test_high_cv_2 + test_low_cv_2)/2

# --- EST ---
# Mean of high controls within plates:
# Batch 1
est_high_mean1_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlH"&Saliva_EST_interCV_1$Plate=="1","450"]))
est_high_mean2_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlH"&Saliva_EST_interCV_1$Plate=="2","450"]))
est_high_mean3_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlH"&Saliva_EST_interCV_1$Plate=="3","450"]))
est_high_mean4_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlH"&Saliva_EST_interCV_1$Plate=="4","450"]))
est_high_mean5_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlH"&Saliva_EST_interCV_1$Plate=="5","450"]))
est_high_mean6_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlH"&Saliva_EST_interCV_1$Plate=="6","450"]))
est_high_mean7_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlH"&Saliva_EST_interCV_1$Plate=="7","450"]))
est_high_mean8_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlH"&Saliva_EST_interCV_1$Plate=="8","450"]))
est_high_mean9_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlH"&Saliva_EST_interCV_1$Plate=="9","450"]))
est_high_mean10_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlH"&Saliva_EST_interCV_1$Plate=="10","450"]))
est_high_mean11_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlH"&Saliva_EST_interCV_1$Plate=="11","450"]))
est_high_mean12_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlH"&Saliva_EST_interCV_1$Plate=="12","450"]))
est_high_mean13_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlH"&Saliva_EST_interCV_1$Plate=="13","450"]))
est_high_mean14_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlH"&Saliva_EST_interCV_1$Plate=="14","450"]))
est_high_mean15_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlH"&Saliva_EST_interCV_1$Plate=="15","450"]))
# Batch 2
est_high_mean1_2 <- mean(data.matrix(Saliva_EST_interCV_2[Saliva_EST_interCV_2$Well_ID=="CtrlH"&Saliva_EST_interCV_2$Plate=="1","450"]))
est_high_mean2_2 <- mean(data.matrix(Saliva_EST_interCV_2[Saliva_EST_interCV_2$Well_ID=="CtrlH"&Saliva_EST_interCV_2$Plate=="2","450"]))

# High controls mean of means:
# Batch 1
est_high_mean_1 <- mean(c(est_high_mean1_1, est_high_mean2_1, est_high_mean3_1, est_high_mean4_1, est_high_mean5_1, est_high_mean6_1, est_high_mean7_1, est_high_mean8_1, est_high_mean9_1, est_high_mean10_1, est_high_mean11_1, est_high_mean12_1, est_high_mean13_1, est_high_mean14_1, est_high_mean15_1))
# Batch 2
est_high_mean_2 <- mean(c(est_high_mean1_2, est_high_mean2_2))

# High controls SD of means:
# Batch 1
est_high_sd_1 <- sd(c(est_high_mean1_1, est_high_mean2_1, est_high_mean3_1, est_high_mean4_1, est_high_mean5_1, est_high_mean6_1, est_high_mean7_1, est_high_mean8_1, est_high_mean9_1, est_high_mean10_1, est_high_mean11_1, est_high_mean12_1, est_high_mean13_1, est_high_mean14_1, est_high_mean15_1))
# Batch 2
est_high_sd_2 <- sd(c(est_high_mean1_2, est_high_mean2_2))

# % CV high across plates. Note this is NOT the same as just averaging each of the individual CVs for the result 1 and 2 of each high and low control (i.e., we don't want to just average the "450 CV (%)" column from the HighsLows sheet):
# Batch 1
est_high_cv_1 <- (est_high_sd_1/est_high_mean_1)*100
# Batch 2
est_high_cv_2 <- (est_high_sd_2/est_high_mean_2)*100

# Mean of low controls within plates:
# Batch 1
est_low_mean1_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlL"&Saliva_EST_interCV_1$Plate=="1","450"]))
est_low_mean2_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlL"&Saliva_EST_interCV_1$Plate=="2","450"]))
est_low_mean3_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlL"&Saliva_EST_interCV_1$Plate=="3","450"]))
est_low_mean4_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlL"&Saliva_EST_interCV_1$Plate=="4","450"]))
est_low_mean5_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlL"&Saliva_EST_interCV_1$Plate=="5","450"]))
est_low_mean6_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlL"&Saliva_EST_interCV_1$Plate=="6","450"]))
est_low_mean7_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlL"&Saliva_EST_interCV_1$Plate=="7","450"]))
est_low_mean8_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlL"&Saliva_EST_interCV_1$Plate=="8","450"]))
est_low_mean9_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlL"&Saliva_EST_interCV_1$Plate=="9","450"]))
est_low_mean10_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlL"&Saliva_EST_interCV_1$Plate=="10","450"]))
est_low_mean11_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlL"&Saliva_EST_interCV_1$Plate=="11","450"]))
est_low_mean12_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlL"&Saliva_EST_interCV_1$Plate=="12","450"]))
est_low_mean13_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlL"&Saliva_EST_interCV_1$Plate=="13","450"]))
est_low_mean14_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlL"&Saliva_EST_interCV_1$Plate=="14","450"]))
est_low_mean15_1 <- mean(data.matrix(Saliva_EST_interCV_1[Saliva_EST_interCV_1$Well_ID=="CtrlL"&Saliva_EST_interCV_1$Plate=="15","450"]))
# Batch 2
est_low_mean1_2 <- mean(data.matrix(Saliva_EST_interCV_2[Saliva_EST_interCV_2$Well_ID=="CtrlL"&Saliva_EST_interCV_2$Plate=="1","450"]))
est_low_mean2_2 <- mean(data.matrix(Saliva_EST_interCV_2[Saliva_EST_interCV_2$Well_ID=="CtrlL"&Saliva_EST_interCV_2$Plate=="2","450"]))

# low controls mean of means:
# Batch 1
est_low_mean_1 <- mean(c(est_low_mean1_1, est_low_mean2_1, est_low_mean3_1, est_low_mean4_1, est_low_mean5_1, est_low_mean6_1, est_low_mean7_1, est_low_mean8_1, est_low_mean9_1, est_low_mean10_1, est_low_mean11_1, est_low_mean12_1, est_low_mean13_1, est_low_mean14_1, est_low_mean15_1))
#batch 2
est_low_mean_2 <- mean(c(est_low_mean1_2, est_low_mean2_2))

# low controls SD of means:
# Batch 1
est_low_sd_1 <- sd(c(est_low_mean1_1, est_low_mean2_1, est_low_mean3_1, est_low_mean4_1, est_low_mean5_1, est_low_mean6_1, est_low_mean7_1, est_low_mean8_1, est_low_mean9_1, est_low_mean10_1, est_low_mean11_1, est_low_mean12_1, est_low_mean13_1, est_low_mean14_1, est_low_mean15_1))
# Batch 2
est_low_sd_2 <- sd(c(est_low_mean1_2, est_low_mean2_2))

# % CV low across plates:
#batch 1
est_low_cv_1 <- (est_low_sd_1/est_low_mean_1)*100
#batch 2
est_low_cv_2 <- (est_low_sd_2/est_low_mean_2)*100

# AVERAGE DHEA % CV:
#batch 1
est_inter_cv_1 <- (est_high_cv_1 + est_low_cv_1)/2
# batch 2
est_inter_cv_2 <- (est_high_cv_2 + est_low_cv_2)/2
```
