---
title: "TAG Cleaning Saliva Hormone Data"
author: "Nandi"
date: "28 March 2018"
output: html_document
---

```{r, include=FALSE}
#LOAD PACKAGES AND SET DIRECTORIES

packages <- c("ggplot2","tidyr","stringr","knitr","corrplot","data.table","readxl","gridExtra","dplyr", "psych","kableExtra","lavaan","xlsx")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}
lapply(packages, library, character.only = TRUE)

cas_dir <- '/Volumes/psych-cog/dsnlab/TAG/'
saliva_dir <- paste0(cas_dir,'behavior/Saliva/Wave1')
options(digits=3)

in_dir <- '~/Downloads/' #to be updated once Saliva Overview Doc is finished.
```

###IMPORT SESSION DATES AND CALCULATE INTERVALS BETWEEN SALIVA SAMPLES
```{r, include=FALSE, message=FALSE}
#import session 1 and 2 dates
session_df <- read.xlsx(paste0(cas_dir,'behavior/Demographics/Age/DOB_W1W2_SessionDates.xlsx'),1)

session_dates <- session_df %>% 
  mutate(SID=gsub("[^0-9\\.]", "", TAG_ID)) %>%
  select(SID,W1S1_Date,W1S2_Date) %>%
  mutate(sa_date=as.Date(W1S1_Date),
         sb_date=as.Date(W1S2_Date)) %>%
  filter(!is.na(SID))

#import saliva sample dates
saliva_df <- read.csv(paste0(saliva_dir,'/W1_at_home_saliva_overview.csv'))

saliva_dates <- saliva_df %>% 
  mutate(SID=gsub("[^0-9\\.]", "", subject_spit_id)) %>%
  filter(!SID=="") %>%
  select(SID,s1_doc,s2_doc,s3_doc,s4_doc,s5_doc,s6_doc,s7_doc) %>%
  mutate(s1_sdate = as.Date(s1_doc, "%d/%m/%Y"),
         s2_sdate = as.Date(s2_doc, "%d/%m/%Y"),
         s3_sdate = as.Date(s3_doc, "%d/%m/%Y"),
         s4_sdate = as.Date(s4_doc, "%d/%m/%Y"),
         s5_sdate = as.Date(s5_doc, "%d/%m/%Y"),
         s6_sdate = as.Date(s6_doc, "%d/%m/%Y"),
         s7_sdate = as.Date(s7_doc, "%d/%m/%Y")) %>%
  select(-s1_doc,-s2_doc,-s3_doc,-s4_doc,-s5_doc,-s6_doc,-s7_doc)

#combine session and saliva dates
dates <- session_dates %>% full_join(., saliva_dates) %>%
  mutate(int1 = as.numeric(difftime(s1_sdate, sa_date, units = "days")),
         int2 = as.numeric(difftime(s2_sdate, s1_sdate, units = "days")),
         int3 = as.numeric(difftime(s3_sdate, s2_sdate, units = "days")),
         int4 = as.numeric(difftime(s4_sdate, s3_sdate, units = "days")),
         int5 = as.numeric(difftime(s5_sdate, s4_sdate, units = "days")),
         int6 = as.numeric(difftime(s6_sdate, s5_sdate, units = "days")),
         int7 = as.numeric(difftime(s7_sdate, s6_sdate, units = "days")),
         totLength = as.numeric(difftime(sb_date, sa_date, units = "days"))) #totLength = time between session 1 and 2

dates <- dates %>% 
  rowwise() %>% 
  mutate(intSum = sum(int1,int2,int3,int4,int5,int6,int7,na.rm=T), #intSum = time between session 1 and final sample
         intFinal = totLength - intSum) #intFinal = time between final sample and session 2.
```

###PLOT SALIVA INTERVALS AND DETERMINE WHICH SAMPLES TO EXCLUDE
```{r, echo=FALSE, message=FALSE, warning=FALSE, results="asis", fig.height=7, fig.width=7}
dates_long <- dates %>% 
  select(SID,s1_sdate:s7_sdate,sb_date) %>% gather(., week, sample, c(s1_sdate,s2_sdate,s3_sdate,s4_sdate,s5_sdate,s6_sdate,s7_sdate,sb_date), factor_key=TRUE) %>%
  mutate(sample_bin = ifelse(!is.na(sample), 1,0)) %>%
  arrange(SID) %>%
  filter(sample_bin == 1) %>%
  group_by(SID) %>% mutate(sample_num = row_number()) %>%
  mutate(interval = as.numeric(sample - lag(sample)))

plot1 <- dates_long[1:200,]
plot2 <- dates_long[201:400,]
plot3 <- dates_long[401:600,]
plot4 <- dates_long[601:844,]

fills <- c("blue","orange","green","red","grey","yellow","purple","black")
colors <- c("grey","grey","grey","grey","grey","grey","grey","grey",NA)

fig1 <- ggplot(plot1, aes(SID, interval), group=week) +
  geom_bar(aes(fill= week), stat="identity", width=0.2) +
  geom_point(aes(colour = week), position = "stack") +
  coord_flip() +
  scale_fill_manual(values = fills) + 
  scale_colour_manual(values = colors)
fig1

fig2 <- ggplot(plot2, aes(SID, interval), group=week) +
  geom_bar(aes(fill= week), stat="identity", width=0.2) +
  geom_point(aes(colour = week), position = "stack") +
  coord_flip() +
  scale_fill_manual(values = fills) + 
  scale_colour_manual(values = colors)
fig2

fig3 <- ggplot(plot3, aes(SID, interval), group=week) +
  geom_bar(aes(fill= week), stat="identity", width=0.2) +
  geom_point(aes(colour = week), position = "stack") +
  coord_flip() +
  scale_fill_manual(values = fills) + 
  scale_colour_manual(values = colors)
fig3

fig4 <- ggplot(plot4, aes(SID, interval), group=week) +
  geom_bar(aes(fill= week), stat="identity", width=0.2) +
  geom_point(aes(colour = week), position = "stack") +
  coord_flip() +
  scale_fill_manual(values = fills) + 
  scale_colour_manual(values = colors)
fig4

#exclusions
funky_dates = c("045","067","266")
missing_dates = c("028","070","071")
```

###PLOT SALIVA INTERVALS AFTER EXCLUSIONS
```{r, echo=FALSE, message=FALSE, warning=FALSE, results="asis", fig.height=10, fig.width=7}
dates_long <- dates_long %>% arrange(SID) %>% 
  filter(!SID %in% paste0(missing_dates)) %>% 
  filter(!SID %in% paste0(funky_dates)) %>%
  filter(!is.na(sample)) %>%
  select(-sample_num,-interval) %>%
  group_by(SID) %>% mutate(sample_num = row_number()) %>%
  mutate(interval = as.numeric(sample - lag(sample)))

fills <- c("blue","orange","green","red","grey","yellow","purple","black")
colors <- c("grey","grey","grey","grey","grey","grey","grey","grey",NA)

fig <- ggplot(dates_long, aes(SID, interval), group=week) +
  geom_bar(aes(fill= week), stat="identity", width=0.2) +
  geom_point(aes(colour = week), position = "stack") +
  coord_flip() +
  scale_fill_manual(values = fills) + 
  scale_colour_manual(values = colors)
fig
```

###CALCULATE N SAMPLES
```{r, echo=FALSE, message=FALSE, warning=FALSE, results="asis", fig.height=7, fig.width=7}
summaryN <- dates_long %>% 
  filter(!week == "sb_date") %>%
  select(-interval) %>% group_by(SID) %>%
  summarise(N = n())

barplot_samples <- ggplot(summaryN, aes(N)) +
    geom_bar() + 
    scale_x_continuous(limits = c(0, 8), breaks = seq(0,8,by=1))+
    xlab("# Samples")+
    scale_y_continuous(limits = c(0, 120), breaks = seq(0,120,by=20))+
    theme_bw() +
    theme_minimal(base_size = 12, base_family = "Arial") +
    theme(axis.line = element_line(colour = "black"),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank(),
          legend.position="none")
barplot_samples
