---
title: "TAG Cleaning Hair Hormone Data"
author: "Nandi"
date: "28 March 2018"
output: html_document
---

```{r, include=FALSE}
#LOAD PACKAGES AND SET DIRECTORIES

packages <- c("ggplot2","tidyr","stringr","knitr","corrplot","data.table","readxl","gridExtra","dplyr", "psych","kableExtra","lavaan","xlsx","DescTools")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}
lapply(packages, library, character.only = TRUE)

cas_dir <- '/Volumes/psych-cog/dsnlab/TAG/'
hair_dir <- paste0(cas_dir,'behavior/Puberty/Hair/Wave1')
options(digits=3)
```

###IMPORT TAG OVERVIEW DOC FROM CAS
```{r, include = F}
overview <- read.xlsx(paste0(cas_dir,'behavior/Overview/Overview_Withdrawn_Completed/TAG_Overview_Doc.xlsx'),1)
overview <- overview[,c("TAG_ID","W1S2_Completed","Withdrawn_W1","Exclusionary_Withdrawl")]

#removing everyone who withdrew at W1 (exclusionary withdrawals)
overview <- overview %>% 
  rename(SID = TAG_ID) %>%
  replace_na(list(Withdrawn_W1 = 0)) %>%
  replace_na(list(Exclusionary_Withdrawl = 0)) %>% 
  arrange(Exclusionary_Withdrawl) %>% 
  mutate(SID=gsub("[^0-9\\.]", "", SID)) %>%
  filter(Exclusionary_Withdrawl==0) %>%
  filter(Withdrawn_W1==0)
```

###IMPORT "FINAL" HAIR CONCENTRATIONS
```{r, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
###IMPORT & CLEAN CONCENTRATIONS 
#import dataframe for each hormone, create SID as 3 digit numeric factor (i.e. "001"), combine all three hormones in one dataframe.

#round 1 of assays
Hair_DHEA1 <- read_xlsx(paste0(hair_dir,'/TAG_W1_Hair_Master_File.xlsx'), sheet=2)
Hair_TEST1 <- read_xlsx(paste0(hair_dir,'/TAG_W1_Hair_Master_File.xlsx'), sheet=5)
Hair_EST1 <- read_xlsx(paste0(hair_dir,'/TAG_W1_Hair_Master_File.xlsx'), sheet=8)

#round 2 of assays
Hair_DHEA2 <- read_xlsx(paste0(hair_dir,'/TAG_W1_Hair_2nd_Run_Master_Sheet.xlsx'), sheet=2)
Hair_TEST2 <- read_xlsx(paste0(hair_dir,'/TAG_W1_Hair_2nd_Run_Master_Sheet.xlsx'), sheet=5)
Hair_EST2 <- read_xlsx(paste0(hair_dir,'/TAG_W1_Hair_2nd_Run_Master_Sheet.xlsx'), sheet=8)

#clean up formatting and merge two DFs
Hair_DHEA1 <- Hair_DHEA1 %>% 
  mutate(SID = as.factor(round(as.numeric(ID),2)),
         hair_DHEA = round(as.numeric(Concentration),3),
         hair_DHEA_pgmg = round(as.numeric(`Concentration in pg/mg`),3)) %>%
  replace_na(list(hair_DHEA_pgmg = NA)) %>%
  select(SID,hair_DHEA_pgmg) %>%
  filter(!is.na(SID)) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  select(-week) %>%
  mutate(SID = as.factor(SID)) %>%
  mutate(SID = str_pad(SID, 3, pad = "0"))

Hair_DHEA2 <- Hair_DHEA2 %>% 
  separate(ID, into =c("ID","junk")) %>%
  mutate(SID = as.factor(round(as.numeric(ID),2)),
         hair_DHEA = round(as.numeric(Concentration),3),
         hair_DHEA_pgmg = round(as.numeric(`Concentration in pg/mg`),3)) %>%
  select(SID,hair_DHEA_pgmg) %>%
  filter(!is.na(SID)) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  select(-week) %>%
  mutate(SID = as.factor(SID)) %>%
  mutate(SID = str_pad(SID, 3, pad = "0"))

Hair_DHEA <- Hair_DHEA1 %>% rbind(Hair_DHEA2)
  
Hair_TEST1 <- Hair_TEST1 %>% 
  mutate(SID = as.factor(round(as.numeric(ID),2)),
         hair_TEST = round(as.numeric(Concentration),3),
         hair_TEST_pgmg = round(as.numeric(`Concentration in pg/mg`),3)) %>%
  mutate(hair_TEST = ifelse(SID==101.1,600,hair_TEST),
         hair_TEST_pgmg = ifelse(SID==101.1,(600/25),hair_TEST_pgmg)) %>%  
  select(SID,hair_TEST_pgmg) %>%
  filter(!is.na(SID)) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  select(-week) %>%
  mutate(SID = as.factor(SID)) %>%
  mutate(SID = str_pad(SID, 3, pad = "0"))

Hair_TEST2 <- Hair_TEST2 %>% 
  separate(ID, into =c("ID","junk")) %>%
  mutate(SID = as.factor(round(as.numeric(ID),2)),
         hair_TEST = round(as.numeric(Concentration),3),
         hair_TEST_pgmg = round(as.numeric(`Concentration in pg/mg`),3)) %>%
  mutate(hair_TEST = ifelse(SID==110,600,hair_TEST),
         hair_TEST_pgmg = ifelse(SID==110,(600/25),hair_TEST_pgmg)) %>%  
  select(SID,hair_TEST_pgmg) %>%
  filter(!is.na(SID)) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  select(-week) %>%
  mutate(SID = as.factor(SID)) %>%
  mutate(SID = str_pad(SID, 3, pad = "0"))

Hair_TEST <- Hair_TEST1 %>% rbind(Hair_TEST2)

Hair_EST1 <- Hair_EST1 %>% 
  separate(ID, into =c("ID","junk")) %>%
  mutate(SID = as.factor(round(as.numeric(ID),2)),
         hair_EST = round(as.numeric(`Adjusted Concentration`),3),
         hair_EST_pgug = round(as.numeric(`Concentration in pg/ug`),3)) %>%
  replace_na(list(hair_EST_pgug = NA)) %>%
  select(SID,hair_EST_pgug) %>%
  filter(!is.na(SID)) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  select(-week) %>%
  mutate(SID = as.factor(SID)) %>%
  mutate(SID = str_pad(SID, 3, pad = "0"))

Hair_EST2 <- Hair_EST2 %>% 
  mutate(SID = as.factor(round(as.numeric(ID),2)),
         hair_EST = round(as.numeric(`Adjusted Concentration`),3),
         hair_EST_pgug = round(as.numeric(`Concentration in pg/ug`),3)) %>%
  replace_na(list(hair_EST_pgug = NA)) %>%
  select(SID,hair_EST_pgug) %>%
  filter(!is.na(SID)) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  select(-week) %>%
  mutate(SID = as.factor(SID)) %>%
  mutate(SID = str_pad(SID, 3, pad = "0"))

Hair_EST <- Hair_EST1 %>% rbind(Hair_EST2)

Hair <- Hair_EST %>% full_join(.,Hair_TEST) %>% full_join(.,Hair_DHEA) %>%
  mutate(SID = as.factor(SID)) %>% arrange(SID) %>%
  filter(SID %in% overview$SID)
```

###NO HAIR RE-RUNS TO CHECK

###FINAL CONCENTRATIONS & DISTRIBUTIONS
```{r, echo=FALSE, message=FALSE, warning=FALSE, results="asis", fig.height=7, fig.width=15}
Hair_long <- Hair %>% select(SID,contains("pg")) %>% gather(., hormone, concentration, c(hair_DHEA_pgmg,hair_TEST_pgmg,hair_EST_pgug), factor_key=TRUE)

Hair_long <- Hair_long %>%
  mutate(concentration = as.numeric(concentration))

#plot distributions
Hair_plot <- Hair_long %>% 
  ggplot(aes(x = concentration)) +
  geom_histogram(color="black",fill="white") +
  facet_wrap(~ hormone, scales="free")

Hair_plot

#table of distributions
Hair_distributions <- Hair_long %>% group_by(hormone) %>%
  summarise(mean = mean(concentration,na.rm=T),
            sd = sd(concentration,na.rm=T),
            min = min(concentration,na.rm=T),
            max = max(concentration,na.rm=T),
            skew = skew(concentration,na.rm=T),
            kurtosis = kurtosi(concentration,na.rm=T))

###LOG TRANSFORMATION GIVEN SKEW & KURTOSIS###
#NOTE: from here on, "concentration_ln" is log transformed
Hair_long <- Hair_long %>% group_by(hormone) %>%
  mutate(concentration_orig = concentration,
         concentration_ln = log(concentration + 4))

#plot transformed concentrations
Hair_plot <- Hair_long %>% 
  ggplot(aes(x = concentration_ln)) +
  geom_histogram(color="black",fill="white") +
  facet_wrap(~ hormone, scales="free")
Hair_plot
```

###WINSORIZE OUTLIERS
```{r}
#this section provided by MB and Johnny
#set outlier limits for winsoring

TEST_up_limit <- (mean(subset(Hair_long, hormone == "hair_TEST_pgmg")$concentration_ln,na.rm=T) + 
  3*(sd(subset(Hair_long, hormone == "hair_TEST_pgmg")$concentration_ln,na.rm=T)))
TEST_lo_limit <-  (mean(subset(Hair_long, hormone == "hair_TEST_pgmg")$concentration_ln,na.rm=T) - 
                     3*(sd(subset(Hair_long, hormone == "hair_TEST_pgmg")$concentration_ln,na.rm=T)))
TEST_lo_limit <- ifelse(TEST_lo_limit<0, 0, TEST_lo_limit)

EST_up_limit <- (mean(subset(Hair_long, hormone == "hair_EST_pgug")$concentration_ln,na.rm=T) + 
                    3*(sd(subset(Hair_long, hormone == "hair_EST_pgug")$concentration_ln,na.rm=T)))
EST_lo_limit <-  (mean(subset(Hair_long, hormone == "hair_EST_pgug")$concentration_ln,na.rm=T) - 
                     3*(sd(subset(Hair_long, hormone == "hair_EST_pgug")$concentration_ln,na.rm=T)))
EST_lo_limit <- ifelse(EST_lo_limit<0, 0, EST_lo_limit)

DHEA_up_limit <- (mean(subset(Hair_long, hormone == "hair_DHEA_pgmg")$concentration_ln,na.rm=T) + 
                   3*(sd(subset(Hair_long, hormone == "hair_DHEA_pgmg")$concentration_ln,na.rm=T)))
DHEA_lo_limit <-  (mean(subset(Hair_long, hormone == "hair_DHEA_pgmg")$concentration_ln,na.rm=T) - 
                    3*(sd(subset(Hair_long, hormone == "hair_DHEA_pgmg")$concentration_ln,na.rm=T)))
DHEA_lo_limit <- ifelse(DHEA_lo_limit<0, 0, DHEA_lo_limit)

#Prep data & plot outliers
Hair_EST <- Hair_long %>% filter(hormone=="hair_EST_pgug")
Hair_TEST <- Hair_long %>% filter(hormone=="hair_TEST_pgmg")
Hair_DHEA <- Hair_long %>% filter(hormone=="hair_DHEA_pgmg")

hist(Hair_EST$concentration_ln, main="", xlab="EST")
abline(v=EST_up_limit,col="red")
hist(Hair_TEST$concentration_ln, main="", xlab="TEST")
abline(v=TEST_up_limit,col="red")
hist(Hair_DHEA$concentration_ln, main="", xlab="DHEA")
abline(v=DHEA_up_limit,col="red")

# Winsorize data with min and max values
Hair_EST$concentration_ln_w <- Winsorize(Hair_EST$concentration_ln, minval = EST_lo_limit, maxval = EST_up_limit, na.rm = TRUE)
Hair_TEST$concentration_ln_w <- Winsorize(Hair_TEST$concentration_ln, minval = TEST_lo_limit, maxval = TEST_up_limit, na.rm = TRUE)
Hair_DHEA$concentration_ln_w <- Winsorize(Hair_DHEA$concentration_ln, minval = DHEA_lo_limit, maxval = DHEA_up_limit, na.rm = TRUE)

# Code from here to end of chunk thank you to Johnny

# identify the points that were changed to the min and max
# (aka those points that are equal to the min and max but weren't before)

cleaned_EST <- na.omit(Hair_EST$concentration_ln_w)
original_EST <- na.omit(Hair_EST$concentration_ln)

min_pts_EST <- which(cleaned_EST == min(cleaned_EST) & original_EST != min(cleaned_EST))
max_pts_EST <- which(cleaned_EST == max(cleaned_EST) & original_EST != max(cleaned_EST))

cleaned_TEST <- na.omit(Hair_TEST$concentration_ln_w)
original_TEST <- na.omit(Hair_TEST$concentration_ln)

min_pts_TEST <- which(cleaned_TEST == min(cleaned_TEST) & original_TEST != min(cleaned_TEST))
max_pts_TEST <- which(cleaned_TEST == max(cleaned_TEST) & original_TEST != max(cleaned_TEST))

cleaned_DHEA <- na.omit(Hair_DHEA$concentration_ln_w)
original_DHEA <- na.omit(Hair_DHEA$concentration_ln)

min_pts_DHEA <- which(cleaned_DHEA == min(cleaned_DHEA) & original_DHEA != min(cleaned_DHEA))
max_pts_DHEA <- which(cleaned_DHEA == max(cleaned_DHEA) & original_DHEA != max(cleaned_DHEA))

# NOTE: Rank-preserving changes below are only done for max TEST values. The rest either didn't have any outliers or only had one outlier.

# then rank them
# rank will give you smallest -> largest ranks, 
# so to get least-> most outlierish we just reverse min_ranks
max_ranks_TEST <- rank(original_TEST[max_pts_TEST])

# now you can replace them with whatever you want
increment=0.05

rank_preserving_TEST <- cleaned_TEST
rank_preserving_TEST[max_pts_TEST] <- rank_preserving_TEST[max_pts_TEST]+(increment * max_ranks_TEST)

# check out what we did
outliers_TEST <- c(min_pts_TEST, max_pts_TEST)
comparison_TEST <- cbind(original_TEST[outliers_TEST],
                         cleaned_TEST[outliers_TEST],
                         rank_preserving_TEST[outliers_TEST])

# reorder by the first column
comparison_TEST <- comparison_TEST[order(comparison_TEST[,1]),]
comparison_TEST <- as.data.frame(comparison_TEST) %>% rename(concentration_ln=V1,
                                                             concentration_ln_w=V2,
                                                             concentration_ln_w_r=V3)
comparison_TEST <- comparison_TEST[!duplicated(comparison_TEST), ]

Hair_long <- Hair_long %>% left_join(.,comparison_TEST,by="concentration_ln") %>%
  mutate(concentration_ln = ifelse(!is.na(concentration_ln_w_r),concentration_ln_w_r,concentration_ln)) %>%
  mutate(concentration_ln = ifelse((hormone=="hair_DHEA_pgmg" & (concentration_ln > DHEA_up_limit)),DHEA_up_limit,concentration_ln)) %>%
  mutate(concentration_ln = ifelse((hormone=="hair_EST_pgug" & (concentration_ln > EST_up_limit)),EST_up_limit,concentration_ln)) %>%
  select(-concentration_ln_w_r,-concentration_ln_w,-concentration)
```

###CHECK FINAL SKEW AND KURTOSIS AFTER WINSORIZING
```{r}
skew(subset(Hair_long,hormone=="hair_DHEA_pgmg")$concentration_ln,na.rm=T)
skew(subset(Hair_long,hormone=="hair_TEST_pgmg")$concentration_ln,na.rm=T)
skew(subset(Hair_long,hormone=="hair_EST_pgug")$concentration_ln,na.rm=T)
kurtosi(subset(Hair_long,hormone=="hair_DHEA_pgmg")$concentration_ln,na.rm=T)
kurtosi(subset(Hair_long,hormone=="hair_TEST_pgmg")$concentration_ln,na.rm=T)
kurtosi(subset(Hair_long,hormone=="hair_EST_pgug")$concentration_ln,na.rm=T)

#plot final concentrations
Hair_plot <- Hair_long %>% 
  ggplot(aes(x = concentration_ln)) +
  geom_histogram(color="black",fill="white") +
  facet_wrap(~ hormone, scales="free")
Hair_plot
```

###SUMMARY
```{r, include=FALSE}
#Samples sent
cat('No of Subjects: ') 
cat(length(unique(Hair$SID)))

#Samples assayed
Hair_assayed <- Hair_long %>% 
  mutate(concentration_ln = as.numeric(concentration_ln)) %>%
  group_by(SID,hormone) %>% 
  summarise(Assayed = sum(!is.na(concentration_ln)),
            notAssayed = sum(is.na(concentration_ln))) %>%
  group_by(hormone) %>% 
  summarise(Assayed = sum(Assayed),
            notAssayed = sum(notAssayed))

####Summary of samples
kable(Hair_assayed, "html", align='c') %>%
kable_styling(full_width = F, position = "left", font_size = 12)
```

###CONTROL FOR CONFOUNDS
```{r}
confounds <- read.csv(paste0(hair_dir,'/TAG_W1_Hair_questionnaire_coded.csv'))
confounds$SID <- as.factor(confounds$SID)
Hair_long <- Hair_long %>% left_join(.,confounds) %>%
  mutate(colour_6mn = as.factor(colour_6mn),
         perm_6mn = as.factor(perm_6mn),
         curly = as.factor(curly),
         sweat = as.numeric(sweat))

summary(lm(concentration_ln ~ colour_6mn, data = subset(Hair_long,Hair_long$hormone=="hair_DHEA_pgmg")))
summary(lm(concentration_ln ~ colour_6mn, data = subset(Hair_long,Hair_long$hormone=="hair_TEST_pgmg")))
summary(lm(concentration_ln ~ colour_6mn, data = subset(Hair_long,Hair_long$hormone=="hair_EST_pgug")))

summary(lm(concentration_ln ~ perm_6mn, data = subset(Hair_long,Hair_long$hormone=="hair_DHEA_pgmg")))
summary(lm(concentration_ln ~ perm_6mn, data = subset(Hair_long,Hair_long$hormone=="hair_TEST_pgmg")))
summary(lm(concentration_ln ~ perm_6mn, data = subset(Hair_long,Hair_long$hormone=="hair_EST_pgug")))

summary(lm(concentration_ln ~ curly, data = subset(Hair_long,Hair_long$hormone=="hair_DHEA_pgmg")))
summary(lm(concentration_ln ~ curly, data = subset(Hair_long,Hair_long$hormone=="hair_TEST_pgmg")))
summary(lm(concentration_ln ~ curly, data = subset(Hair_long,Hair_long$hormone=="hair_EST_pgug")))

summary(lm(concentration_ln ~ sweat, data = subset(Hair_long,Hair_long$hormone=="hair_DHEA_pgmg")))
summary(lm(concentration_ln ~ sweat, data = subset(Hair_long,Hair_long$hormone=="hair_TEST_pgmg")))
summary(lm(concentration_ln ~ sweat, data = subset(Hair_long,Hair_long$hormone=="hair_EST_pgug")))

#no effects of coloring or perming hair, or curlyr hair. did not use the "hair treatment" info as girls seem to have interpreted this as straightening or curling their hair on occassion.
```

###SAVE HAIR CONCENTRATIONS
```{r}
Hair_long <- Hair_long %>% select(-colour,-colour_6mn,-perm_6mn,-curly,-sweat)
write.csv(Hair_long,paste0(hair_dir,'/TAG_W1_Hair_processed.csv'),row.names=F)
save.image(paste0(hair_dir,"/TAG_W1_Hair.RData"))
```


###--------------------------------------TBC---------------------------------------###
###IMPORT HAIR CVs
```{r, include=FALSE}
Hair_DHEA_CV_1 <- read_xlsx(paste0(hair_dir,'/TAG_W1_HAIR_Master_File.xlsx'), sheet=1)
Hair_TEST_CV_1 <- read_xlsx(paste0(hair_dir,'/TAG_W1_HAIR_Master_File.xlsx'), sheet=4)
Hair_EST_CV_1 <- read_xlsx(paste0(hair_dir,'/TAG_W1_HAIR_Master_File.xlsx'), sheet=7)

Hair_DHEA_CV_1 <- Hair_DHEA_CV_1 %>% 
  rename(ID = Name,
         Conc = `[Concentration]`,
         OD = `450`) %>%
  mutate(Conc = as.numeric(Conc),
         OD = as.numeric(OD),
         Conc_2 = lead(Conc),
         OD_2 = lead(OD)) %>% 
  select(ID,Conc,Conc_2,OD,OD_2) %>%
  filter(!is.na(ID)) %>%
  rowwise() %>%
  mutate(Conc_mean = mean(c(Conc,Conc_2),na.rm=T),
         Conc_sd = sd(c(Conc,Conc_2),na.rm=T),
         OD_mean = mean(c(OD,OD_2),na.rm=T),
         OD_sd = sd(c(OD,OD_2),na.rm=T)) %>%
  mutate(DHEA_Conc_CV = 100*(Conc_sd/Conc_mean),
         DHEA_Conc_CV = round(as.numeric(DHEA_Conc_CV),3),
         DHEA_OD_CV = 100*(OD_sd/OD_mean),
         DHEA_OD_CV = round(as.numeric(DHEA_OD_CV),3),
         SID = as.factor(round(as.numeric(ID),2))) %>%
  select(SID,DHEA_Conc_CV,DHEA_OD_CV) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID)) %>%
  select(-week) %>%
  filter(!is.na(SID)) %>%
  arrange(SID) 
  
Hair_TEST_CV_1 <- Hair_TEST_CV_1 %>% 
  rename(ID = Name,
         Conc = `[Concentration]`,
         OD = `450`) %>%
  mutate(Conc = as.numeric(Conc),
         OD = as.numeric(OD),
         Conc_2 = lead(Conc),
         OD_2 = lead(OD)) %>% 
  select(ID,Conc,Conc_2,OD,OD_2) %>%
  filter(!is.na(ID)) %>%
  rowwise() %>%
  mutate(Conc_mean = mean(c(Conc,Conc_2),na.rm=T),
         Conc_sd = sd(c(Conc,Conc_2),na.rm=T),
         OD_mean = mean(c(OD,OD_2),na.rm=T),
         OD_sd = sd(c(OD,OD_2),na.rm=T)) %>%
  mutate(TEST_Conc_CV = 100*(Conc_sd/Conc_mean),
         TEST_Conc_CV = round(as.numeric(TEST_Conc_CV),3),
         TEST_OD_CV = 100*(OD_sd/OD_mean),
         TEST_OD_CV = round(as.numeric(TEST_OD_CV),3),
         SID = as.factor(round(as.numeric(ID),2))) %>%
  select(SID,TEST_Conc_CV,TEST_OD_CV) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID)) %>%
  select(-week) %>%
  filter(!is.na(SID)) %>%
  arrange(SID) 

Hair_EST_CV_1 <- Hair_EST_CV_1 %>% 
  rename(ID = Name,
         Conc = `[Concentration]`,
         OD = `450`) %>%
  mutate(Conc = as.numeric(Conc),
         OD = as.numeric(OD),
         Conc_2 = lead(Conc),
         OD_2 = lead(OD)) %>% 
  select(ID,Conc,Conc_2,OD,OD_2) %>%
  filter(!is.na(ID)) %>%
  rowwise() %>%
  mutate(Conc_mean = mean(c(Conc,Conc_2),na.rm=T),
         Conc_sd = sd(c(Conc,Conc_2),na.rm=T),
         OD_mean = mean(c(OD,OD_2),na.rm=T),
         OD_sd = sd(c(OD,OD_2),na.rm=T)) %>%
  mutate(EST_Conc_CV = 100*(Conc_sd/Conc_mean),
         EST_Conc_CV = round(as.numeric(EST_Conc_CV),3),
         EST_OD_CV = 100*(OD_sd/OD_mean),
         EST_OD_CV = round(as.numeric(EST_OD_CV),3),
         SID = as.factor(round(as.numeric(ID),2))) %>%
  select(SID,EST_Conc_CV,EST_OD_CV) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID)) %>%
  select(-week) %>%
  filter(!is.na(SID)) %>%
  arrange(SID) 

Hair_DHEA_CV_2 <- read_xlsx(paste0(hair_dir,'/TAG_W1_Hair_2nd_Run_Master_Sheet.xlsx'), sheet=1)
Hair_TEST_CV_2 <- read_xlsx(paste0(hair_dir,'/TAG_W1_Hair_2nd_Run_Master_Sheet.xlsx'), sheet=4)
Hair_EST_CV_2 <- read_xlsx(paste0(hair_dir,'/TAG_W1_Hair_2nd_Run_Master_Sheet.xlsx'), sheet=7)

Hair_DHEA_CV_2 <- Hair_DHEA_CV_2 %>% 
  rename(ID = Name,
         Conc = `[Concentration]`,
         OD = `450`) %>%
  mutate(Conc = as.numeric(Conc),
         OD = as.numeric(OD),
         Conc_2 = lead(Conc),
         OD_2 = lead(OD)) %>% 
  select(ID,Conc,Conc_2,OD,OD_2) %>%
  filter(!is.na(ID)) %>%
  rowwise() %>%
  mutate(Conc_mean = mean(c(Conc,Conc_2),na.rm=T),
         Conc_sd = sd(c(Conc,Conc_2),na.rm=T),
         OD_mean = mean(c(OD,OD_2),na.rm=T),
         OD_sd = sd(c(OD,OD_2),na.rm=T)) %>%
  mutate(DHEA_Conc_CV = 100*(Conc_sd/Conc_mean),
         DHEA_Conc_CV = round(as.numeric(DHEA_Conc_CV),3),
         DHEA_OD_CV = 100*(OD_sd/OD_mean),
         DHEA_OD_CV = round(as.numeric(DHEA_OD_CV),3)) %>%
  separate(ID,into=c("SID","week")) %>%
  mutate(SID = as.factor(round(as.numeric(SID),2))) %>%
  select(SID,DHEA_Conc_CV,DHEA_OD_CV) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID)) %>%
  select(-week) %>%
  filter(!is.na(SID)) %>%
  filter(!SID %in% c("024","179","202","077")) %>%
  arrange(SID) 
  
Hair_TEST_CV_2 <- Hair_TEST_CV_2 %>% 
  rename(ID = Name,
         Conc = `[Concentration]`,
         OD = `450`) %>%
  mutate(Conc = as.numeric(Conc),
         OD = as.numeric(OD),
         Conc_2 = lead(Conc),
         OD_2 = lead(OD)) %>% 
  select(ID,Conc,Conc_2,OD,OD_2) %>%
  filter(!is.na(ID)) %>%
  rowwise() %>%
  mutate(Conc_mean = mean(c(Conc,Conc_2),na.rm=T),
         Conc_sd = sd(c(Conc,Conc_2),na.rm=T),
         OD_mean = mean(c(OD,OD_2),na.rm=T),
         OD_sd = sd(c(OD,OD_2),na.rm=T)) %>%
  mutate(TEST_Conc_CV = 100*(Conc_sd/Conc_mean),
         TEST_Conc_CV = round(as.numeric(TEST_Conc_CV),3),
         TEST_OD_CV = 100*(OD_sd/OD_mean),
         TEST_OD_CV = round(as.numeric(TEST_OD_CV),3)) %>%
  separate(ID,into=c("SID","week")) %>%
  mutate(SID = as.factor(round(as.numeric(SID),2))) %>%
  select(SID,TEST_Conc_CV,TEST_OD_CV) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID)) %>%
  select(-week) %>%
  filter(!is.na(SID)) %>%
  filter(!SID %in% c("024","179","202","077")) %>%
  arrange(SID) 
  
Hair_EST_CV_2 <- Hair_EST_CV_2 %>% 
  rename(ID = Name,
         Conc = `[Concentration]`,
         OD = `450`) %>%
  mutate(Conc = as.numeric(Conc),
         OD = as.numeric(OD),
         Conc_2 = lead(Conc),
         OD_2 = lead(OD)) %>% 
  select(ID,Conc,Conc_2,OD,OD_2) %>%
  filter(!is.na(ID)) %>%
  rowwise() %>%
  mutate(Conc_mean = mean(c(Conc,Conc_2),na.rm=T),
         Conc_sd = sd(c(Conc,Conc_2),na.rm=T),
         OD_mean = mean(c(OD,OD_2),na.rm=T),
         OD_sd = sd(c(OD,OD_2),na.rm=T)) %>%
  mutate(EST_Conc_CV = 100*(Conc_sd/Conc_mean),
         EST_Conc_CV = round(as.numeric(EST_Conc_CV),3),
         EST_OD_CV = 100*(OD_sd/OD_mean),
         EST_OD_CV = round(as.numeric(EST_OD_CV),3),
         SID = as.factor(round(as.numeric(ID),2))) %>%
  select(SID,EST_Conc_CV,EST_OD_CV) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID)) %>%
  select(-week) %>%
  filter(!is.na(SID)) %>%
  arrange(SID) 

Hair_DHEA_CV <- rbind(Hair_DHEA_CV_1,Hair_DHEA_CV_2)
Hair_TEST_CV <- rbind(Hair_TEST_CV_1,Hair_TEST_CV_2)
Hair_EST_CV <- rbind(Hair_EST_CV_1,Hair_EST_CV_2)

Hair_CV <- Hair_DHEA_CV %>% full_join(.,Hair_TEST_CV) %>% 
  full_join(.,Hair_EST_CV) %>% arrange(SID) %>% 
  filter(SID %in% overview$SID)
```

###DISTRIBUTIONS OF ICV
```{r, echo=FALSE, message=FALSE, warning=FALSE, results="asis", fig.height=7, fig.width=15}
CVplot <- Hair_CV %>% select(SID, DHEA_CV, TEST_CV, EST_CV) %>%
  gather(-SID, key = "var", value = "value") %>% 
  ggplot(aes(x = value)) +
  geom_histogram(color="black",fill="white") +
  facet_wrap(~ var,scales="free")

CVplot

#if we want to see how many kids have CV > 20...
DHEA_CV_exc <- Hair_CV %>% filter(DHEA_CV > 20) %>% select(SID)
TEST_CV_exc <- Hair_CV %>% filter(TEST_CV > 20) %>% select(SID)
EST_CV_exc <- Hair_CV %>% filter(EST_CV > 20) %>% select(SID)
```

###DISTRIBUTIONS OF 450 ICV
```{r, echo=FALSE, message=FALSE, warning=FALSE, results="asis", fig.height=7, fig.width=15}

CV_450_plot <- Hair_CV %>% select(SID, DHEA_450CV, TEST_450CV, EST_450CV) %>%
  gather(-SID, key = "var", value = "value") %>% 
  ggplot(aes(x = value)) +
  geom_histogram(color="black",fill="white") +
  facet_wrap(~ var,scales="free")

CV_450_plot

#if we want to see how many kids have CV > 30...
DHEA_450CV_exc <- Hair_CV %>% filter(DHEA_450CV > 20) %>% select(SID)
TEST_450CV_exc <- Hair_CV %>% filter(TEST_450CV > 20) %>% select(SID)
EST_450CV_exc <- Hair_CV %>% filter(EST_450CV > 20) %>% select(SID)
```


```{r, include=FALSE}
####Checking for outliers (of mean of duplicates)

hist(Hair$hair_DHEA_pgmg, main="", xlab="DHEA")
abline(v=100,col="red")
writeLines("\n")
writeLines("\n")
hist(Hair$hair_TEST_pgmg, main="", xlab="TEST")
abline(v=10,col="red")
writeLines("\n")
writeLines("\n")
hist(Hair$hair_EST_pgug, main="", xlab="EST")
abline(v=100,col="red")
writeLines("\n")

#calculate number of outliers based on visual inspection cut-offs
Hair <- Hair %>%
  mutate(hair_DHEAout = if_else(hair_DHEA_pgmg > 100, 1, 0),
         hair_TESTout = if_else(hair_TEST_pgmg > 10, 1, 0),
         hair_ESTout = if_else(hair_EST_pgug > 100, 1, 0))

cat("\n*Number of outlier samples*")
writeLines("\n")
cat("\nDHEA: ")
cat(summary(as.factor(Hair$hair_DHEAout))[2])
writeLines("\n")
writeLines("\n")
cat("\nTEST: ")
cat(summary(as.factor(Hair$hair_TESTout))[2])
writeLines("\n")
cat("\nEST: ")
cat(summary(as.factor(Hair$hair_ESTout))[2])
writeLines("\n")
```


```{r, include=FALSE}
####Check intra-assay CV

DHEA_CV<-ggplot(Hair_DHEA_CV, aes(x=DHEA_CV)) +
  geom_histogram(color="black",fill="white") +
  geom_vline(xintercept=30,linetype="dashed",colour="red")
DHEA_CV
Hair_DHEA_CV_exc <- Hair_DHEA_CV %>% filter(DHEA_CV > 30) %>% select(SID)

TEST_CV<-ggplot(Hair_TEST_CV, aes(x=TEST_CV)) +
  geom_histogram(color="black",fill="white") +
  geom_vline(xintercept=30,linetype="dashed",colour="red")
TEST_CV
Hair_TEST_CV_exc <- Hair_TEST_CV %>% filter(TEST_CV > 30) %>% select(SID)

EST_CV<-ggplot(Hair_EST_CV, aes(x=EST_CV)) +
  geom_histogram(color="black",fill="white") +
  geom_vline(xintercept=30,linetype="dashed",colour="red")
EST_CV
Hair_EST_CV_exc <- Hair_EST_CV %>% filter(EST_CV > 30) %>% select(SID)

writeLines("\n")
cat("\n*Number of high CVs*")
writeLines("\n")
cat("\nDHEA: ")
cat(length(Hair_DHEA_CV_exc$SID))
writeLines("\n")
cat("\nTEST: ")
cat(length(Hair_TEST_CV_exc$SID))
writeLines("\n")
cat("\nEST: ")
cat(length(Hair_EST_CV_exc$SID))
writeLines("\n")
```


```{r, include=FALSE}
#Set exclusion critera

#Remove hair confounds?
removeConfounds="FALSE"
```



```{r, include = FALSE}
###THINGS WE NEED TO DECIDE ON...
#High 450 CVs
hairExc_EST = c("010","049","131","167","177")
hairExc_DHEA = c("008","020")

#Hair confounds
hairExc_Q = c("029","036","045","059","072","091","093","100","102","111","113","117","120","127","166","175","203","209","211","003","049","053","056","067","068","073","075","083","085","086","099","107","114","132","160","181","205")

Hair <- Hair %>%
  mutate(hair_confounds = if_else(SID %in% hairExc_Q, 1, 0),
         hair_DHEA_450 = if_else(SID %in% hairExc_DHEA, 1, 0),
         hair_EST_450 = if_else(SID %in% hairExc_EST, 1, 0))
```

```{r, include=FALSE}
#UPDATE DATAFRAMES WITH EXCLUSIONS
#replace outlier values with NA
if (removeOut) {
Hair <- Hair %>%
  mutate(hair_EST_pgug = replace(hair_EST_pgug, hair_EST_pgug > 100, NA),
         hair_TEST_pgmg = replace(hair_TEST_pgmg, hair_TEST_pgmg > 10, NA),
         hair_DHEA_pgmg = replace(hair_DHEA_pgmg, hair_DHEA_pgmg > 100, NA))
}

#replace intrassay CV > 30 with NA
if (removeCV) {
  Hair <- Hair %>%
    mutate(hair_DHEA_pgmg = replace(hair_DHEA_pgmg, SID %in% Hair_DHEA_CV_exc$SID, NA),
           hair_TEST_pgmg = replace(hair_TEST_pgmg, SID %in% Hair_TEST_CV_exc$SID, NA),
           hair_EST_pgug = replace(hair_EST_pgug, SID %in% Hair_EST_CV_exc$SID, NA))
  }

#replace problematic 450 CV with NA
if (remove450CV) {
  Hair <- Hair %>%
    mutate(hair_DHEA_pgmg = replace(hair_DHEA_pgmg, SID %in% hairExc_DHEA, NA),
           hair_EST_pgug = replace(hair_EST_pgug, SID %in% hairExc_EST, NA))
}

#replace confounds with NA
if (removeConfounds) {
  Hair <- Hair %>%
    mutate(hair_DHEA_pgmg = replace(hair_DHEA_pgmg, SID %in% hairExc_Q, NA),
           hair_TEST_pgmg = replace(hair_TEST_pgmg, SID %in% hairExc_Q, NA),
           hair_EST_pgug = replace(hair_EST_pgug, SID %in% hairExc_Q, NA))
}
```

```{r, include=FALSE}
####Final dataset post exclusions
#re-create longer format and summary datasets for hair with updated values
Hair_long <- Hair %>% select(SID,contains("pg")) %>% gather(., hormone, concentration, c(hair_DHEA_pgmg,hair_TEST_pgmg,hair_EST_pgug), factor_key=TRUE)

Hair_summary2 <- Hair_long %>% group_by(SID,hormone) %>% 
  summarise(Conc = sum(!is.na(concentration))) %>%
  group_by(hormone) %>% 
  summarise(N = sum(Conc)) 

kable(Hair_summary2, "html", align='c') %>%
kable_styling(full_width = F, position = "left", font_size = 12)
```


```{r,echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
###Calcualte Inter-assay CV

Hair_DHEA_interCV <- read_xlsx(paste0(hair_dir,'/TAG_HAIR_Master_File.xlsx'), sheet=3)
Hair_TEST_interCV <- read_xlsx(paste0(hair_dir,'/TAG_HAIR_Master_File.xlsx'), sheet=6)
Hair_EST_interCV <- read_xlsx(paste0(hair_dir,'/TAG_HAIR_Master_File.xlsx'), sheet=9)

Hair_DHEA_interCV <- Hair_DHEA_interCV %>% 
  rename(wellID = `Well ID`) %>%
  filter(grepl('Ctrl', wellID)) %>%
  select(wellID, Mean) %>%
  mutate(wellID = as.factor(wellID),
         Mean=as.numeric(Mean)) %>%
  group_by(wellID) %>%
  summarize(meanOf_Means = mean(Mean),
            sdOf_Means = sd(Mean)) %>%
  mutate(CV = 100*(sdOf_Means/meanOf_Means))
 
Hair_TEST_interCV <- Hair_TEST_interCV %>% 
  rename(wellID = `Well ID`) %>%
  filter(grepl('CTL', wellID)) %>%
  select(wellID, Mean) %>%
  mutate(wellID = as.factor(wellID),
         Mean=as.numeric(Mean)) %>%
  group_by(wellID) %>%
  summarize(meanOf_Means = mean(Mean),
            sdOf_Means = sd(Mean)) %>%
  mutate(CV = 100*(sdOf_Means/meanOf_Means))

Hair_EST_interCV <- Hair_EST_interCV %>% 
  rename(wellID = `Well ID`) %>%
  filter(grepl('Ctr', wellID)) %>%
  select(wellID, Mean) %>%
  mutate(wellID = as.factor(wellID),
         Mean=as.numeric(Mean)) %>%
  group_by(wellID) %>%
  summarize(meanOf_Means = mean(Mean,na.rm=T),
            sdOf_Means = sd(Mean,na.rm=T)) %>%
  mutate(CV = 100*(sdOf_Means/meanOf_Means))