---
title: "TAG Cleaning Hair Hormone Data"
author: "Nandi"
date: "28 March 2018"
output: html_document
---

```{r, include=FALSE}
#LOAD PACKAGES AND SET DIRECTORIES

packages <- c("ggplot2","tidyr","stringr","knitr","corrplot","data.table","readxl","gridExtra","dplyr", "psych","kableExtra","lavaan")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}
lapply(packages, library, character.only = TRUE)

cas_dir <- '/Volumes/psych-cog/dsnlab/TAG/'
hair_dir <- paste0(cas_dir,'behavior/Hair/Wave1')
options(digits=3)
```

```{r, include=FALSE}
#Set exclusion critera

#Remove outliers?
removeOut="TRUE"
#Remove high CV?
removeCV="TRUE"
#Remove high 450 CV?
remove450CV="FALSE"
#Remove hair confounds?
removeConfounds="FALSE"
```

###IMPORT AND CLEAN HAIR DATA
```{r, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
###IMPORT & CLEAN CONCENTRATIONS 
#import dataframe for each hormone, create SID as 3 digit numeric factor (i.e. "001"), combine all three hormones in one dataframe.
Hair_DHEA <- read_xlsx(paste0(hair_dir,'/TAG_HAIR_Master_File.xlsx'), sheet=2)
Hair_TEST <- read_xlsx(paste0(hair_dir,'/TAG_HAIR_Master_File.xlsx'), sheet=5)
Hair_EST <- read_xlsx(paste0(hair_dir,'/TAG_HAIR_Master_File.xlsx'), sheet=8)

Hair_DHEA <- Hair_DHEA %>% 
  mutate(SID = as.factor(round(as.numeric(ID),2)),
         hair_DHEA = round(as.numeric(Concentration),3),
         hair_DHEA_pgmg = round(as.numeric(`Concentration in pg/mg`),3)) %>%
  replace_na(list(hair_DHEA_pgmg = "missing")) %>%
  select(SID,hair_DHEA_pgmg) %>%
  filter(!is.na(SID)) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  select(-week) %>%
  mutate(SID = as.factor(SID)) %>%
  mutate(SID = str_pad(SID, 3, pad = "0"))

Hair_TEST <- Hair_TEST %>% 
  mutate(SID = as.factor(round(as.numeric(ID),2)),
         hair_TEST = round(as.numeric(Concentration),3),
         hair_TEST_pgmg = round(as.numeric(`Concentration in pg/mg`),3)) %>%
  replace_na(list(hair_TEST_pgmg = "missing")) %>%
  select(SID,hair_TEST_pgmg) %>%
  filter(!is.na(SID)) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  select(-week) %>%
  mutate(SID = as.factor(SID)) %>%
  mutate(SID = str_pad(SID, 3, pad = "0"))

Hair_EST <- Hair_EST %>% 
  mutate(SID = as.factor(round(as.numeric(ID),2)),
         hair_EST = round(as.numeric(`Adjusted Concentration`),3),
         hair_EST_pgug = round(as.numeric(`Concentration in pg/ug`),3)) %>%
  replace_na(list(hair_EST_pgug = "missing")) %>%
  select(SID,hair_EST_pgug) %>%
  filter(!is.na(SID)) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  select(-week) %>%
  mutate(SID = as.factor(SID)) %>%
  mutate(SID = str_pad(SID, 3, pad = "0"))

Hair <- Hair_DHEA %>% full_join(.,Hair_TEST) %>% full_join(.,Hair_EST) %>%
  mutate(SID = as.factor(SID)) %>% arrange(SID)

###IMPORT & CLEAN COV
Hair_DHEA_CV <- read_xlsx(paste0(hair_dir,'/TAG_HAIR_Master_File.xlsx'), sheet=1)
Hair_TEST_CV <- read_xlsx(paste0(hair_dir,'/TAG_HAIR_Master_File.xlsx'), sheet=4)
Hair_EST_CV <- read_xlsx(paste0(hair_dir,'/TAG_HAIR_Master_File.xlsx'), sheet=7)

Hair_DHEA_CV <- Hair_DHEA_CV %>% 
  filter(!is.na(Name)) %>%
  select(Name,`CV (%)`) %>%
  rename(ID = Name,
         DHEA_CV = `CV (%)`) %>%
  mutate(SID = as.factor(round(as.numeric(ID),2)),
         DHEA_CV = round(as.numeric(DHEA_CV),3)) %>%
  select(SID,DHEA_CV) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID)) %>%
  select(-week) %>%
  filter(!is.na(SID)) %>%
  arrange(SID) 
  

Hair_TEST_CV <- Hair_TEST_CV %>% 
  filter(!is.na(Name)) %>%
  select(Name,`CV (%)`) %>%
  rename(ID = Name,
         TEST_CV = `CV (%)`) %>%
  mutate(SID = as.factor(round(as.numeric(ID),2)),
         TEST_CV = round(as.numeric(TEST_CV),3)) %>%
  select(SID,TEST_CV) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID)) %>%
  select(-week) %>%
  filter(!is.na(SID)) %>%
  arrange(SID)
  
Hair_EST_CV <- Hair_EST_CV %>% 
  filter(!is.na(Name)) %>%
  select(Name,`CV (%)`) %>%
  rename(ID = Name,
         EST_CV = `CV (%)`) %>%
  mutate(SID = as.factor(round(as.numeric(ID),2)),
         EST_CV = round(as.numeric(EST_CV),3)) %>%
  select(SID,EST_CV) %>%
  filter(!SID == "0.1") %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID)) %>%
  select(-week) %>%
  filter(!is.na(SID)) %>%
  arrange(SID)

Hair_CV <- Hair_DHEA_CV %>% full_join(.,Hair_TEST_CV) %>% full_join(.,Hair_EST_CV) %>% arrange(SID)
```

###SUMMARIES
```{r, echo=FALSE, message=FALSE, warning=FALSE, results="asis", fig.height=4, fig.width=4}
Hair_long <- Hair %>% select(SID,contains("pg")) %>% gather(., hormone, concentration, c(hair_DHEA_pgmg,hair_TEST_pgmg,hair_EST_pgug), factor_key=TRUE)

Hair_missing <- Hair_long %>% 
  mutate(missing = ifelse(is.na(concentration),1,0)) %>%
  select(-concentration) %>%
  group_by(hormone) %>% 
  summarise(missing = sum(missing))

Hair_assayed <- Hair_long %>% 
  filter(!is.na(concentration)) %>%
  mutate(concentration = as.numeric(concentration)) %>%
  group_by(SID,hormone) %>% 
  summarise(Conc = sum(!is.na(concentration)),
            NoCon = sum(is.na(concentration))) %>%
  group_by(hormone) %>% 
  summarise(Conc = sum(Conc),
            NoCon = sum(NoCon))

Hair_summary <- Hair_assayed %>% left_join(.,Hair_missing)

####Samples sent
cat('No of Subjects: ') 
cat(length(unique(Hair$SID)))

####Summary of samples
kable(Hair_summary, "html", align='c') %>%
kable_styling(full_width = F, position = "left", font_size = 12)

Hair <- Hair %>% mutate(hair_DHEA_pgmg = as.numeric(hair_DHEA_pgmg),
                        hair_TEST_pgmg = as.numeric(hair_TEST_pgmg),
                        hair_EST_pgug = as.numeric(hair_EST_pgug))
```

####Checking for outliers (of mean of duplicates)
```{r, echo=FALSE, message=FALSE, warning=FALSE, results="asis", fig.height=4, fig.width=4}
hist(Hair$hair_DHEA_pgmg, main="", xlab="DHEA")
abline(v=100,col="red")
writeLines("\n")
writeLines("\n")
hist(Hair$hair_TEST_pgmg, main="", xlab="TEST")
abline(v=10,col="red")
writeLines("\n")
writeLines("\n")
hist(Hair$hair_EST_pgug, main="", xlab="EST")
abline(v=100,col="red")
writeLines("\n")

#calculate number of outliers based on visual inspection cut-offs
Hair <- Hair %>%
  mutate(hair_DHEAout = if_else(hair_DHEA_pgmg > 100, 1, 0),
         hair_TESTout = if_else(hair_TEST_pgmg > 10, 1, 0),
         hair_ESTout = if_else(hair_EST_pgug > 100, 1, 0))

cat("\n*Number of outlier samples*")
writeLines("\n")
cat("\nDHEA: ")
cat(summary(as.factor(Hair$hair_DHEAout))[2])
writeLines("\n")
writeLines("\n")
cat("\nTEST: ")
cat(summary(as.factor(Hair$hair_TESTout))[2])
writeLines("\n")
cat("\nEST: ")
cat(summary(as.factor(Hair$hair_ESTout))[2])
writeLines("\n")
```

####Check intra-assay CV
```{r, echo=FALSE, message=FALSE, warning=FALSE, results="asis", fig.height=4, fig.width=4}
DHEA_CV<-ggplot(Hair_DHEA_CV, aes(x=DHEA_CV)) +
  geom_histogram(color="black",fill="white") +
  geom_vline(xintercept=30,linetype="dashed",colour="red")
DHEA_CV
Hair_DHEA_CV_exc <- Hair_DHEA_CV %>% filter(DHEA_CV > 30) %>% select(SID)

TEST_CV<-ggplot(Hair_TEST_CV, aes(x=TEST_CV)) +
  geom_histogram(color="black",fill="white") +
  geom_vline(xintercept=30,linetype="dashed",colour="red")
TEST_CV
Hair_TEST_CV_exc <- Hair_TEST_CV %>% filter(TEST_CV > 30) %>% select(SID)

EST_CV<-ggplot(Hair_EST_CV, aes(x=EST_CV)) +
  geom_histogram(color="black",fill="white") +
  geom_vline(xintercept=30,linetype="dashed",colour="red")
EST_CV
Hair_EST_CV_exc <- Hair_EST_CV %>% filter(EST_CV > 30) %>% select(SID)

writeLines("\n")
cat("\n*Number of high CVs*")
writeLines("\n")
cat("\nDHEA: ")
cat(length(Hair_DHEA_CV_exc$SID))
writeLines("\n")
cat("\nTEST: ")
cat(length(Hair_TEST_CV_exc$SID))
writeLines("\n")
cat("\nEST: ")
cat(length(Hair_EST_CV_exc$SID))
writeLines("\n")
```


```{r, include = FALSE}
###THINGS WE NEED TO DECIDE ON...
#High 450 CVs
hairExc_EST = c("010","049","131","167","177")
hairExc_DHEA = c("008","020")

#Hair confounds
hairExc_Q = c("029","036","045","059","072","091","093","100","102","111","113","117","120","127","166","175","203","209","211","003","049","053","056","067","068","073","075","083","085","086","099","107","114","132","160","181","205")

Hair <- Hair %>%
  mutate(hair_confounds = if_else(SID %in% hairExc_Q, 1, 0),
         hair_DHEA_450 = if_else(SID %in% hairExc_DHEA, 1, 0),
         hair_EST_450 = if_else(SID %in% hairExc_EST, 1, 0))
```


```{r, include=FALSE}
#UPDATE DATAFRAMES WITH EXCLUSIONS
#replace outlier values with NA
if (removeOut) {
Hair <- Hair %>%
  mutate(hair_EST_pgug = replace(hair_EST_pgug, hair_EST_pgug > 100, NA),
         hair_TEST_pgmg = replace(hair_TEST_pgmg, hair_TEST_pgmg > 10, NA),
         hair_DHEA_pgmg = replace(hair_DHEA_pgmg, hair_DHEA_pgmg > 100, NA))
}

#replace intrassay CV > 30 with NA
if (removeCV) {
  Hair <- Hair %>%
    mutate(hair_DHEA_pgmg = replace(hair_DHEA_pgmg, SID %in% Hair_DHEA_CV_exc$SID, NA),
           hair_TEST_pgmg = replace(hair_TEST_pgmg, SID %in% Hair_TEST_CV_exc$SID, NA),
           hair_EST_pgug = replace(hair_EST_pgug, SID %in% Hair_EST_CV_exc$SID, NA))
  }

#replace problematic 450 CV with NA
if (remove450CV) {
  Hair <- Hair %>%
    mutate(hair_DHEA_pgmg = replace(hair_DHEA_pgmg, SID %in% hairExc_DHEA, NA),
           hair_EST_pgug = replace(hair_EST_pgug, SID %in% hairExc_EST, NA))
}

#replace confounds with NA
if (removeConfounds) {
  Hair <- Hair %>%
    mutate(hair_DHEA_pgmg = replace(hair_DHEA_pgmg, SID %in% hairExc_Q, NA),
           hair_TEST_pgmg = replace(hair_TEST_pgmg, SID %in% hairExc_Q, NA),
           hair_EST_pgug = replace(hair_EST_pgug, SID %in% hairExc_Q, NA))
}
```

####Final dataset post exclusions
```{r, echo=FALSE, message=FALSE, warning=FALSE, results="asis", fig.height=4, fig.width=4}
#re-create longer format and summary datasets for hair with updated values
Hair_long <- Hair %>% select(SID,contains("pg")) %>% gather(., hormone, concentration, c(hair_DHEA_pgmg,hair_TEST_pgmg,hair_EST_pgug), factor_key=TRUE)

Hair_summary2 <- Hair_long %>% group_by(SID,hormone) %>% 
  summarise(Conc = sum(!is.na(concentration))) %>%
  group_by(hormone) %>% 
  summarise(N = sum(Conc)) 

kable(Hair_summary2, "html", align='c') %>%
kable_styling(full_width = F, position = "left", font_size = 12)
```

```{r,echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
#write final output for analyses

```

###Calcualte Inter-assay CV
```{r,echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
Hair_DHEA_interCV <- read_xlsx(paste0(hair_dir,'/TAG_HAIR_Master_File.xlsx'), sheet=3)
Hair_TEST_interCV <- read_xlsx(paste0(hair_dir,'/TAG_HAIR_Master_File.xlsx'), sheet=6)
Hair_EST_interCV <- read_xlsx(paste0(hair_dir,'/TAG_HAIR_Master_File.xlsx'), sheet=9)

Hair_DHEA_interCV <- Hair_DHEA_interCV %>% 
  rename(wellID = `Well ID`) %>%
  filter(grepl('Ctrl', wellID)) %>%
  select(wellID, Mean) %>%
  mutate(wellID = as.factor(wellID),
         Mean=as.numeric(Mean)) %>%
  group_by(wellID) %>%
  summarize(meanOf_Means = mean(Mean),
            sdOf_Means = sd(Mean)) %>%
  mutate(CV = 100*(sdOf_Means/meanOf_Means))
 
Hair_TEST_interCV <- Hair_TEST_interCV %>% 
  rename(wellID = `Well ID`) %>%
  filter(grepl('CTL', wellID)) %>%
  select(wellID, Mean) %>%
  mutate(wellID = as.factor(wellID),
         Mean=as.numeric(Mean)) %>%
  group_by(wellID) %>%
  summarize(meanOf_Means = mean(Mean),
            sdOf_Means = sd(Mean)) %>%
  mutate(CV = 100*(sdOf_Means/meanOf_Means))

Hair_EST_interCV <- Hair_EST_interCV %>% 
  rename(wellID = `Well ID`) %>%
  filter(grepl('Ctr', wellID)) %>%
  select(wellID, Mean) %>%
  mutate(wellID = as.factor(wellID),
         Mean=as.numeric(Mean)) %>%
  group_by(wellID) %>%
  summarize(meanOf_Means = mean(Mean,na.rm=T),
            sdOf_Means = sd(Mean,na.rm=T)) %>%
  mutate(CV = 100*(sdOf_Means/meanOf_Means))