---
title: "auto-motion-fmriprep"
author: "Nandi"
date: "14 June 2018"
output: html_document
---

This script will create an artifact regressor from fmriprep confounds, and combine them with the euclidean regressors to create a motion regressor file. 
Output is saved in a folder called "auto-motion-fmriprep"

###LOAD PACKAGES AND SET DIRECTORIES
```{r, include=FALSE}
packages <- c("dplyr","tidyr","data.table","tibble")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}
lapply(packages, library, character.only = TRUE)

#Set variables
study = 'TAG'
subPattern = 'sub-TAG([0-9]{3})'
wavePattern = 'ses-wave([0-9]{1})'
taskPattern = 'task-(DSD|SVC)'
runPattern = 'run-([0-9]{2})'

#Set scripts directory
scriptDir = '/Volumes/StorEDGE/WORK/DSN/TAG/TAG_scripts/fMRI/fx/motion/'

#Set fmriprep confounds directory
confoundDir = '/Volumes/psych-cog/dsnlab/TAG/bids_data/derivatives/fmriprep/'

#Set euclidean motion directory
eucDir = '/Volumes/psych-cog/dsnlab/TAG/nonbids_data/fMRI/fx/motion/wave1/eucmotion/rp_txt'

#Set output directory to save final motion regressors (with euclidean and artifact regressors). Make sure this folder exists
motionDir = '/Volumes/psych-cog/dsnlab/TAG/nonbids_data/fMRI/fx/motion/wave1/auto-motion-fmriprep/rp_txt/fd0.8_dv2.0_noNeighbors/'

#Set output directory to save plots of fmriprep motion regressors. Make sure this folder exists
plotDir = '/Volumes/psych-cog/dsnlab/TAG/nonbids_data/fMRI/fx/motion/wave1/auto-motion-fmriprep/plots/'

#Set artifact threshold
thresh = 'FramewiseDisplacement > 0.8 | stdDVARS > 2.0'
neighbor = "FALSE"
```

###IMPORT FMRIPREP MOTION CONFOUNDS
```{r}

if (!file.exists(paste0(scriptDir,'output/fmriprep_motion.csv'))) {
  
  # if the merged dataset doesn't exist, create it
  file_list = list.files(confoundDir, pattern = 'confounds.tsv', recursive = TRUE)
  
  for (file in file_list){
    if (!exists('dataset')){
      filePattern = paste(subPattern, wavePattern, taskPattern, runPattern, 'bold_confounds.tsv', sep = "_")
      dataset <- read_tsv(paste0(confoundDir, file)) %>%
        mutate(file = file) %>%
        extract(file, c('SID', 'wave', 'task', 'run'),
                file.path('sub-.*','ses-wave.*', 'func', filePattern)) %>%
        mutate(wave = as.integer(wave),
               run = as.integer(run),
               stdDVARS = as.numeric(ifelse(stdDVARS %in% "n/a", NA, stdDVARS)),
               `non-stdDVARS` = as.numeric(ifelse(`non-stdDVARS` %in% "n/a", NA, `non-stdDVARS`)),
               `vx-wisestdDVARS` = as.numeric(ifelse(`vx-wisestdDVARS` %in% "n/a", NA, `vx-wisestdDVARS`)),
               FramewiseDisplacement = as.numeric(ifelse(FramewiseDisplacement %in% "n/a", NA, FramewiseDisplacement)),
               volume = row_number()) %>%
        select(SID, wave, task, run, volume, everything())
    }
  
    # if the merged dataset does exist, append to it
    else {
      filePattern = paste(subPattern, wavePattern, taskPattern, runPattern, 'bold_confounds.tsv', sep = "_")
      tmp <- read_tsv(paste0(confoundDir, file)) %>%
        mutate(file = file) %>%
        extract(file, c('SID', 'wave', 'task', 'run'),
                file.path('sub-.*','ses-wave.*', 'func', filePattern)) %>%
        mutate(wave = as.integer(wave),
               run = as.integer(run),
               stdDVARS = as.numeric(ifelse(stdDVARS %in% "n/a", NA, stdDVARS)),
               `non-stdDVARS` = as.numeric(ifelse(`non-stdDVARS` %in% "n/a", NA, `non-stdDVARS`)),
               `vx-wisestdDVARS` = as.numeric(ifelse(`vx-wisestdDVARS` %in% "n/a", NA, `vx-wisestdDVARS`)),
               FramewiseDisplacement = as.numeric(ifelse(FramewiseDisplacement %in% "n/a", NA, FramewiseDisplacement)),
               volume = row_number()) %>%
        select(SID, wave, task, run, volume, everything())
      dataset = bind_rows(dataset, tmp)
      rm(tmp)
    }
  write.csv(dataset, paste0(scriptDir,'output/fmriprep_motion.csv'), row.names = FALSE)
  }
} else {
  dataset = read.csv(paste0(scriptDir,'output/fmriprep_motion.csv'), stringsAsFactors = FALSE)
}

dataset = dataset %>%
  mutate(sub.run = paste(SID, task, run, sep = "_"),
         SID = as.integer(SID))
```

###LOAD EUCLIDEAN DISTANCES
```{r}
if (!file.exists(paste0(scriptDir,'output/euclidean_motion.csv'))) {
  
  # if the merged dataset doesn't exist, create it
  euc_file_list = list.files(eucDir, pattern='rp_', recursive = TRUE, full.names=T)
  
  eucDF <- lapply(X=euc_file_list, FUN=function(file) {
  
    SID <- sub(".*rp_txt/rp_", "", file) %>% substring(., 1,3)
    task <- ifelse(grepl("DSD",file),"DSD",
               ifelse(grepl("SVC",file),"SVC",NA))  
    run <- sub(paste0('.*',task),"", file) %>% substring(., 1,1)   
    eucData <- read.table(file, sep = ' ', header=F)
    eucData <- eucData %>% 
      rename(eucTrans = V1,
           eucRot = V4,
           eucTransDer = V7,
           eucRotDer = V10,
           eucArt = V13) %>%
      mutate(SID = as.integer(SID),
           task = task,
           run = as.integer(run)) %>%
      select(-contains("V")) %>%
      rownames_to_column("volume") %>%
      mutate(volume = as.integer(volume))
    })
  
  eucDF<-rbindlist(eucDF)
  write.csv(eucDF, paste0(scriptDir,'output/euclidean_motion.csv'), row.names = FALSE)  
  
} else {
  eucDF = read.csv(paste0(scriptDir,'output/euclidean_motion.csv'), stringsAsFactors = FALSE)
}

```

###COMBINE DATASETS & CREATE ARTIFACT
```{r}
joined = left_join(dataset, eucDF, by = c("SID", "task", "run", "volume")) %>% select(SID, task, run, volume, everything())

is.na(joined) <- joined == "n/a"

joined <- joined %>% 
  mutate_(artifact = paste0('ifelse(',thresh,', 1, 0)')) %>%
  mutate(artifact_N = ifelse(artifact == 1 | lag(artifact) == 1 | lead(artifact) ==1, 1, 0)) %>%
  mutate(artifact = ifelse(is.na(artifact), 0, artifact),
         artifact_N = ifelse(is.na(artifact_N), 0, artifact_N),
         stdDVARS = ifelse(is.na(stdDVARS), 0, stdDVARS),
         non.stdDVARS = ifelse(is.na(non.stdDVARS), 0, non.stdDVARS),
         vx.wisestdDVARS = ifelse(is.na(vx.wisestdDVARS), 0, vx.wisestdDVARS),
         FramewiseDisplacement = ifelse(is.na(FramewiseDisplacement), 0, FramewiseDisplacement)) 

#save joined DF
write.csv(joined, paste0(scriptDir,'output/all_motion.csv'), row.names = FALSE)  

```

###PRINT MOTION FILES
```{r}
subjectList <- as.character(unique(joined$SID))

if (neighbor) {
  joined$artifact = joined$artifact_N
  } else {}

motion <- lapply(X=subjectList, df=joined, FUN=function(sid, df) {
                           
  adf <- joined %>% filter(SID == as.integer(sid)) %>% 
    select(SID, task, run, volume, eucTrans, eucRot, eucTransDer, eucRotDer, artifact) %>%
    group_by(task,run) %>%
    do({
      ungroup(.) 
      saveDF <- select(.,eucTrans, eucRot, eucTransDer, eucRotDer, artifact)
      write.table(saveDF, file=paste0(motionDir,'rp_',str_pad(sid,3,pad="0"),'_',.$task[[1]],.$run[[1]],'.txt'), sep='\t', row.name=F, quote=F, col.names=F)
      data.frame()
      }) })
```

###PLOT MOTION CONFOUNDS
```{r, fig.width = 12, fig.height = 15}
data.plot = joined %>% select(-sub.run) %>%
  gather(feature, value, -c(SID, task, run, volume))

features = c("CSF", "WhiteMatter", "GlobalSignal", "FramewiseDisplacement", "stdDVARS", "vx.wisestdDVARS", "non.stdDVARS","eucTrans","eucRot","eucTransDer","eucRotDer","eucArt","artifact","artifact_N")

data.sub = data.plot %>%
  filter(feature %in% features) %>%
  mutate(sort = ifelse(feature == "CSF", 1,
                ifelse(feature == "GlobalSignal", 2,
                ifelse(feature == "WhiteMatter", 3,
                ifelse(feature == "FramewiseDisplacement", 4,
                ifelse(feature == "stdDVARS", 5,
                ifelse(feature == "vx.wisestdDVARS", 6,
                ifelse(feature == "non.stdDVARS", 7, 
                ifelse(feature == "eucTrans", 8,
                ifelse(feature == "eucRot", 9,
                ifelse(feature == "eucTransDer", 10,
                ifelse(feature == "eucRotDer", 11, 
                ifelse(feature == "eucArt", 12, 
                ifelse(feature == "artifact", 13, 
                ifelse(feature == "artifact_N", 14, NA))))))))))))))) %>%
  mutate(value=round(as.numeric(value),1),
         task2=paste0(task,run))

nada = data.sub %>% 
  group_by(SID,task2) %>%
    do({
      plot = ggplot(., aes(volume, value)) + 
        geom_line(aes(colour = feature), size = .25, show.legend = FALSE) +
        facet_wrap(task2 ~ reorder(feature,sort), ncol = 4, scales = "free") +
        labs(title = .$SID[[1]])
      print(plot)
      ggsave(plot, file = paste0(plotDir,.$SID[[1]],'_',.$task2[[1]],'.pdf'), height = 10, width = 12)
      data.frame()
    })
```

###PRINT DSD MOTION SUMMARY
```{r}
#summarise artifacts in each subject in DSD. first load DSD overview and limit sample to 146 participants with DSD pre motion.

dsd_overview <- read.csv('~/Desktop/dsd_overview.csv',header=T)

DSDids <- dsd_overview %>% filter(Withdrawn_W1==0) %>% filter(W1S2_Completed==1) %>% filter(!check_mri_completed.2.partial.1.full.0.none.==0) %>% filter(dsd_completed==2) %>% filter(is.na(technical_missing)) %>% filter(is.na(participant_error)) %>% mutate(subjectID=SID) %>% select(subjectID)

summaryDF_dsd <- joined %>% filter(SID %in% DSDids$subjectID) %>% filter(task=="DSD") %>%
  select(SID,run,artifact,artifact_N) %>% group_by(SID) %>% 
  summarise(artifact=100*(sum(artifact)/n()),
            artifact_N=100*(sum(artifact_N/n())),
            N = n()) %>%
  arrange(-artifact)

write.csv(summaryDF_dsd,paste0(motionDir,'summary_DSD_Motion.csv'))
```
