---
title: "auto-motion-fmriprep"
author: "Nandi"
date: "13 June 2018"
output: html_document
---

# set paths & variables
```{r, message=FALSE}
#This is where all subject-numbered directories are:
scriptDir = '/Volumes/StorEDGE/WORK/DSN/TAG/TAG_scripts/fMRI/fx/motion/'
confoundDir = '/Volumes/psych-cog/dsnlab/TAG/bids_data/derivatives/fmriprep/'
eucDir = '/Volumes/psych-cog/dsnlab/TAG/nonbids_data/fMRI/fx/motion/wave1/eucmotion/rp_txt'
outputDir = '/Volumes/psych-cog/dsnlab/TAG/nonbids_data/fMRI/fx/motion/wave1/auto-motion-fmriprep/rp_txt'
plotDir = '/Volumes/psych-cog/dsnlab/TAG/nonbids_data/fMRI/fx/motion/wave1/auto-motion-fmriprep/plots/'
  
# variables
study = 'TAG'
subPattern = 'sub-TAG([0-9]{3})'
wavePattern = 'ses-wave([0-9]{1})'
taskPattern = 'task-(DSD|SVC)'
runPattern = 'run-([0-9]{2})'
```

# load confound files
```{r, message=FALSE}
file_list = list.files(confoundDir, pattern = 'confounds.tsv', recursive = TRUE)

if (!file.exists(paste0(outputDir,'/fmriprep_motion.csv'))) {
  for (file in file_list){
    # if the merged dataset doesn't exist, create it
    if (!exists('dataset')){
      filePattern = paste(subPattern, wavePattern, taskPattern, runPattern, 'bold_confounds.tsv', sep = "_")
      dataset <- read_tsv(paste0(confoundDir, file)) %>%
        mutate(file = file) %>%
        extract(file, c('subjectID', 'wave', 'task', 'run'),
                file.path('sub-.*','ses-wave.*', 'func', filePattern)) %>%
        mutate(wave = as.integer(wave),
               run = as.integer(run),
               stdDVARS = as.numeric(ifelse(stdDVARS %in% "n/a", NA, stdDVARS)),
               `non-stdDVARS` = as.numeric(ifelse(`non-stdDVARS` %in% "n/a", NA, `non-stdDVARS`)),
               `vx-wisestdDVARS` = as.numeric(ifelse(`vx-wisestdDVARS` %in% "n/a", NA, `vx-wisestdDVARS`)),
               FramewiseDisplacement = as.numeric(ifelse(FramewiseDisplacement %in% "n/a", NA, FramewiseDisplacement)),
               volume = row_number()) %>%
        select(subjectID, wave, task, run, volume, everything())
    }
  
    # if the merged dataset does exist, append to it
    else {
      filePattern = paste(subPattern, wavePattern, taskPattern, runPattern, 'bold_confounds.tsv', sep = "_")
      tmp <- read_tsv(paste0(confoundDir, file)) %>%
        mutate(file = file) %>%
        extract(file, c('subjectID', 'wave', 'task', 'run'),
                file.path('sub-.*','ses-wave.*', 'func', filePattern)) %>%
        mutate(wave = as.integer(wave),
               run = as.integer(run),
               stdDVARS = as.numeric(ifelse(stdDVARS %in% "n/a", NA, stdDVARS)),
               `non-stdDVARS` = as.numeric(ifelse(`non-stdDVARS` %in% "n/a", NA, `non-stdDVARS`)),
               `vx-wisestdDVARS` = as.numeric(ifelse(`vx-wisestdDVARS` %in% "n/a", NA, `vx-wisestdDVARS`)),
               FramewiseDisplacement = as.numeric(ifelse(FramewiseDisplacement %in% "n/a", NA, FramewiseDisplacement)),
               volume = row_number()) %>%
        select(subjectID, wave, task, run, volume, everything())
      dataset = bind_rows(dataset, tmp)
      rm(tmp)
    }
  write.csv(dataset, paste0(scriptDir,'fmriprep_motion.csv'), row.names = FALSE)
  }
} else {
  dataset = read.csv(paste0(scriptDir,'fmriprep_motion.csv'), stringsAsFactors = FALSE)
}

dataset = dataset %>%
  mutate(sub.run = paste(SID, task, run, sep = "_"),
         subjectID = as.integer(SID))

dataset$subjectID <- dataset$SID
```

# load euclidean distances
```{r}
eucFiles = list.files(path=eucDir,pattern='rp_', recursive = TRUE, full.names=T)

eucDF <- lapply(X=eucFiles, FUN=function(file) {
  subjectID <- sub(".*rp_txt/rp_", "", file) %>% substring(., 1,3)
  task <- ifelse(grepl("DSD",file),"DSD",
               ifelse(grepl("SVC",file),"SVC",NA))  
  run <- sub(paste0('.*',task),"", file) %>% substring(., 1,1)   
  eucData <- read.table(file, sep = ' ', header=F)
  eucData <- eucData %>% 
    rename(eucTrans = V1,
           eucRot = V4,
           eucTransDer = V7,
           eucRotDer = V10,
           eucArt = V13) %>%
    mutate(subjectID = as.integer(subjectID),
           task = task,
           run = as.integer(run)) %>%
    select(-contains("V")) %>%
    rownames_to_column("volume") %>%
    mutate(volume = as.integer(volume))
  })
eucDF_backup<-rbindlist(eucDF)
eucDF<-eucDF_backup

eucDF$subjectID <- eucDF$SID
```

# combine fmriprep and euclidean motion confounds 
```{r}
joined = left_join(dataset, eucDF, by = c("subjectID", "task", "run", "volume")) %>% select(subjectID, wave, task, run, volume, everything()) 
```

# visualize confounds
```{r, fig.width = 10, fig.height = 15}
data.plot = joined %>% select(-sub.run) %>%
  gather(feature, value, -c(subjectID, wave, task, run, volume))

ggplot(data.plot, aes(value)) + 
  geom_density(fill = "pink") +
  facet_wrap(~feature, scales = "free", ncol = 4)
```

# visualize confounds on a subject level
```{r, fig.width = 12, fig.height = 15}
features = c("CSF", "WhiteMatter", "GlobalSignal", "FramewiseDisplacement", "stdDVARS", "vx.wisestdDVARS", "non.stdDVARS","eucTrans","eucRot","eucTransDer","eucRotDer","eucArt")

data.sub = data.plot %>%
  filter(feature %in% features) %>%
  mutate(sort = ifelse(feature == "CSF", 1,
                ifelse(feature == "GlobalSignal", 2,
                ifelse(feature == "WhiteMatter", 3,
                ifelse(feature == "FramewiseDisplacement", 4,
                ifelse(feature == "stdDVARS", 5,
                ifelse(feature == "vx.wisestdDVARS", 6,
                ifelse(feature == "non.stdDVARS", 7, 
                ifelse(feature == "eucTrans", 8,
                ifelse(feature == "eucRot", 9,
                ifelse(feature == "eucTransDer", 10,
                ifelse(feature == "eucRotDer", 11, 
                ifelse(feature == "eucArt", 12, NA))))))))))))) %>%
  mutate(value=round(as.numeric(value),1),
         task2=paste0(task,run))

nada = data.sub %>% 
  group_by(subjectID,task) %>%
    do({
      plot = ggplot(., aes(volume, value)) + 
        geom_line(aes(colour = feature), size = .25, show.legend = FALSE) +
        facet_wrap(task2 ~ reorder(feature,sort), ncol = 4, scales = "free") +
        labs(title = .$subjectID[[1]])
      print(plot)
      ggsave(plot, file = paste0(plotDir,'raw/',.$subjectID[[1]],'_',.$task[[1]],'.pdf'), height = 10, width = 12)
      data.frame()
    })
```

# thresholds FD & DVARS & visualize
```{r, fig.width = 12, fig.height = 15}
# recode FD and DVARS into binary variables. 

joined <- joined %>% 
  mutate(FD_0.6 = (ifelse(FramewiseDisplacement > 0.6, 1, 0)),
         FD_0.7 = (ifelse(FramewiseDisplacement > 0.7, 1, 0)),
         FD_0.8 = (ifelse(FramewiseDisplacement > 0.8, 1, 0)),
         FD_0.9 = (ifelse(FramewiseDisplacement > 0.9, 1, 0)),
         FD_1.0 = (ifelse(FramewiseDisplacement > 1.0, 1, 0)),
         FD_1.1 = (ifelse(FramewiseDisplacement > 1.1, 1, 0)),
         FD_0.8_DVARS_2.0 = (ifelse(FramewiseDisplacement > 0.8 | stdDVARS > 2.0, 1, 0)),
         FD_0.8_DVARS_2.1 = (ifelse(FramewiseDisplacement > 0.8 | stdDVARS > 2.1, 1, 0)),
         FD_0.9_DVARS_2.0 = (ifelse(FramewiseDisplacement > 0.9 | stdDVARS > 2.0, 1, 0)),
         FD_0.9_DVARS_2.1 = (ifelse(FramewiseDisplacement > 0.9 | stdDVARS > 2.1, 1, 0)),
         FD_1.0_DVARS_2.0 = (ifelse(FramewiseDisplacement > 1.0 | stdDVARS > 2.0, 1, 0)),
         FD_1.0_DVARS_2.1 = (ifelse(FramewiseDisplacement > 1.0 | stdDVARS > 2.1, 1, 0))) %>%
  mutate(FD_0.6N = ifelse(FD_0.6 == 1 | lag(FD_0.6) == 1 | lead(FD_0.6) ==1, 1, 0),
         FD_0.7N = ifelse(FD_0.7 == 1 | lag(FD_0.7) == 1 | lead(FD_0.7) ==1, 1, 0),
         FD_0.8N = ifelse(FD_0.8 == 1 | lag(FD_0.8) == 1 | lead(FD_0.8) ==1, 1, 0),
         FD_0.9N = ifelse(FD_0.9 == 1 | lag(FD_0.9) == 1 | lead(FD_0.9) ==1, 1, 0),
         FD_1.0N = ifelse(FD_1.0 == 1 | lag(FD_1.0) == 1 | lead(FD_1.0) ==1, 1, 0),
         FD_1.1N = ifelse(FD_1.1 == 1 | lag(FD_1.1) == 1 | lead(FD_1.1) ==1, 1, 0),
         FD_0.8_DVARS_2.0N = ifelse(FD_0.8_DVARS_2.0 == 1 | lag(FD_0.8_DVARS_2.0) == 1 | lead(FD_0.8_DVARS_2.0) ==1, 1, 0),
         FD_0.8_DVARS_2.1N = ifelse(FD_0.8_DVARS_2.1 == 1 | lag(FD_0.8_DVARS_2.1) == 1 | lead(FD_0.8_DVARS_2.1) ==1, 1, 0),
         FD_0.9_DVARS_2.0N = ifelse(FD_0.9_DVARS_2.0 == 1 | lag(FD_0.9_DVARS_2.0) == 1 | lead(FD_0.9_DVARS_2.0) ==1, 1, 0),
         FD_0.9_DVARS_2.1N = ifelse(FD_0.9_DVARS_2.1 == 1 | lag(FD_0.9_DVARS_2.1) == 1 | lead(FD_0.9_DVARS_2.1) ==1, 1, 0),
         FD_1.0_DVARS_2.0N = ifelse(FD_1.0_DVARS_2.0 == 1 | lag(FD_1.0_DVARS_2.0) == 1 | lead(FD_1.0_DVARS_2.0) ==1, 1, 0),
         FD_1.0_DVARS_2.1N = ifelse(FD_1.0_DVARS_2.1 == 1 | lag(FD_1.0_DVARS_2.1) == 1 | lead(FD_1.0_DVARS_2.1) ==1, 1, 0))

# summarise artifacts in each subject and task
summaryDF <- joined %>% group_by(subjectID,task,run) %>%
  summarise(FD_0.6_perc = 100*(sum(FD_0.6,na.rm=T))/n(),
            FD_0.7_perc = 100*(sum(FD_0.7,na.rm=T))/n(),
            FD_0.8_perc = 100*(sum(FD_0.8,na.rm=T))/n(),
            FD_0.9_perc = 100*(sum(FD_0.9,na.rm=T))/n(),
            FD_1.0_perc = 100*(sum(FD_1.0,na.rm=T))/n(),
            FD_1.1_perc = 100*(sum(FD_1.1,na.rm=T))/n(),
            FD_0.6N_perc = 100*(sum(FD_0.6N,na.rm=T))/n(),
            FD_0.7N_perc = 100*(sum(FD_0.7N,na.rm=T))/n(),
            FD_0.8N_perc = 100*(sum(FD_0.8N,na.rm=T))/n(),
            FD_0.9N_perc = 100*(sum(FD_0.9N,na.rm=T))/n(),
            FD_1.0N_perc = 100*(sum(FD_1.0N,na.rm=T))/n(),
            FD_1.1N_perc = 100*(sum(FD_1.1N,na.rm=T))/n(),
            FD_0.8_DVARS_2.0_perc = 100*(sum(FD_0.8_DVARS_2.0,na.rm=T))/n(),
            FD_0.8_DVARS_2.1_perc = 100*(sum(FD_0.8_DVARS_2.1,na.rm=T))/n(),
            FD_0.9_DVARS_2.0_perc = 100*(sum(FD_0.9_DVARS_2.0,na.rm=T))/n(),
            FD_0.9_DVARS_2.1_perc = 100*(sum(FD_0.9_DVARS_2.1,na.rm=T))/n(),
            FD_1.0_DVARS_2.0_perc = 100*(sum(FD_1.0_DVARS_2.0,na.rm=T))/n(),
            FD_1.0_DVARS_2.1_perc = 100*(sum(FD_1.0_DVARS_2.1,na.rm=T))/n(),
            FD_0.8_DVARS_2.0N_perc = 100*(sum(FD_0.8_DVARS_2.0N,na.rm=T))/n(),
            FD_0.8_DVARS_2.1N_perc = 100*(sum(FD_0.8_DVARS_2.1N,na.rm=T))/n(),
            FD_0.9_DVARS_2.0N_perc = 100*(sum(FD_0.9_DVARS_2.0N,na.rm=T))/n(),
            FD_0.9_DVARS_2.1N_perc = 100*(sum(FD_0.9_DVARS_2.1N,na.rm=T))/n(),
            FD_1.0_DVARS_2.0N_perc = 100*(sum(FD_1.0_DVARS_2.0N,na.rm=T))/n(),
            FD_1.0_DVARS_2.1N_perc = 100*(sum(FD_1.0_DVARS_2.1N,na.rm=T))/n())

# summarise artifacts in each subject in DSD. first load DSD overview and limit sample to 147 participants with DSD pre motion.

dsd_overview <- read.csv('~/Desktop/dsd_overview.csv',header=T)

DSDids <- dsd_overview %>% filter(Withdrawn_W1==0) %>% filter(W1S2_Completed==1) %>% filter(!check_mri_completed.2.partial.1.full.0.none.==0) %>% filter(dsd_completed==2) %>% filter(is.na(technical_missing)) %>% filter(is.na(participant_error)) %>% mutate(subjectID=SID) %>% select(subjectID)

summaryDF_dsd <- summaryDF %>% filter(subjectID %in% DSDids$subjectID) %>%
  filter(task=="DSD") %>% 
  group_by(subjectID) %>% 
  summarise(FD_0.6_perc = mean(FD_0.6_perc,na.rm=T),
            FD_0.7_perc = mean(FD_0.7_perc,na.rm=T),
            FD_0.8_perc = mean(FD_0.8_perc,na.rm=T),
            FD_0.9_perc = mean(FD_0.9_perc,na.rm=T),
            FD_1.0_perc = mean(FD_1.0_perc,na.rm=T),
            FD_1.1_perc = mean(FD_1.1_perc,na.rm=T),
            FD_0.6N_perc = mean(FD_0.6N_perc,na.rm=T),
            FD_0.7N_perc = mean(FD_0.7N_perc,na.rm=T),
            FD_0.8N_perc = mean(FD_0.8N_perc,na.rm=T),
            FD_0.9N_perc = mean(FD_0.9N_perc,na.rm=T),
            FD_1.0N_perc = mean(FD_1.0N_perc,na.rm=T),
            FD_1.1N_perc = mean(FD_1.1N_perc,na.rm=T),
            FD_0.8_DVARS_2.0_perc = mean(FD_0.8_DVARS_2.0_perc,na.rm=T),
            FD_0.8_DVARS_2.1_perc = mean(FD_0.8_DVARS_2.1_perc,na.rm=T),
            FD_0.9_DVARS_2.0_perc = mean(FD_0.9_DVARS_2.0_perc,na.rm=T),
            FD_0.9_DVARS_2.1_perc = mean(FD_0.9_DVARS_2.1_perc,na.rm=T),
            FD_1.0_DVARS_2.0_perc = mean(FD_1.0_DVARS_2.0_perc,na.rm=T),
            FD_1.0_DVARS_2.1_perc = mean(FD_1.0_DVARS_2.1_perc,na.rm=T),
            FD_0.8_DVARS_2.0N_perc = mean(FD_0.8_DVARS_2.0N_perc,na.rm=T),
            FD_0.8_DVARS_2.1N_perc = mean(FD_0.8_DVARS_2.1N_perc,na.rm=T),
            FD_0.9_DVARS_2.0N_perc = mean(FD_0.9_DVARS_2.0N_perc,na.rm=T),
            FD_0.9_DVARS_2.1N_perc = mean(FD_0.9_DVARS_2.1N_perc,na.rm=T),
            FD_1.0_DVARS_2.0N_perc = mean(FD_1.0_DVARS_2.0N_perc,na.rm=T),
            FD_1.0_DVARS_2.1N_perc = mean(FD_1.0_DVARS_2.1N_perc,na.rm=T)) %>% 
  arrange(-FD_0.8_DVARS_2.0_perc)
```

# print motion files with EUC and artifact
```{r}
df <- joined
subjectList <- as.character(unique(joined$subjectID))
  
motion <- lapply(X=subjectList, df=df, FUN=function(sid, df) {
                           
  adf <- joined %>% filter(subjectID == as.integer(sid)) %>% 
    select(subjectID, task, run, volume, eucTrans, eucRot, eucTransDer, eucRotDer, FD_0.8_DVARS_2.0) %>%
    mutate(FD_0.8_DVARS_2.0 = ifelse(is.na(FD_0.8_DVARS_2.0),0,FD_0.8_DVARS_2.0)) %>%
    group_by(task,run) %>%
    do({
      ungroup(.) 
      saveDF <- select(.,eucTrans, eucRot, eucTransDer, eucRotDer, FD_0.8_DVARS_2.0)
      write.table(saveDF, file=paste0('/Volumes/psych-cog/dsnlab/TAG/nonbids_data/fMRI/fx/motion/wave1/auto-motion-fmriprep/rp_txt/fd0.8_dv2.0_Neighbors/rp_',str_pad(sid,3,pad="0"),'_',.$task[[1]],.$run[[1]],'.txt'), sep='\t', row.name=F, quote=F, col.names=F)
      data.frame()
      }) })
      
str_pad(anim, 6, pad = "0")
    



    do({
      
      write.table(saveDF, file=paste0('/Volumes/psych-cog/dsnlab/TAG/nonbids_data/fMRI/fx/motion/wave1/auto-motion-fmriprep/rp_txt/fd0.8_dv2.0_Neighbors/tag_',sid,'_',.$task[[1]],.$run[[1]],'.txt'), sep='\t', row.name=F, quote=F, col.names=F)
      
      

      ggsave(plot, file = paste0(plotDir,'thresh_combined2/',.$subjectID[[1]],'.pdf'), height = 10, width = 12)  
  
  SID <- sid
  
  
  SID <- sub(".*sub-TAG", "", file) %>% substring(., 1,3)
  task <- sub(".*task-", "", file) %>% substring(., 1,3)
  run <- sub(".*run-0", "", file) %>% substring(., 1,1)  
  motionData <- read.table(file, sep = '\t', header=T)
  motionData <- motionData %>% select(X,Y,Z,RotX,RotY,RotZ)
  write.table(motionData, file=paste0(cas_dir,'nonbids_data/fMRI/fx/motion/wave',wave,'/rawmotion/TAG',SID,'_',task,run,'.txt'), sep='\t', row.name=F, quote=F, col.names=F)
  
  out <- as.data.frame(cbind(SID,task,run))
  })
```

# extra
```{r}
# plot
data.plot = joined %>%
  gather(feature, value, -c(subjectID, wave, task, run, volume))

features = c("FD_5", "FD_6", "FD_7", "FD_8", "DVARS_1.5", "DVARS_1.6", "DVARS_1.7","DVARS_1.8","DVARS_1.9","DVARS_2.0")

data.sub = data.plot %>%
  filter(feature %in% features) %>%
  mutate(sort = ifelse(feature == "FD_5", 1,
                ifelse(feature == "FD_6", 2,
                ifelse(feature == "FD_7", 3,
                ifelse(feature == "FD_8", 4,
                ifelse(feature == "DVARS_1.5", 5,
                ifelse(feature == "DVARS_1.6", 6,
                ifelse(feature == "DVARS_1.7", 7, 
                ifelse(feature == "DVARS_1.8", 8,
                ifelse(feature == "DVARS_1.9", 9,
                ifelse(feature == "DVARS_2.0", 10, NA))))))))))) %>%
  mutate(value=round(as.numeric(value),1),
         task2=paste0(task,run))

nada = data.sub %>% 
  #filter(subjectID==1) %>%
  group_by(subjectID,task) %>%
    do({
      plot = ggplot(., aes(volume, value)) + 
        geom_line(aes(colour = feature), size = .25, show.legend = FALSE) +
        facet_wrap(task2 ~ reorder(feature,sort), ncol = 4, scales = "free") +
        labs(title = .$subjectID[[1]])
      print(plot)
      ggsave(plot, file = paste0(plotDir,'thresh/',.$subjectID[[1]],'_',.$task[[1]],'.pdf'), height = 10, width = 12)
      data.frame()
    })
```

# moving onto building a model based on rough visualization of plots
```{r}

joined <- joined %>% 
  mutate(artifact_fmriprep1 = ifelse(FramewiseDisplacement > 0.8 | stdDVARS > 2.0, 1, 0),
         artifact_fmriprep2 = ifelse(FramewiseDisplacement > 0.8 | stdDVARS > 2.1, 1, 0),
         artifact_fmriprep3 = ifelse(FramewiseDisplacement > 1.0 | stdDVARS > 2.0, 1, 0),
         artifact_fmriprep4 = ifelse(FramewiseDisplacement > 1.0 | stdDVARS > 2.1, 1, 0),
         artifact_fmriprep5 = ifelse(FramewiseDisplacement > 1.2 | stdDVARS > 2.0, 1, 0),
         artifact_fmriprep6 = ifelse(FramewiseDisplacement > 1.2 | stdDVARS > 2.1, 1, 0)) %>%
  mutate(artifact_fmriprep1N = ifelse(artifact_fmriprep1 == 1 | lag(artifact_fmriprep1) == 1 | lead(artifact_fmriprep1) ==1, 1, 0),
         artifact_fmriprep2N = ifelse(artifact_fmriprep2 == 1 | lag(artifact_fmriprep2) == 1 | lead(artifact_fmriprep2) ==1, 1, 0),
         artifact_fmriprep3N = ifelse(artifact_fmriprep3 == 1 | lag(artifact_fmriprep3) == 1 | lead(artifact_fmriprep3) ==1, 1, 0),
         artifact_fmriprep4N = ifelse(artifact_fmriprep4 == 1 | lag(artifact_fmriprep4) == 1 | lead(artifact_fmriprep4) ==1, 1, 0),
         artifact_fmriprep5N = ifelse(artifact_fmriprep5 == 1 | lag(artifact_fmriprep5) == 1 | lead(artifact_fmriprep5) ==1, 1, 0),
         artifact_fmriprep6N = ifelse(artifact_fmriprep6 == 1 | lag(artifact_fmriprep6) == 1 | lead(artifact_fmriprep6) ==1, 1, 0)) %>%
  mutate(artifact_fmriprep1 = as.factor(artifact_fmriprep1),
         artifact_fmriprep2 = as.factor(artifact_fmriprep2),
         artifact_fmriprep3 = as.factor(artifact_fmriprep3),
         artifact_fmriprep4 = as.factor(artifact_fmriprep4),
         artifact_fmriprep5 = as.factor(artifact_fmriprep5),
         artifact_fmriprep6 = as.factor(artifact_fmriprep6),
         artifact_fmriprep1N = as.factor(artifact_fmriprep1N),
         artifact_fmriprep2N = as.factor(artifact_fmriprep2N),
         artifact_fmriprep3N = as.factor(artifact_fmriprep3N),
         artifact_fmriprep4N = as.factor(artifact_fmriprep4N),
         artifact_fmriprep5N = as.factor(artifact_fmriprep5N),
         artifact_fmriprep6N = as.factor(artifact_fmriprep6N))

# visualize new models
data.plot = joined %>%
  gather(feature, value, -c(subjectID, wave, task, run, volume))

features = c("artifact_fmriprep1","artifact_fmriprep1N","artifact_fmriprep2","artifact_fmriprep2N","artifact_fmriprep3","artifact_fmriprep3N","artifact_fmriprep4","artifact_fmriprep4N","artifact_fmriprep5","artifact_fmriprep5N","artifact_fmriprep6","artifact_fmriprep6N")

data.sub = data.plot %>%
  filter(feature %in% features) %>%
  mutate(sort = ifelse(feature == "artifact_fmriprep1", 1,
                ifelse(feature == "artifact_fmriprep1N", 2,       
                ifelse(feature == "artifact_fmriprep2", 3,
                ifelse(feature == "artifact_fmriprep2N", 4,       
                ifelse(feature == "artifact_fmriprep3", 5,
                ifelse(feature == "artifact_fmriprep3N", 6,       
                ifelse(feature == "artifact_fmriprep4", 7,
                ifelse(feature == "artifact_fmriprep4N", 8,
                ifelse(feature == "artifact_fmriprep5", 9,
                ifelse(feature == "artifact_fmriprep5N", 10,
                ifelse(feature == "artifact_fmriprep6", 11,
                ifelse(feature == "artifact_fmriprep6N", 12, NA))))))))))))) %>%
  mutate(value=round(as.numeric(value),1),
         task2=paste0(task,run))

nada = data.sub %>% 
  #filter(subjectID==1) %>%
  group_by(subjectID,task) %>%
    do({
      plot = ggplot(., aes(volume, value)) + 
        geom_line(aes(colour=feature), size = .25, show.legend = FALSE) +
        facet_wrap(task2 ~ reorder(feature,sort), ncol = 4, scales = "free") +
        labs(title = .$subjectID[[1]])
      print(plot)
      ggsave(plot, file = paste0(plotDir,'thresh_combined/',.$subjectID[[1]],'_',.$task[[1]],'.pdf'), height = 10, width = 12)
      data.frame()
    })