---
title: "extractMotion"
author: "Nandi"
date: "28 March 2018"
output: html_document
---

This script will extract the 6 realignment parameters (x, y, z, pitch, roll, yaw) from fmriprep output (*confounds.tsv), in preparation for use in the 'create_eucMotion.R' script.
Output is saved in folder called "rawmotion"

###LOAD PACKAGES AND SET DIRECTORIES
```{r, include=FALSE}
packages <- c("dplyr","tidyr","data.table")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}
lapply(packages, library, character.only = TRUE)

#Set scripts directory
scriptDir = '/Volumes/StorEDGE/WORK/DSN/TAG/TAG_scripts/fMRI/fx/motion/'

#Set fmriprep confounds directory
confoundDir = '/Volumes/psych-cog/dsnlab/TAG/bids_data/derivatives/fmriprep/'

#Set output directory to save rawmotion (make sure this folder exists)
outputDir = '/Volumes/psych-cog/dsnlab/TAG/nonbids_data/fMRI/fx/motion/wave1/rawmotion/'

#Directory with MRI overview document
overviewDoc = '/Volumes/psych-cog/dsnlab/TAG/behavior/MRI/Wave1/MRI_W1overview.csv'
```

###IMPORT FMRIPREP MOTION CONFOUNDS AND SAVE LARGE DF IN SCRIPTS DIR 
```{r, include=FALSE}
motionFiles = list.files(path=confoundDir,pattern='bold_confounds.tsv', recursive = TRUE, full.names=T)

motion <- lapply(X=motionFiles, FUN=function(file) {
  SID <- sub(".*sub-TAG", "", file) %>% substring(., 1,3)
  task <- sub(".*task-", "", file) %>% substring(., 1,3)
  run <- sub(".*run-0", "", file) %>% substring(., 1,1)  
  motionData <- read.table(file, sep = '\t', header=T)
  motionData <- as.data.frame(motionData) %>% 
    mutate(SID = SID,
           task = task,
           run = run) %>%
    rownames_to_column("volume") %>%
    mutate(volume = as.integer(volume)) %>%
    select(SID, task, run, volume, everything())
  })

motionDF <- rbindlist(motion,fill=T)
write.csv(motionDF, paste0(scriptDir,'fmriprep_motion.csv'), row.names = FALSE)
```

###WRITE RAW PARAMS (X,Y,Z,pitch,roll,yaw)
```{r}
rawData <- motionDF %>% 
  group_by(SID,task,run) %>% 
  do({
    ungroup(.) 
    saveDF <- select(.,X,Y,Z,RotX,RotY,RotZ)
    write.table(saveDF, file=paste0(outputDir,'TAG',.$SID[[1]],'_',.$task[[1]],.$run[[1]],'.txt'), sep='\t', row.name=F, quote=F, col.names=F)
      data.frame()
      })
```  

###CHECK THAT ALL SUBKECTS HAVE MOTION DATA 
```{r, include=FALSE}
motionDF2 <- motionDF %>% mutate(task = paste0(task, "_", run)) %>%
  select(SID,task) %>%
  group_by(SID,task) %>%
  summarize(n=n()) %>%
  spread(key=task,value=n) %>%
  ungroup() %>%
  mutate(SID = as.numeric(as.character(SID)))

# import mri overview doc from CAS & get list of everyone who should have fmri data according to masterfile
MRIoverview <- read.csv(overviewDoc,header=T)
MRIoverview <- MRIoverview %>% filter(!check_mri_completed.2.partial.1.full.0.none.==0) %>% select(SID,svc1_num,svc2_num,dsd1_num,dsd2_num)

# check that all subjects have motion data
MRIoverview <- MRIoverview %>% full_join(.,motionDF2) %>% 
  mutate(svc1_missing = ifelse(!svc1_num == 0 & is.na(SVC_1), 1, 0),
         svc2_missing = ifelse(!svc2_num == 0 & is.na(SVC_2), 1, 0),
         dsd1_missing = ifelse(!dsd1_num == 0 & is.na(DSD_1), 1, 0),
         dsd2_missing = ifelse(!dsd2_num == 0 & is.na(DSD_2), 1, 0)) %>%
  arrange(-dsd1_missing, -dsd2_missing, -svc1_missing, -svc2_missing)
```

#check: 5, 28, 253, 218, 140, 233 

