---
title: "update_automotion_manualQC_DSD_waves1_2_3"
author: "Theresa Cheng"
date: "5/26/2021"
output: html_document
---

Adapted from Nandi's update_automotion_with_manualQC.Rmd script. This script formats and names motion confound files for fx models. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load packages
packages <- c("dplyr","tidyr","data.table","tibble","stringr", "rio")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}
lapply(packages, library, character.only = TRUE)
```

```{r set variables, include = FALSE}

#Set variables
study = 'TAG'
subPattern = 'sub-TAG([0-9]{3})'
wavePattern = 'ses-wave([0-9]{1})'
taskPattern = 'task-(DSD|SVC)'
runPattern = 'run-([0-9]{2})'

#Set scripts directory
scriptDir = '~/projects/dsnlab/TAG/TAG_scripts/fMRI/fx/motion/'

#Set motion directories
motionDir <-'/Volumes/psych-cog/dsnlab/TAG/nonbids_data/fMRI/fx/motion/'
wave1_rptxtDir <- paste0(motionDir, 'wave1/auto-motion-fmriprep/rp_txt/DSDwith_manualEdits/renamed_as_bids_subject_ids')
wave123_rptxtDir <- paste0(motionDir, 'waves123/DSD_manualQC/rp_txt')

motionDir2 <- '/Volumes/psych-cog/dsnlab/TAG/bids_data/derivatives/fmriprep_20.2.1_QC/auto_motion/'

# rptxtDir = paste0(motionDir,'rp_txt/')
# classDir = paste0(motionDir,'classification/')

#Set output directory to save final motion regressors (with euclidean and artifact regressors). Make sure this folder exists
outputDir = paste0(motionDir, 'waves123/DSD_manualQC/')
```

# Wave 1 
We will be using the rp_art.txt motion files that were edited for as created by Nandi for the 
```{r import wave1 previous manualQC, include = FALSE}

# setwd(wave1_rptxtDir)

wave1_rptxt_filenames <- list.files(wave1_rptxtDir)

# file.rename(list.files(wave1_rptxtDir)
wave1_rptxt_filenames_edited <- unlist(lapply(str_split(wave1_rptxt_filenames, "_"), function(x) {
  prefix <- x[1]
  suffix <- x[3]
  new_subject_id <- paste0("sub-TAG", x[2], "w01")
  wave1_rptxt_filenames_edited <- paste(prefix, new_subject_id, suffix, sep = "_")
}))

# file.rename(wave1_rptxt_filenames, wave1_rptxt_filenames_edited) # already ran

# rsync these files to the output dir: rsync -aiv /Volumes/psych-cog/dsnlab/TAG/nonbids_data/fMRI/fx/motion/wave1/auto-motion-fmriprep/rp_txt/DSDwith_manualEdits/renamed_as_bids_subject_ids/rp_*.txt /Volumes/psych-cog/dsnlab/TAG/nonbids_data/fMRI/fx/motion/waves123/DSD_manualQC/rp_txt
```

# Waves 2 and 3

## Prepare for manual QC
For this step, read in the manual QC files and identify which Volumes were flagged as trash regressors (participants with auto-motion trash regressors comprising 15-20% of the run only) -- this is to facilitate the speed and ease of the manual QC. 
```{r export manualQC files}

# read in subject info for those needing manual QC
subject_ids_for_manualQC <- import(paste0(scriptDir, "subject_ids_for_manualQC_waves2and3.txt"), header = TRUE)

motionQC_df <- data.frame(subject_id = as.character(),
                          run_num = as.integer(),
                          trash_volumes = integer())

# read in
for (i in 1:nrow(subject_ids_for_manualQC)){
  subject_id <- subject_ids_for_manualQC$subject_id[i]
  wave_num <- subject_ids_for_manualQC$wave_num[i]
  run_num <- subject_ids_for_manualQC$run_num[i]
  
  rptxt <- import(paste0(motionDir2, "sub-", subject_id, "_ses-", wave_num, "_task-DSD_run-", run_num, "_desc-motion_regressors.txt"))

  motionQC_this_subject <- data.frame(subject_id = rep(subject_id, length(which(rptxt$trash == 1))),
                                      run_num = rep(run_num, length(which(rptxt$trash == 1))),
                                      trash_volumes = which(rptxt$trash == 1))
    
  motionQC_df <- rbind(motionQC_df, motionQC_this_subject)
}

# write.csv(motionQC_df, paste0(outputDir, "manualQC_template_w_auto-motion_trash_regressor.csv"))
```

## Edit wave 2 and 3 files
For participants that did not need manual QC edits, remove the header and move to the correct location only. 
```{r }

automotion_rptxt_filenames <- list.files(motionDir2)

output <- lapply(str_split(automotion_rptxt_filenames, "_"), function(x) {
  subject_id <- x[1]
  ses <- x[2]
  run_num <- substr(x[4], 5, 5)
  
  target_filename <- paste0("rp_", subject_id, "_DSD", run_num, ".txt")
  
  data.frame(target_filename = unlist(target_filename), 
             wave = unlist(ses))
})

output_df <- do.call(rbind,output)
output_df$original_filename <- automotion_rptxt_filenames
output_df <- output_df[-nrow(output_df), ] # remove last row

# rename wave 2 and 3 files only within the test folder
setwd(paste0(motionDir2, "test"))

apply(output_df, 1, function(x){
  
  target_filename <- x[1]
  wave <- x[2]
  original_filename <- x[3]
  
  # if (wave != "ses-wave1"){
  #   file.rename(original_filename, target_filename)
  # }
})

# remove headers
apply(output_df, 1, function(x){
  
  target_filename <- x[1]
  wave <- x[2]
  original_filename <- x[3]
  
  if (wave != "ses-wave1"){
    
    rptxt_orig <- import(target_filename)
    #write.table(rptxt_orig, target_filename, col.names = FALSE, row.names = FALSE)
  }
})

# now rsync files beginning with rp* into output directory: rsync -aiv /Volumes/psych-cog/dsnlab/TAG/bids_data/derivatives/fmriprep_20.2.1_QC/auto_motion/test/rp_*.txt /Volumes/psych-cog/dsnlab/TAG/nonbids_data/fMRI/fx/motion/waves123/DSD_manualQC/rp_txt
```

## Overwrite trash regressors with manual QC
For this step, read in the manual QC edits and overwrite the trash regressor with these more accurate values.
```{r overwrite with manual QC edits}

subject_ids_for_manualQC_replacement <- import(paste0(scriptDir, "subject_ids_for_manualQC_replacement.txt"), header = TRUE)

manualQC_override <- import(paste0(motionDir, 'waves123/DSD_manualQC/DSD_motionQC_waves2and3_edited_to_keep.csv'))
manualQC_override$Volume <- manualQC_override$Volume_minus1 + 1

# there is only one participant that needs manual QC replacement, so 
subject_id_manualQC_edit <- subject_ids_for_manualQC_replacement$subject_id[1]
wave_num_manualQC_edit <- subject_ids_for_manualQC_replacement$wave_num[1]
run_num_manualQC_edit <- subject_ids_for_manualQC_replacement$run_num[1]

rptxt_orig <- import(paste0(motionDir2, "sub-", subject_id_manualQC_edit, "_ses-", wave_num_manualQC_edit, "_task-DSD_run-", run_num_manualQC_edit, "_desc-motion_regressors.txt"))
# rptxt_orig$volume_num <- 

rptxt_edited <- rptxt_orig %>% 
  mutate(trash = ifelse(rownames(.) %in%  manualQC_override$Volume, 1, 0))

#write.table(rptxt_edited, paste0(outputDir, "rp_txt/rp_sub-", subject_id_manualQC_edit, "_DSD", run_num_manualQC_edit, ".txt"), col.names = FALSE, row.names = FALSE)
```

