---
title: "update_manualQC"
author: "Nandi"
date: "29 June 2018"
output: html_document
---

This is the final motion script for DSD, which updates the automated trash regressor with manual QC that was completed for participants with 15-25% trash regressors.

###LOAD PACKAGES AND SET DIRECTORIES
```{r, include=FALSE}
packages <- c("dplyr","tidyr","data.table","tibble","stringr")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}
lapply(packages, library, character.only = TRUE)

#Set variables
study = 'TAG'
subPattern = 'sub-TAG([0-9]{3})'
wavePattern = 'ses-wave([0-9]{1})'
taskPattern = 'task-(DSD|SVC)'
runPattern = 'run-([0-9]{2})'

#Set scripts directory
scriptDir = '/Volumes/StorEDGE/WORK/DSN/TAG/TAG_scripts/fMRI/fx/motion/'

#Set output directory to save final motion regressors (with euclidean and artifact regressors). Make sure this folder exists
motionDir = '/Volumes/psych-cog/dsnlab/TAG/nonbids_data/fMRI/fx/motion/wave1/auto-motion-fmriprep/rp_txt/with_manualEdits/'

#Set artifact threshold
neighbor = "FALSE"
```

###IMPORT "ALL MOTION" CSV SAVED BY PRIOR AUTO-MOTION-FMRIPREP SCRIPT 
```{r}
motion <- read.csv(paste0(scriptDir,'output/all_motion.csv')) 
motion <- motion %>%
  mutate(sub.run.vol = paste(SID, task, run, volume, sep = "_")) %>%
  filter(task=="DSD")
```

###IMPORT MANUAL MOTION QC
```{r}
coded = read.csv('/Volumes/psych-cog/dsnlab/TAG/nonbids_data/fMRI/fx/motion/wave1/auto-motion-fmriprep/rp_txt/fd0.8_dv2.0_noNeighbors/DSD_motionQC.csv')
coded <- coded %>%
  extract("Run", c("task", "run"), "([A-Z]{3})([0-9]{1})") %>%
  mutate(run = as.integer(run),
         SID = as.integer(gsub("[^0-9\\.]", "", Subject)),
         volume = Volume+1) %>%
  mutate(sub.run.vol = paste(SID, task, run, volume, sep = "_")) %>%
  mutate(manual_artifact = 1,
         manual_artifact = as.factor(manual_artifact))
```

###UPDATE "ALL MOTION" DF BASED ON MANUAL QC 
```{r}
motion <- motion %>% 
  mutate(artifact2 = ifelse(sub.run.vol %in% coded$sub.run.vol, 1, artifact),
         artifact_N2 = ifelse(sub.run.vol %in% coded$sub.run.vol, 1, artifact_N))
```

###PRINT MOTION FILES
```{r}
subjectList <- as.character(unique(motion$SID))

if (neighbor) {
  motion$artifact = motion$artifact_N
  } else {}

motion_final <- lapply(X=subjectList, df=motion, FUN=function(sid, df) {
                           
  adf <- motion %>% filter(SID == as.integer(sid)) %>% 
    select(SID, task, run, volume, eucTrans, eucRot, eucTransDer, eucRotDer, artifact) %>%
    group_by(task,run) %>%
    do({
      ungroup(.) 
      saveDF <- select(.,eucTrans, eucRot, eucTransDer, eucRotDer, artifact)
      write.table(saveDF, file=paste0(motionDir,'rp_',str_pad(sid,3,pad="0"),'_',.$task[[1]],.$run[[1]],'.txt'), sep='\t', row.name=F, quote=F, col.names=F)
      data.frame()
      }) })
```




###PRINT DSD MOTION SUMMARY
```{r}
#summarise artifacts in each subject in DSD. first load DSD overview and limit sample to 146 participants with DSD pre motion.

dsd_overview <- read.csv('~/Desktop/dsd_overview.csv',header=T)

DSDids <- dsd_overview %>% filter(Withdrawn_W1==0) %>% filter(W1S2_Completed==1) %>% filter(!check_mri_completed.2.partial.1.full.0.none.==0) %>% filter(dsd_completed==2) %>% filter(is.na(technical_missing)) %>% filter(is.na(participant_error)) %>% mutate(subjectID=SID) %>% select(subjectID)

summaryDF_dsd <- joined %>% filter(SID %in% DSDids$subjectID) %>% filter(task=="DSD") %>%
  select(SID,run,artifact,artifact_N) %>% group_by(SID) %>% 
  summarise(artifact=100*(sum(artifact)/n()),
            artifact_N=100*(sum(artifact_N/n())),
            N = n()) %>%
  arrange(-artifact)

write.csv(summaryDF_dsd,paste0(motionDir,'summary_DSD_Motion.csv'))
```
