---
title: "TAG Cleaning Saliva Hormone Data"
author: "Nandi"
date: "28 March 2018"
output: html_document
---

```{r, include=FALSE}
#LOAD PACKAGES AND SET DIRECTORIES

packages <- c("ggplot2","tidyr","stringr","knitr","corrplot","data.table","readxl","gridExtra","dplyr", "psych","kableExtra","lavaan")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}
lapply(packages, library, character.only = TRUE)

cas_dir <- '/Volumes/psych-cog/dsnlab/TAG/'
saliva_dir <- paste0(cas_dir,'behavior/Saliva/Wave1')
options(digits=3)

in_dir <- '~/Downloads/' #to be updated once Saliva Overview Doc is finished.
```


```{r, include=FALSE}
#Set exclusion critera

#Remove outliers?
removeOut="TRUE"
#Remove high CV?
removeCV="FALSE"
#Remove high 450 CV?
remove450CV="FALSE"
#Remove hair confounds?
removeConfounds="FALSE"
```

###IMPORT AND CLEAN SALIVA DATA
```{r, echo=FALSE, message=FALSE, warning=FALSE, results="asis", fig.height=4, fig.width=4}
###IMPORT & CLEAN CONCENTRATIONS 
#import dataframe for each hormone, create SID as 3 digit numeric factor (i.e. "001"), combine all three hormones in one dataframe. 
Sal_DHEA <- read_xlsx(paste0(saliva_dir,'/TAG_SALIVA_Master_File.xlsx'), sheet=4)
Sal_TEST <- read_xlsx(paste0(saliva_dir,'/TAG_SALIVA_Master_File.xlsx'), sheet=8)
Sal_EST <- read_xlsx(paste0(saliva_dir,'/TAG_SALIVA_Master_File.xlsx'), sheet=12)

Sal_DHEA <- Sal_DHEA %>% 
  mutate(Concentration = ifelse(Concentration =='?????',1,Concentration)) %>%
  mutate(SID = as.factor(round(as.numeric(ID),2)),
         sal_DHEA = round(as.numeric(Concentration),3)) %>%
  select(SID,sal_DHEA) %>%
  replace_na(list(sal_DHEA = "missing")) %>%
  filter(!is.na(SID)) %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID),
         week = as.factor(week))

Sal_TEST <- Sal_TEST %>% 
  mutate(Concentration = ifelse(Concentration =='?????',4,Concentration)) %>%
  mutate(SID = as.factor(round(as.numeric(ID),2)),
         sal_TEST = round(as.numeric(Concentration),3)) %>%
  select(SID,sal_TEST) %>%
  replace_na(list(sal_TEST = "missing")) %>%
  filter(!is.na(SID)) %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID),
         week = as.factor(week))

Sal_EST <- Sal_EST %>% 
  mutate(Concentration = ifelse(Concentration =='?????',0.1,Concentration)) %>%
  mutate(SID = as.factor(round(as.numeric(ID),2)),
         sal_EST = round(as.numeric(Concentration),3)) %>%
  select(SID,sal_EST) %>%
  replace_na(list(sal_EST = "missing")) %>%
  filter(!is.na(SID)) %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID),
         week = as.factor(week))

Saliva <- Sal_DHEA %>% full_join(.,Sal_TEST) %>% full_join(.,Sal_EST) %>%
  mutate(ID = paste(SID,week,sep="_"))

###IMPORT & CLEAN COV
Sal_DHEA_CV <- read_xlsx(paste0(saliva_dir,'/TAG_SALIVA_Master_File.xlsx'), sheet=1)
Sal_TEST_CV <- read_xlsx(paste0(saliva_dir,'/TAG_SALIVA_Master_File.xlsx'), sheet=5)
Sal_EST_CV <- read_xlsx(paste0(saliva_dir,'/TAG_SALIVA_Master_File.xlsx'), sheet=9)

Sal_DHEA_CV <- Sal_DHEA_CV %>% 
  filter(!is.na(Name)) %>%
  select(Name,`CV (%)`) %>%
  rename(ID = Name,
         DHEA_CV = `CV (%)`) %>%
  mutate(SID = as.factor(round(as.numeric(ID),2)),
         DHEA_CV = round(as.numeric(DHEA_CV),3)) %>%
  select(SID,DHEA_CV) %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID),
         week = as.factor(week)) %>%
  filter(!is.na(SID))

Sal_TEST_CV <- Sal_TEST_CV %>% 
  filter(!is.na(Name)) %>%
  select(Name,`CV (%)`) %>%
  rename(ID = Name,
         TEST_CV = `CV (%)`) %>%
  mutate(SID = as.factor(round(as.numeric(ID),2)),
         TEST_CV = round(as.numeric(TEST_CV),3)) %>%
  select(SID,TEST_CV) %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID),
         week = as.factor(week)) %>%
  filter(!is.na(SID))

Sal_EST_CV <- Sal_EST_CV %>% 
  filter(!is.na(Name)) %>%
  select(Name,`CV (%)`) %>%
  rename(ID = Name,
         EST_CV = `CV (%)`) %>%
  mutate(SID = as.factor(round(as.numeric(ID),2)),
         EST_CV = round(as.numeric(EST_CV),3)) %>%
  select(SID,EST_CV) %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID),
         week = as.factor(week)) %>%
  filter(!is.na(SID))

Saliva_CV <- Sal_DHEA_CV %>% full_join(.,Sal_TEST_CV) %>% full_join(.,Sal_EST_CV) %>%
  mutate(ID = paste(SID,week,sep="_"))

#Read in replicates
Sal_DHEA_CV_rep <- read_xlsx(paste0(saliva_dir,'/TAG_SALIVA_Master_File.xlsx'), sheet=3)
Sal_TEST_CV_rep <- read_xlsx(paste0(saliva_dir,'/TAG_SALIVA_Master_File.xlsx'), sheet=7)
Sal_EST_CV_rep <- read_xlsx(paste0(saliva_dir,'/TAG_SALIVA_Master_File.xlsx'), sheet=11)

Sal_DHEA_CV_rep <- Sal_DHEA_CV_rep %>%
  rename(SID = Name,
         rep1 = TAG_2017.07.18_DHEA_Yoojin.xlsx,
         rep2 = X__1,
         CV2 = X__2,
         notes = X__3) %>%
  mutate(rep1 = as.numeric(rep1)) %>%
  filter(!is.na(rep1)) %>%
  mutate(SID = as.factor(round(as.numeric(SID),2))) %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID),
         week = as.factor(week)) %>%
  filter(!(SID == "Name"))

Sal_TEST_CV_rep <- Sal_TEST_CV_rep %>% 
  rename(SID = Name,
         rep1 = tag_06.18.2017_testo_tray2_ellen.xlsx,
         rep2 = X__1,
         CV2 = X__2,
         notes = X__3) %>%
  mutate(rep1 = as.numeric(rep1)) %>%
  filter(!is.na(rep1)) %>%
  mutate(SID = as.factor(round(as.numeric(SID),2))) %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID),
         week = as.factor(week)) %>%
  filter(!(SID == "Name"))

Sal_EST_CV_rep <- Sal_EST_CV_rep %>% 
  rename(SID = Name,
         rep1 = TAG_06.18.2017_Estradiol_Tray2_Olivia.xlsx,
         rep2 = X__1,
         CV2 = X__2,
         notes = X__3) %>%
  mutate(rep1 = as.numeric(rep1)) %>%
  filter(!is.na(rep1)) %>%
  mutate(SID = as.factor(round(as.numeric(SID),2))) %>%
  separate(SID, into =c("SID","week")) %>%
  mutate(SID = str_pad(SID, 3, pad = "0")) %>%
  mutate(SID = as.factor(SID),
         week = as.factor(week)) %>%
  filter(!(SID == "Name"))
```

###SUMMARIES
```{r, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
Saliva_long <- gather(Saliva, hormone, concentration, c(sal_DHEA,sal_TEST,sal_EST), factor_key=TRUE)

#Missing samples (i.e. assayed for some hormones, but not others)
Saliva_missingIDs <- Saliva_long %>% 
  select(-ID) %>% 
  mutate(missing = ifelse(is.na(concentration),1,0)) %>%
  filter(missing == 1)
Saliva_missing <- Saliva_missingIDs %>%
  select(-concentration) %>%
  group_by(hormone) %>% 
  summarise(missing = sum(missing))

#Of the assayed samples, how many had missing concentrations
Saliva_assayed <- Saliva_long %>% 
  select(-ID) %>% 
  filter(!is.na(concentration)) %>%
  mutate(concentration = as.numeric(concentration)) %>%
  group_by(SID,hormone) %>% 
  summarise(Samples = n(),
            Conc = sum(!is.na(concentration)),
            NoConc = sum(is.na(concentration))) %>% ungroup() %>%
  mutate(Missing = if_else(NoConc > 0,1,0))

#Number of samples per subject (filtering by DHEA as there were no missing samples, unlike TEST)
Saliva_summaryPP <- Saliva_assayed %>% filter(hormone == "sal_DHEA") %>% 
  group_by(Samples) %>% 
  summarise(N = n())

#Number of samples with and without concentrations
Saliva_summary <- Saliva_assayed %>% 
  group_by(hormone,NoConc) %>% 
  summarise(N = n())
```

####Samples sent
```{r, echo=FALSE, message=FALSE, warning=FALSE, results="asis", fig.height=4, fig.width=4}
Saliva_long <- Saliva_long %>% 
  mutate(missing = if_else(concentration == "missing",1,0))

cat('No of Subjects: ') 
cat(length(unique(Saliva$SID)))  
writeLines("\n")
cat('No of Samples: ') 
cat(length((Saliva$SID)))
writeLines("\n")
cat('No of Samples per Subject: ') 
kable(Saliva_summaryPP, "html", align='c') %>%
kable_styling(full_width = F, position = "left", font_size = 12)
```

####Missing concentrations - unable to assay
```{r, echo=FALSE, message=FALSE, warning=FALSE, results="asis", fig.height=4, fig.width=4}
cat("\nNumber of samples ")
writeLines("\n")
cat("\nDHEA: ")
cat(nrow(Saliva_long %>% filter(hormone == "sal_DHEA" & missing == 1) %>% select(missing)))
writeLines("\n")
cat('TEST: \n')
cat(nrow(Saliva_long %>% filter(hormone == "sal_TEST" & missing == 1) %>% select(missing)))
writeLines("\n")
cat('EST: \n')
cat(nrow(Saliva_long %>% filter(hormone == "sal_EST" & missing == 1) %>% select(missing)))

writeLines("\n")
cat("Broken down by number of missing samples per subject")
kable(Saliva_summary, "html", align='c') %>%
kable_styling(full_width = F, position = "left", font_size = 12)
```

####Checking for outliers (of mean of duplicates)
```{r, echo=FALSE, message=FALSE, warning=FALSE, results="asis", fig.height=4, fig.width=4}
Saliva_long <- Saliva_long %>%
  mutate(concentration = as.numeric(concentration))

hist(subset(Saliva_long, hormone == "sal_DHEA")$concentration, main="", xlab="DHEA")
#abline(v=600,col="red")
writeLines("\n")
hist(subset(Saliva_long, hormone == "sal_TEST")$concentration, main="", xlab="TEST")
#abline(v=200,col="red")
writeLines("\n")
hist(subset(Saliva_long, hormone == "sal_EST")$concentration, main="", xlab="EST")
#abline(v=3,col="red")
writeLines("\n")

#calculate number of outliers based on visual inspection cut-offs
Saliva_long <- Saliva_long %>%
  mutate(out = if_else(hormone == "sal_DHEA" & concentration > 600, 1, 
                       if_else(hormone == "sal_TEST" & concentration > 200, 1, 
                               if_else(hormone == "sal_EST" & concentration > 3, 1,0)))) 

cat("\n*Number of outlier samples*")
writeLines("\n")
cat("\nDHEA: ")
cat(nrow(Saliva_long %>% filter(hormone == "sal_DHEA" & out == 1) %>% select(out)))
writeLines("\n")
cat("\nTEST: ")
cat(nrow(Saliva_long %>% filter(hormone == "sal_TEST" & out == 1) %>% select(out)))
writeLines("\n")
cat("\nEST: ")
cat(nrow(Saliva_long %>% filter(hormone == "sal_EST" & out == 1) %>% select(out)))
writeLines("\n")
```

####Check intra-assay CV
```{r, echo=FALSE, message=FALSE, warning=FALSE, results="asis", fig.height=4, fig.width=4}
DHEA_CV<-ggplot(Saliva_CV, aes(x=DHEA_CV)) +
  geom_histogram(color="black",fill="white") +
  #geom_vline(xintercept=30,linetype="dashed",colour="red")
DHEA_CV
DHEA_CV_exc <- Saliva_CV %>% filter(DHEA_CV > 30) %>% select(ID)

TEST_CV<-ggplot(Saliva_CV, aes(x=TEST_CV)) +
  geom_histogram(color="black",fill="white") +
  #geom_vline(xintercept=30,linetype="dashed",colour="red")
TEST_CV
TEST_CV_exc <- Saliva_CV %>% filter(TEST_CV > 30) %>% select(ID)

EST_CV<-ggplot(Saliva_CV, aes(x=EST_CV)) +
  geom_histogram(color="black",fill="white") +
  #geom_vline(xintercept=30,linetype="dashed",colour="red")
EST_CV
EST_CV_exc <- Saliva_CV %>% filter(EST_CV > 30) %>% select(ID)

#calculate number of outliers based on high intra-assayCV
Saliva_long <- Saliva_long %>%
  mutate(highCV = if_else(hormone == "sal_DHEA" & ID %in% DHEA_CV_exc$ID, 1,
                          ifelse(hormone == "sal_TEST" & ID %in% TEST_CV_exc$ID, 1,
                                 ifelse(hormone == "sal_EST" & ID %in% EST_CV_exc$ID, 1, 0))))

writeLines("\n")
cat("\n*Number of high CVs*")
writeLines("\n")
cat("\nDHEA: ")
cat(nrow(Saliva_long %>% filter(hormone == "sal_DHEA" & highCV == 1) %>% select(highCV)))
writeLines("\n")
cat("\nTEST: ")
cat(nrow(Saliva_long %>% filter(hormone == "sal_TEST" & highCV == 1) %>% select(highCV)))
writeLines("\n")
cat("\nEST: ")
cat(nrow(Saliva_long %>% filter(hormone == "sal_EST" & highCV == 1) %>% select(highCV)))
writeLines("\n")
```

```{r, include=FALSE, message=FALSE}
#IMPORT SESSION DATES AND CALCULATE INTERVALS BETWEEN SALIVA SAMPLES

#import session 1 and 2 dates
session_df <- read.csv(paste0(in_dir,'/TAGIDENTIFIERS_DATA_2018-01-26_1905.csv'), header=T)

session_dates <- session_df %>% 
  filter(!subject_spit_id=="TAG_001P") %>%
  mutate(SID=gsub("[^0-9\\.]", "", subject_spit_id)) %>%
  filter(redcap_event_name=="wave_1_scheduling_arm_1") %>%
  select(SID,sa_date,sb_date) %>%
  mutate(sa_date=as.Date(sa_date),
         sb_date=as.Date(sb_date))

#import saliva sample dates
saliva_df <- read.csv(paste0(in_dir,'/TAGDATADeidentified_DATA_2018-01-26_1904.csv'), header=T)

saliva_dates <- saliva_df %>% 
  filter(!subject_spit_id=="TAG_001P") %>%
  mutate(SID=gsub("[^0-9\\.]", "", subject_spit_id)) %>%
  filter(redcap_event_name=="wave_1_session_b_arm_1") %>%
  select(SID,s1_doc,s2_doc,s3_doc,s4_doc,s5_doc,s6_doc,s7_doc) %>%
  mutate(s1_sdate = as.Date(s1_doc, "%Y-%m-%d"),
         s2_sdate = as.Date(s2_doc, "%Y-%m-%d"),
         s3_sdate = as.Date(s3_doc, "%Y-%m-%d"),
         s4_sdate = as.Date(s4_doc, "%Y-%m-%d"),
         s5_sdate = as.Date(s5_doc, "%Y-%m-%d"),
         s6_sdate = as.Date(s6_doc, "%Y-%m-%d"),
         s7_sdate = as.Date(s7_doc, "%Y-%m-%d")) %>%
  select(-s1_doc,-s2_doc,-s3_doc,-s4_doc,-s5_doc,-s6_doc,-s7_doc)

#combine session and saliva dates
dates <- session_dates %>% full_join(., saliva_dates) %>%
  filter(SID %in% paste0(Saliva_long$SID)) %>%
  mutate(int1 = as.numeric(difftime(s1_sdate, sa_date, units = "days")),
         int2 = as.numeric(difftime(s2_sdate, s1_sdate, units = "days")),
         int3 = as.numeric(difftime(s3_sdate, s2_sdate, units = "days")),
         int4 = as.numeric(difftime(s4_sdate, s3_sdate, units = "days")),
         int5 = as.numeric(difftime(s5_sdate, s4_sdate, units = "days")),
         int6 = as.numeric(difftime(s6_sdate, s5_sdate, units = "days")),
         int7 = as.numeric(difftime(s7_sdate, s6_sdate, units = "days")),
         totLength = as.numeric(difftime(sb_date, sa_date, units = "days"))) #totLength = time between session 1 and 2
dates <- dates %>% 
  rowwise() %>% 
  mutate(intSum = sum(int1,int2,int3,int4,int5,int6,int7,na.rm=T), #intSum = time between session 1 and final sample
         intFinal = totLength - intSum) #intFinal = time between final sample and session 2.
```

```{r, include=FALSE, message=FALSE}
#PLOT SALIVA INTERVALS AND DETERMINE WHICH SAMPLES TO EXCLUDE
dates_long <- dates %>% 
  select(SID,s1_sdate:s7_sdate,sb_date) %>% gather(., week, sample, c(s1_sdate,s2_sdate,s3_sdate,s4_sdate,s5_sdate,s6_sdate,s7_sdate,sb_date), factor_key=TRUE) %>%
  mutate(sample_bin = ifelse(!is.na(sample), 1,0)) %>%
  arrange(SID) %>%
  filter(sample_bin == 1) %>%
  group_by(SID) %>% mutate(sample_num = row_number()) %>%
  mutate(interval = as.numeric(sample - lag(sample)))

plot1 <- dates_long[1:200,]
plot2 <- dates_long[201:400,]
plot3 <- dates_long[401:600,]

fills <- c("blue","orange","green","red","grey","yellow","purple","black")
colors <- c("grey","grey","grey","grey","grey","grey","grey","grey",NA)

fig1 <- ggplot(plot1, aes(SID, interval), group=week) +
  geom_bar(aes(fill= week), stat="identity", width=0.2) +
  geom_point(aes(colour = week), position = "stack") +
  coord_flip() +
  scale_fill_manual(values = fills) + 
  scale_colour_manual(values = colors)
fig1

fig2 <- ggplot(plot2, aes(SID, interval), group=week) +
  geom_bar(aes(fill= week), stat="identity", width=0.2) +
  geom_point(aes(colour = week), position = "stack") +
  coord_flip() +
  scale_fill_manual(values = fills) + 
  scale_colour_manual(values = colors)
fig2

fig3 <- ggplot(plot3, aes(SID, interval), group=week) +
  geom_bar(aes(fill= week), stat="identity", width=0.2) +
  geom_point(aes(colour = week), position = "stack") +
  coord_flip() +
  scale_fill_manual(values = fills) + 
  scale_colour_manual(values = colors)
fig3

#BASED ON PLOTS:
#inclusionary critera:
#must have at least 3 samples within 40 days preceding session 2. 
#note: not plotting or using interval between session1 and sample 1 (int1) as it is not of importance to the quesiton of saliva/hair/puberty correlations.

#overall exclusions
missing_dates = c("028","042","070","071")
#funky dates
exclusions = c("029","057","067","091","143","152","080","130","169")
#exclude first sample alone (i.e. remove interval between 1st and 2nd sample; int2)
exclusions1 = c("014","027","038","051","068")
```

####Excluded subjects based on funky dates 
```{r, echo=FALSE, message=FALSE, warning=FALSE, results="asis", fig.height=4, fig.width=4}
plot_exc <- dates_long %>% arrange(SID) %>% filter(SID %in% paste0(c(exclusions,missing_dates))) %>%
  filter(!SID == "067") 

cat('Excluded N: ') 
cat(length(unique(plot_exc$SID))+1)
writeLines("\n")
fig4 <- ggplot(plot_exc, aes(SID, interval), group=week) +
  geom_bar(aes(fill= week), stat="identity", width=0.2) +
  geom_point(aes(colour = week), position = "stack") +
  coord_flip() +
  scale_fill_manual(values = fills) + 
  scale_colour_manual(values = colors)
fig4
writeLines("\n")
cat('Did not plot 067 as they were throwing axis off') 
```

####Included subjects with normal dates
Inclusionary critera: must have at least 3 samples within 40 days preceding session 2.  
Note: not plotting or using interval between session1 and sample 1 as it is not of importance to the quesiton of saliva/hair/puberty correlations.  
```{r, echo=FALSE, message=FALSE, warning=FALSE, results="asis", fig.height=10, fig.width=7}
#Filter dataframe dataset based on prior exclusions and also those with or more 3 samples 

dates_long$sample[which(dates_long$SID == "062" & dates_long$week == "sb_date")] <- "2016-08-16"
dates_long <- dates_long %>% arrange(SID) %>% 
  filter(!SID %in% paste0(missing_dates)) %>% 
  filter(!SID %in% paste0(exclusions)) %>%
  mutate(sample=replace(sample,SID %in% paste0(exclusions1) & week == "s1_sdate", NA)) %>% 
  filter(!is.na(sample)) %>%
  select(-sample_num,-interval) %>%
  group_by(SID) %>% mutate(sample_num = row_number()) %>%
  mutate(interval = as.numeric(sample - lag(sample)))

summaryN <- dates_long %>% 
  filter(!week == "sb_date") %>%
  select(-interval) %>% group_by(SID) %>%
  summarise(n = n()) %>%
  filter(n >2)

dates_long <- dates_long %>% 
  filter(SID %in% paste0(summaryN$SID))

fills <- c("blue","orange","green","red","grey","yellow","purple","black")
colors <- c("grey","grey","grey","grey","grey","grey","grey","grey",NA)

fig <- ggplot(dates_long, aes(SID, interval), group=week) +
  geom_bar(aes(fill= week), stat="identity", width=0.2) +
  geom_point(aes(colour = week), position = "stack") +
  coord_flip() +
  scale_fill_manual(values = fills) + 
  scale_colour_manual(values = colors)
fig

#Update saliva dataframe with dates-based exclusions
Saliva_long <- Saliva_long %>% 
  mutate(dateExc = if_else(SID %in% summaryN$SID, 0, 1))
```

```{r, include = FALSE}
#UPDATE DATAFRAME WITH EXCLUSIONS
#replace outlier values with NA
if (removeOut) {
  Saliva_long <- Saliva_long %>%
    mutate(concentration = replace(concentration, out == 1, NA))
  }

#replace intrassay CV > 30 with NA
if (removeCV) {
  Saliva_long <- Saliva_long %>%
    mutate(concentration = replace(concentration, highCV == 1, NA))
  }

#replace funky dates with NA
if (removeCV) {
  Saliva_long <- Saliva_long %>%
    mutate(concentration = replace(concentration, dateExc == 1, NA))
  }
```

```{r, include=FALSE}
# Create wide format dataset for saliva
Saliva_wide <- Saliva_long %>% select(SID,week,hormone,concentration) %>%
  filter(!is.na(concentration)) %>%
  dcast(., SID ~ hormone + week, value.var="concentration") %>%
  mutate(sal_DHEA_1 = as.numeric(sal_DHEA_1),
         sal_DHEA_2 = as.numeric(sal_DHEA_2),
         sal_DHEA_3 = as.numeric(sal_DHEA_3),
         sal_DHEA_4 = as.numeric(sal_DHEA_4),
         sal_DHEA_5 = as.numeric(sal_DHEA_5),
         sal_DHEA_6 = as.numeric(sal_DHEA_6),
         sal_DHEA_7 = as.numeric(sal_DHEA_7),
         sal_TEST_1 = as.numeric(sal_TEST_1),
         sal_TEST_2 = as.numeric(sal_TEST_2),
         sal_TEST_3 = as.numeric(sal_TEST_3),
         sal_TEST_4 = as.numeric(sal_TEST_4),
         sal_TEST_5 = as.numeric(sal_TEST_5),
         sal_TEST_6 = as.numeric(sal_TEST_6),
         sal_TEST_7 = as.numeric(sal_TEST_7),
         sal_EST_1 = as.numeric(sal_EST_1),
         sal_EST_2 = as.numeric(sal_EST_2),
         sal_EST_3 = as.numeric(sal_EST_3),
         sal_EST_4 = as.numeric(sal_EST_4),
         sal_EST_5 = as.numeric(sal_EST_5),
         sal_EST_6 = as.numeric(sal_EST_6),
         sal_EST_7 = as.numeric(sal_EST_7)) %>%
  rowwise() %>% 
  mutate(nDHEA = sum(!is.na(c(sal_DHEA_1,sal_DHEA_2,sal_DHEA_3,sal_DHEA_4,sal_DHEA_5,sal_DHEA_6,sal_DHEA_7))),
         nTEST = sum(!is.na(c(sal_TEST_1,sal_TEST_2,sal_TEST_3,sal_TEST_4,sal_TEST_5,sal_TEST_6,sal_TEST_7))),
         nEST = sum(!is.na(c(sal_EST_1,sal_EST_2,sal_EST_3,sal_EST_4,sal_EST_5,sal_EST_6,sal_EST_7)))) %>%
  mutate(meanDHEA = mean(c(sal_DHEA_1,sal_DHEA_2,sal_DHEA_3,sal_DHEA_4,sal_DHEA_5,sal_DHEA_6,sal_DHEA_7), na.rm=T),
         meanTEST = mean(c(sal_TEST_1,sal_TEST_2,sal_TEST_3,sal_TEST_4,sal_TEST_5,sal_TEST_6,sal_TEST_7), na.rm=T),
         meanEST = mean(c(sal_EST_1,sal_EST_2,sal_EST_3,sal_EST_4,sal_EST_5,sal_EST_6,sal_EST_7), na.rm=T)) %>%
  mutate(meanDHEA = replace(meanDHEA, (nDHEA<3), NA),
         meanTEST = replace(meanTEST, (nTEST<3), NA),
         meanEST = replace(meanEST, (nEST<3), NA)) 
```

####Final dataset post exclusions 
After accounting for missing concentrations, outliers, funky dates, etc
```{r, echo=FALSE, message=FALSE, warning=FALSE, results="asis", fig.height=4, fig.width=4}
cat("\nNumber of mean (across dates) samples ")
writeLines("\n")
cat("\nDHEA: ")
cat(summary(!is.na((Saliva_wide$meanDHEA)))[3])
writeLines("\n")
cat('TEST: \n')
cat(summary(!is.na((Saliva_wide$meanTEST)))[3])
writeLines("\n")
cat('EST: \n')
cat(summary(!is.na((Saliva_wide$meanEST)))[3])
```

```{r,echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
#write final output for analyses
```

###Calcualte Inter-assay CV
```{r, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
Sal_DHEA_interCV <- read_xlsx(paste0(saliva_dir,'/TAG_SALIVA_Master_File.xlsx'), sheet=1)
Sal_TEST_interCV <- read_xlsx(paste0(saliva_dir,'/TAG_SALIVA_Master_File.xlsx'), sheet=5)
Sal_EST_interCV <- read_xlsx(paste0(saliva_dir,'/TAG_SALIVA_Master_File.xlsx'), sheet=9)

Sal_DHEA_interCV <- Sal_DHEA_interCV %>% 
  rename(wellID = `Well ID`) %>%
  filter(grepl('Ctrl', wellID)) %>%
  select(wellID, Mean) %>%
  mutate(wellID = as.factor(wellID),
         Mean=as.numeric(Mean)) %>%
  group_by(wellID) %>%
  summarize(meanOf_Means = mean(Mean),
            sdOf_Means = sd(Mean)) %>%
  mutate(CV = 100*(sdOf_Means/meanOf_Means))
 
Sal_TEST_interCV <- Sal_TEST_interCV %>% 
  rename(wellID = `Well ID`) %>%
  filter(grepl('CTL', wellID)) %>%
  select(wellID, Mean) %>%
  mutate(wellID = as.factor(wellID),
         Mean=as.numeric(Mean)) %>%
  group_by(wellID) %>%
  summarize(meanOf_Means = mean(Mean),
            sdOf_Means = sd(Mean)) %>%
  mutate(CV = 100*(sdOf_Means/meanOf_Means))

Sal_EST_interCV <- Sal_EST_interCV %>% 
  rename(wellID = `Well ID`) %>%
  filter(grepl('Ctr', wellID)) %>%
  select(wellID, Mean) %>%
  mutate(wellID = as.factor(wellID),
         Mean=as.numeric(Mean)) %>%
  group_by(wellID) %>%
  summarize(meanOf_Means = mean(Mean,na.rm=T),
            sdOf_Means = sd(Mean,na.rm=T)) %>%
  mutate(CV = 100*(sdOf_Means/meanOf_Means))
```
