---
title: "creating contrasts"
author: "Nandi"
date: "1 July 2018"
output: html_document
---

```{r}
packages <- c("tidyr", "stringr","data.table", "dplyr","stringi")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}
lapply(packages, library, character.only = TRUE)
```

###2x2###
```{r}
# read input file from
input_file <- '/Volumes/psych-cog/dsnlab/TAG/nonbids_data/fMRI/fx/multiconds/dsd/wave1/Summary/2x2/summary_contrasts.csv'

# directory to save output. make sure folder is created.
out_dir <- '/Volumes/StorEDGE/WORK/DSN/TAG/TAG_scripts/fMRI/fx/models/dsd/wave1/contrasts/2x2/MLmotion/'
```

#create 2x2 contrasts
```{r}
conDF <- read.csv(input_file)

contrasts <- lapply(X=as.list(conDF$sid), df=conDF, FUN=function(id, df) {
  
adf <- df %>% filter(sid==id) %>% ungroup()
run1 <- adf %>% filter(run==1) %>% select(-sid,-run) %>% mutate(affect_state=1, neutral_state=1) %>%
  select(affect_state,neutral_state,everything())
run2 <- adf %>% filter(run==2) %>% select(-sid,-run) %>% mutate(affect_state=1, neutral_state=1) %>%
  select(affect_state,neutral_state,everything())
run1<-run1[, colSums(run1 != 0) > 0]
run2<-run2[, colSums(run2 != 0) > 0]

affect_state1=rep(0, (length(run1)))
affect_state1[1]=1
neutral_state1=rep(0, (length(run1)))
neutral_state1[2]=1
affect_state2=rep(0, (length(run2)))
affect_state2[1]=1
neutral_state2=rep(0, (length(run2)))
neutral_state2[2]=1

#creat DF of contrasts
affect_state=c(affect_state1,0,0,0,0,0,affect_state2,0,0,0,0,0)
neutral_state=c(neutral_state1,0,0,0,0,0,neutral_state2,0,0,0,0,0)

df <- data.frame(affect_state,neutral_state)

contrasts <- c("affect_share","neutral_share","affect_private","neutral_private",
               "affect_share_pmod","neutral_share_pmod","affect_private_pmod","neutral_private_pmod")

for (i in 1:length(contrasts)) {
  
  conn=contrasts[i]
    
  if(conn %in% colnames(run1)) {
    colnum=which( colnames(run1)==conn )
    conn1=rep(0, (length(run1)))
    conn1[colnum]=1  
    } else {}
  
  if(conn %in% colnames(run2)) {
    colnum=which( colnames(run2)==conn )
    conn2=rep(0, (length(run2)))
    conn2[colnum]=1  
    } else {}

  if (exists("conn1") & exists("conn2")) {
    df <- df %>% 
      mutate(var = c(conn1,0,0,0,0,0,conn2,0,0,0,0,0))
    names(df)[ncol(df)]<-conn
    } else if (exists("conn1") & !exists("conn2")) {
      df <- df %>% 
        mutate(var = c(conn1,0,0,0,0,0,rep(0,length(run2)),0,0,0,0,0))
      names(df)[ncol(df)]<-conn
    } else if (!exists("conn1") & exists("conn2")) {
      df <- df %>% 
        mutate(var = c(rep(0,length(run1)),0,0,0,0,0,conn2,0,0,0,0,0))
      names(df)[ncol(df)]<-conn }
  rm(conn1)
  rm(conn2)
  }

fid = stri_pad_left(id, 3, 0)

sink(paste0(out_dir,"TAG",fid,".m",sep=""))
cat("%-----------------------------------------------------------------------
% Job saved on 01-Jul-2018 20:22:20 by cfg_util (rev $Rev: 6460 $)
% spm SPM - SPM12 (6906)
% cfg_basicio BasicIO - Unknown
%-----------------------------------------------------------------------")
cat("\n")
cat("matlabbatch{1}.spm.stats.con.spmmat = {'/Volumes/psych-cog/dsnlab/TAG/nonbids_data/fMRI/fx/models/dsd/wave1/fd0.8_noN/2x2/sub-TAG",fid,"/SPM.mat'};",sep="")
cat("\n")
for(i in 1:length(df)){
cat("matlabbatch{1}.spm.stats.con.consess{",i,"}.tcon.name = '", colnames(df)[i],"';", sep="")
cat("\n")
cat("matlabbatch{1}.spm.stats.con.consess{",i,"}.tcon.weights = [",noquote(paste0(df[,i],sep=" ")),"];",sep="")
cat("\n")
cat("matlabbatch{1}.spm.stats.con.consess{",i,"}.tcon.sessrep = 'none';",sep="")
cat("\n") }
cat("matlabbatch{1}.spm.stats.con.delete = 0;")
sink()

rows <- names(df)
df2 <- transpose(df) %>% mutate(contrast = names(df), id=id) %>% select(id, contrast, everything())
df2

})

connDF <- rbindlist(contrasts,fill=T)
```

#create summary - to be used for rx scripts
```{r}
conn_summaryDF <- connDF[!duplicated(connDF), ]
conn_summaryDF <- conn_summaryDF %>% group_by(id) %>% mutate(number = 1:n()) %>%
  select(id,contrast,number)
```

#create rx lists
```{r}
#affect share - 137 subjects - everyone present.
affect_share <- conn_summaryDF %>% filter(contrast=="affect_share")

#neutral share - 136 subjects - 1 missing
neutral_share <- conn_summaryDF %>% filter(contrast=="neutral_share")
  #missing = 179
  as.character(setdiff(affect_share$id,neutral_share$id)) 

#affect private - 127 subjects - 1 missing
affect_private <- conn_summaryDF %>% filter(contrast=="affect_private")
  #missing = "51"  "55"  "72"  "75"  "109" "200" "209" "224" "240" "250"
  as.character(setdiff(affect_share$id,affect_private$id)) 

#neutral private - 119 subjects - 1 missing
neutral_private <- conn_summaryDF %>% filter(contrast=="neutral_private")
  #missing = "34"  "35"  "42"  "51"  "55"  "68"  "71"  "72"  "75"  "109" "119" "155" "165" "200" "207" "209" "223" "250"
  as.character(setdiff(affect_share$id,neutral_private$id)) #179

###create subject lists
#share t-test
list_share_ttest <- conn_summaryDF %>% filter(contrast %in% c("affect_share","neutral_share")) %>% group_by(id) %>% summarise(N=n()) %>% filter(N == 2) %>% select(id)
write.csv(full2x2_list,'~/Desktop/subject_list_ttest.txt',row.names=F)
#
  
#2x2
list_2x2 <- conn_summaryDF %>% filter(contrast %in% c("affect_share","neutral_share","affect_private","neutral_private")) %>% group_by(id) %>% summarise(N=n()) %>% filter(N == 4) %>% select(id)
write.csv(full2x2_list,'~/Desktop/subject_list_2x2.txt',row.names=F)

#share pmod t-test
list_share_pmod_ttest <- conn_summaryDF %>% filter(contrast %in% c("affect_share_pmod","neutral_share_pmod")) %>% group_by(id) %>% summarise(N=n()) %>% filter(N == 2) %>% select(id)
write.csv(full2x2_list,'~/Desktop/subject_list_pmod_ttest.txt',row.names=F)

#pmod 2x2
list_2x2_pmod <- conn_summaryDF %>% filter(contrast %in% c("affect_share_pmod","neutral_share_pmod","affect_private_pmod","neutral_private_pmod")) %>% group_by(id) %>% summarise(N=n()) %>% filter(N == 4) %>% select(id)
write.csv(full2x2_list,'~/Desktop/subject_list_2x2.txt',row.names=F)
```

###PMOD###
```{r}
# read input file from
input_file <- '/Volumes/psych-cog/dsnlab/TAG/nonbids_data/fMRI/fx/multiconds/dsd/wave1/Summary/pmod/summary_contrasts.csv'

# directory to save output. make sure folder is created.
out_dir <- '/Volumes/StorEDGE/WORK/DSN/TAG/TAG_scripts/fMRI/fx/models/dsd/wave1/contrasts/pmod/MLmotion_FAST_RT/'
```

#create pmod contrasts
```{r}
conDF <- read.csv(input_file)

contrasts <- lapply(X=as.list(conDF$sid), df=conDF, FUN=function(id, df) {
  
adf <- df %>% filter(sid==id) %>% ungroup() 
run1 <- adf %>% filter(run==1) %>% select(-sid,-run) %>% mutate(affect_state=1, neutral_state=1, affect_decision=1, affect_value_pmod=1,neutral_decision=1, neutral_value_pmod=1) %>%
  select(affect_state,neutral_state,affect_decision,affect_value_pmod,affect_dec_pmod,neutral_decision,neutral_value_pmod,neutral_dec_pmod,missing)
run2 <- adf %>% filter(run==2) %>% select(-sid,-run) %>% mutate(affect_state=1, neutral_state=1, affect_decision=1, affect_value_pmod=1,neutral_decision=1, neutral_value_pmod=1) %>%
  select(affect_state,neutral_state,affect_decision,affect_value_pmod,affect_dec_pmod,neutral_decision,neutral_value_pmod,neutral_dec_pmod,missing)

run1<-run1[, colSums(run1 != 0) > 0]
run2<-run2[, colSums(run2 != 0) > 0]

affect_state1=rep(0, (length(run1)))
affect_state1[1]=1
neutral_state1=rep(0, (length(run1)))
neutral_state1[2]=1
affect_state2=rep(0, (length(run2)))
affect_state2[1]=1
neutral_state2=rep(0, (length(run2)))
neutral_state2[2]=1
state1=rep(0, (length(run1)))
state1[1]=1
state1[2]=1
state2=rep(0, (length(run2)))
state2[1]=1
state2[2]=1

#creat DF of contrasts
affect_state=c(affect_state1,0,0,0,0,0,affect_state2,0,0,0,0,0)
neutral_state=c(neutral_state1,0,0,0,0,0,neutral_state2,0,0,0,0,0)
state=c(state1,0,0,0,0,0,state2,0,0,0,0,0)

df <- data.frame(state,affect_state,neutral_state)

contrasts <- c("state","affect_state","neutral_state","affect_decision","neutral_decision","affect_value_pmod","neutral_value_pmod","affect_dec_pmod","neutral_dec_pmod","missing","decision_aff_neut","decision_neut_aff","valueP_aff_neut","valueP_neut_aff","decisionP_aff_neut","decisionP_neut_aff")

for (i in 4:10) {
  
  conn=contrasts[i]
    
  if(conn %in% colnames(run1)) {
    colnum=which( colnames(run1)==conn )
    conn1=rep(0, (length(run1)))
    conn1[colnum]=1  
    } else {}
  
  if(conn %in% colnames(run2)) {
    colnum=which( colnames(run2)==conn )
    conn2=rep(0, (length(run2)))
    conn2[colnum]=1  
    } else {}

  if (exists("conn1") & exists("conn2")) {
    df <- df %>% 
      mutate(var = c(conn1,0,0,0,0,0,conn2,0,0,0,0,0))
    names(df)[ncol(df)]<-conn
    } else if (exists("conn1") & !exists("conn2")) {
      df <- df %>% 
        mutate(var = c(conn1,0,0,0,0,0,rep(0,length(run2)),0,0,0,0,0))
      names(df)[ncol(df)]<-conn
    } else if (!exists("conn1") & exists("conn2")) {
      df <- df %>% 
        mutate(var = c(rep(0,length(run1)),0,0,0,0,0,conn2,0,0,0,0,0))
      names(df)[ncol(df)]<-conn }
  rm(conn1)
  rm(conn2)
  }

df <- df %>% 
  mutate(affect_neutral = (affect_state+affect_decision) - (neutral_state+neutral_decision),
         neutral_affect = (neutral_state+neutral_decision) - (affect_state+affect_decision),
         decision_aff_neut = affect_decision-neutral_decision,
         decision_neut_aff = neutral_decision-affect_decision,
         state_aff_neut = affect_state - neutral_state,
         state_neut_aff = neutral_state - affect_state,
         state_dec = (affect_state+neutral_state) - (affect_decision+neutral_decision),
         dec_state = (affect_decision+neutral_decision) - (affect_state+neutral_state),
         affect_dec_state = affect_decision - affect_state,
         neutral_dec_state = neutral_decision - neutral_state,
         affect_state_dec = affect_state - affect_decision,
         neutral_state_dec = neutral_state - neutral_decision,
         interaction1 = 1*affect_state + -1*affect_decision + -1*neutral_state + 1*neutral_decision,
         interaction2 = -1*affect_state + 1*affect_decision + 1*neutral_state + -1*neutral_decision,
         valueP_aff_neut = affect_value_pmod-neutral_value_pmod,
         valueP_neut_aff = neutral_value_pmod-affect_value_pmod)

if(("affect_dec_pmod" %in% colnames(df)) & ("neutral_dec_pmod" %in% colnames(df))) {
  
  df <- df %>% 
    mutate(decisionP_aff_neut = affect_dec_pmod-neutral_dec_pmod,
           decisionP_neut_aff = neutral_dec_pmod-affect_dec_pmod) 
} else {}

df <- df %>% select(state,affect_state,neutral_state,affect_decision,neutral_decision,affect_neutral,neutral_affect,decision_aff_neut,decision_neut_aff,state_aff_neut,state_neut_aff,state_dec,dec_state,affect_dec_state,neutral_dec_state,affect_state_dec,neutral_state_dec,interaction1,interaction2,affect_value_pmod,neutral_value_pmod,valueP_aff_neut,valueP_neut_aff,everything())

if ("missing" %in% colnames(df)) {
  df <- df %>% select(-missing,everything())
}

fid = stri_pad_left(id, 3, 0)

sink(paste0(out_dir,"TAG",fid,".m",sep=""))
cat("%-----------------------------------------------------------------------
% Job saved on 01-Jul-2018 20:22:20 by cfg_util (rev $Rev: 6460 $)
% spm SPM - SPM12 (6906)
% cfg_basicio BasicIO - Unknown
%-----------------------------------------------------------------------")
cat("\n")
cat("matlabbatch{1}.spm.stats.con.spmmat = {'/Volumes/psych-cog/dsnlab/TAG/nonbids_data/fMRI/fx/models/dsd/wave1/pmod/MLmotion_FAST_RT/sub-TAG",fid,"/SPM.mat'};",sep="")
cat("\n")
for(i in 1:length(df)){
cat("matlabbatch{1}.spm.stats.con.consess{",i,"}.tcon.name = '", colnames(df)[i],"';", sep="")
cat("\n")
cat("matlabbatch{1}.spm.stats.con.consess{",i,"}.tcon.weights = [",noquote(paste0(df[,i],sep=" ")),"];",sep="")
cat("\n")
cat("matlabbatch{1}.spm.stats.con.consess{",i,"}.tcon.sessrep = 'none';",sep="")
cat("\n") }
cat("matlabbatch{1}.spm.stats.con.delete = 1;")
sink()

rows <- names(df)
df2 <- transpose(df) %>% mutate(contrast = names(df), id=id) %>% select(id, contrast, everything())
df2

})

connDF <- rbindlist(contrasts,fill=T)
```

#create summary - to be used for rx scripts
```{r}
conn_summaryDF <- connDF[!duplicated(connDF), ]
conn_summaryDF <- conn_summaryDF %>% group_by(id) %>% mutate(number = 1:n()) %>%
  select(id,contrast,number)
```

#create rx lists
```{r}
#state/dec/shareValue - 137 subjects - everyone present.
affect_state <- conn_summaryDF %>% filter(contrast=="affect_state")
affect_decision <- conn_summaryDF %>% filter(contrast=="affect_decision")
affect_value_pmod <- conn_summaryDF %>% filter(contrast=="affect_value_pmod")

#affect_dec_pmod - 100 subjects
affect_dec_pmod <- conn_summaryDF %>% filter(contrast=="affect_dec_pmod")
  #missing 
  affect_dec_pmod_missing <- as.character(setdiff(affect_decision$id,affect_dec_pmod$id)) 

affect_dec_pmod_list <- as.character(affect_dec_pmod$id)

write.csv(affect_dec_pmod_list,'~/Desktop/subject_list_decisionP_aff.txt',row.names=F,quote=F)

#neutral_dec_pmod - 85 subjects
neutral_dec_pmod <- conn_summaryDF %>% filter(contrast=="neutral_dec_pmod")
  #missing 
  neutral_dec_pmod_missing <- as.character(setdiff(affect_decision$id,neutral_dec_pmod$id))

neutral_dec_pmod_list <- as.character(paste0(neutral_dec_pmod$id,',con_00',neutral_dec_pmod$number))

write.csv(neutral_dec_pmod_list,'~/Desktop/subject_list_decisionP_neut.txt',row.names=F,quote=F)

#decisionP_aff_neut 
decisionP_aff_neut <- conn_summaryDF %>% filter(contrast=="decisionP_aff_neut")
  #missing 
  decisionP_aff_neut_missing <- as.character(setdiff(affect_decision$id,decisionP_aff_neut$id))

decisionP_aff_neut_list <- as.character(decisionP_aff_neut$id)
  
###create pmod subject list

write.csv(decisionP_aff_neut_list,'~/Desktop/subject_list_decisionP_aff_neut.txt',row.names=F,quote=F)

#missing
missing <- conn_summaryDF %>% filter(contrast=="missing")
  #missing 
  decisionP_aff_neut_missing <- as.character(setdiff(affect_decision$id,decisionP_aff_neut$id))

decisionP_aff_neut_list <- as.character(decisionP_aff_neut$id)
