---
title: "1_createBetaseriesMulticonds"
author: "Theresa Cheng"
date: "5/12/2021"
output: html_document
---

This script reads cleaned behavioral output from DSD, formats the data, and saves subject-specific files that that can be used to create multicond files in MATLAB. These files are for betaseries analysis, meaning that each disclosure trial is modeled as a separate regressor (name, onset, and duration).

Input:
- dsd_trials_long.csv (output from 'TAG_scripts/behavior/dsd/cleanDSD_behavior.Rmd')

Output: 
- subject-specific files to be passed to '2_generateBetaseriesMulticonds.m'

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

#Load packages
packages <- c("nlme", "ggplot2", "tidyr", "stringr", "knitr","corrplot","data.table", "readxl", "gridExtra", "dplyr", "psych","kableExtra","lavaan", "stringi")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}
lapply(packages, library, character.only = TRUE)

# Set inputs/outputs
input_file <- '/Volumes/psych-cog/dsnlab/TAG/behavior/task/processed/DSD/dsd_trials_long.csv'

# directory to save output. make sure folder is created.
out_dir <- '/Volumes/psych-cog/dsnlab/TAG/nonbids_data/fMRI/fx/multiconds/dsd/betaseries/'
#out_dir <- '~/Downloads/wave1_dsd/'
curr_wave = 1
```

```{r read data}

input_df <- read.csv(input_file)
# input_df <- input_df %>% filter(wave==1)
ids <- as.vector(unique(input_df$sid))
```

```{r format multiconds}

multicondsDF <- lapply(X = ids, df = input_df, FUN = function(id, df) {

df <- input_df %>% filter(sid == id & wave == curr_wave)

# df$run <- c(rep(1, 41), rep(2, 41)) # this line is for if the runs were entered incorrectly

fid = stri_pad_left(id, 3, 0)
print(fid)

# if(nrow(df %>% filter(run==1)) > 0 & nrow(df %>% filter(run==2)) > 0) {
if(nrow(df) > 0){
  
  # clean main dataframe
  df <- df %>% mutate(subject_id = paste0('TAG',fid, 'w0', curr_wave),
                      intimate_cond = ifelse(affective == TRUE, 1,
                                             ifelse(affective == FALSE, 0, NA)),
                      disclosed = ifelse(disclosed == TRUE, 1,
                                         ifelse(disclosed == FALSE, 0, NA)),
                      share_value_cond = case_when(share.value > 0 ~ "gain",
                                                   share.value < 0 ~ "loss", 
                                                   share.value == 0 ~ "equal")) %>%
    select(subject_id, run, trial, intimate_cond, statement.onset, statement.rt.seconds, disclosed, disc.onset, target.rt.seconds, share.value, share_value_cond) %>% 
    rename(disc.rt.seconds=target.rt.seconds)

  # add ful trial information
  df$trial_onset <- df$statement.onset
  df$trial_duration <- ifelse(is.na(df$disc.rt.seconds), round(df$disc.onset - df$statement.onset + mean(df$disc.rt.seconds, na.rm = TRUE), 3), # if the participant didn't make a disclosure decision, take the difference between the onsets and add an average decision response time
                              df$disc.onset - df$statement.onset + df$disc.rt.seconds) # if the participant did make a decision, add the actual response time
 
   # create disclosure betaseries summaries
  df_disc_nod <- df %>% 
    mutate(name = paste("trial", df$trial, sep = "_"),
           onset = disc.onset,
           duration = ifelse(is.na(disc.rt.seconds), round(mean(disc.rt.seconds, na.rm = TRUE), 3), disc.rt.seconds)) #%>% 
   #select(subject_id, run, name, onset, duration, intimate_cond, disclosed, share_value_cond)
  
  df_disc_nod$run <- as.factor(df_disc_nod$run)

  # create evaluation betaseries summaries
  df_eval_nod <- df %>% 
    mutate(name = paste("trial", df$trial, sep = "_"),
           onset = statement.onset,
           eval_missed = is.na(statement.rt.seconds),
           duration = ifelse(is.na(statement.rt.seconds), round(mean(statement.rt.seconds, na.rm = TRUE), 3), statement.rt.seconds)) #%>% 
    #select(subject_id, run, name, onset, duration, eval_missed, intimate_cond, disclosed, share_value_cond) 
  
   # create full trial betaseries summaries
  df_trial_nod <- df %>% 
    mutate(name = paste("trial", df$trial, sep = "_"),
           onset = trial_onset,
           duration = trial_duration) #%>% 
   #select(subject_id, run, name, onset, duration, intimate_cond, disclosed, share_value_cond)
  
  df_trial_nod$run <- as.factor(df_trial_nod$run)
  
  # #save disclosure summaries
  # saveDisc <- df_disc_nod %>% group_by(run) %>%
  #   do({
  #     ungroup(.)
  #     write.csv(.,  file=paste0(out_dir, 'disclosure_summary/wave', curr_wave, '/TAG',fid, 'w0', curr_wave, '_DSD', .$run[[1]],'_disc_betaseries_summary.csv'),row.names = F,na = "",)
  #     data.frame()
  #     })
  # 
  # # save eval summaries
  # saveEval <- df_eval_nod %>% group_by(run) %>%
  #   do({
  #     ungroup(.)
  #     write.csv(., file = paste0(out_dir, 'eval_summary/wave', curr_wave, '/TAG',fid, 'w0', curr_wave, '_DSD', .$run[[1]],'_eval_betaseries_summary.csv'),row.names = F,na = "",)
  #     data.frame()
  #     })
  
  # save trial summaries
  saveTrials <- df_trial_nod %>% group_by(run) %>%
    do({
      ungroup(.)
      write.csv(., file = paste0(out_dir, 'full_trial_summary/wave', curr_wave, '/TAG', fid, 'w0', curr_wave, '_DSD', .$run[[1]],'_full_trial_betaseries_summary.csv'), row.names = F, na = "",)
      data.frame()
      })

} else {
  
  print(paste0('TAG', fid, 'w0', curr_wave, " raw task data do not exist for DSD"))
}

#     sid=id
#     run1 <- nrow(df %>% filter(run==1))
#     run2 <- nrow(df %>% filter(run==2))
#     check <- cbind(sid, run1, run2)
#     check <- as.data.table(check)

})
```
