---
title: "TAG_DSD_multiconds"
author: "Nandi"
date: "27 February 2018"
output: html_document
---

#Load packages and set directories
```{r, include=FALSE}
packages <- c("nlme", "ggplot2", "tidyr", "stringr", "knitr","corrplot","data.table", "readxl", "gridExtra", "dplyr", "psych","kableExtra","lavaan",    "stringi")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}
lapply(packages, library, character.only = TRUE)

in_dir <- '/Volumes/psych-cog/dsnlab/TAG/behavior/task/processed/'
file_dir <- '/Volumes/psych-cog/dsnlab/TAG/behavior/task/processed/subjects/'
out_dir <- '/Volumes/psych-cog/dsnlab/TAG/nonbids_data/fmri/fx/multiconds/dsd/wave1/Summary/'
```

#Read data
```{r}
out_df <- read.csv(paste0(in_dir,'dsd_trials_long.csv'))
out_df <- out_df %>% filter(wave==1)
ids <- as.vector(unique(out_df$sid))
```

#Format one - now deprecated (4 statement and 12 disclosure conditions):
```{r}
multiconds <- lapply(X=ids, df=out_df, FUN=function(id, df) {
  
  df <- df %>% filter(sid==id)
  
  if(nrow(df %>% filter(run==1)) == 41 & nrow(df %>% filter(run==2)) == 41) {
  
    df <- df %>% mutate(statement.condition = ifelse(affective == TRUE & statement.choice == 1, 1,
                                          ifelse(affective == TRUE & statement.choice == 2, 2,
                                                  ifelse(affective == FALSE & statement.choice == 1, 3,
                                                          ifelse(affective == FALSE & statement.choice == 2, 4, NA)))),
                      disc.condition = ifelse(affective == TRUE & disclosed == 1 & share.value < 0, 1,
                                          ifelse(affective == TRUE & disclosed == 1 & share.value > 0, 2,
                                                 ifelse(affective == TRUE & disclosed == 1 & share.value == 0, 3,
                                                        ifelse(affective == TRUE & disclosed == 0 & share.value < 0, 4,
                                                               ifelse(affective == TRUE & disclosed == 0 & share.value > 0, 5,
                                                                      ifelse(affective == TRUE & disclosed == 0 & share.value == 0, 6, 
                                                                             ifelse(affective == FALSE & disclosed == 1 & share.value < 0, 7,
                                                                                    ifelse(affective == FALSE & disclosed == 1 & share.value > 0, 8,
                                                                                           ifelse(affective == FALSE & disclosed == 1 & share.value == 0, 9,
                                                                                                  ifelse(affective == FALSE & disclosed == 0 & share.value < 0, 10,
                                                                                                         ifelse(affective == FALSE & disclosed == 0 & share.value > 0, 11,
                                                                                                                ifelse(affective == FALSE & disclosed == 0 & share.value == 0, 12, NA))))))))))))) %>%
    select(sid,run,trial,statement.condition,statement.onset,disc.condition,disc.onset)

df_long <- df %>% 
  gather(v, value, statement.condition:disc.onset) %>% 
  separate(v, c("task", "v2")) %>% 
  arrange(sid) %>% 
  spread(v2, value) %>%
  arrange(run,trial,desc(task)) %>%
  mutate(name = ifelse(task == "disc" & condition == 1, 5,
                       ifelse(task == "disc" & condition == 2, 6,
                              ifelse(task == "disc" & condition == 3, 7,
                                     ifelse(task == "disc" & condition == 4, 8,
                                            ifelse(task == "disc" & condition == 5, 9,
                                                   ifelse(task == "disc" & condition == 6, 10,
                                                          ifelse(task == "disc" & condition == 7, 11,
                                                                 ifelse(task == "disc" & condition == 8, 12,
                                                                        ifelse(task == "disc" & condition == 9, 13,
                                                                               ifelse(task == "disc" & condition == 10, 14,
                                                                                      ifelse(task == "disc" & condition == 11, 15,
                                                                                             ifelse(task == "disc" & condition == 12, 16,
                                                                                                    ifelse(task == "statement" & is.na(condition), 17,
                                                                                                           ifelse(task == "disc" & is.na(condition), 18, condition))))))))))))))) %>%
  mutate(duration = 0) %>%
  select(sid,run,name,onset,duration)

#df_long1 <- df_long %>% filter(run==1)
#df_long2 <- df_long %>% filter(run==2)
#write.csv(df_long1,file=paste0(out_dir,id,'_run1_summary.csv'),row.names=F) 
#write.csv(df_long2,file=paste0(out_dir,id,'_run2_summary.csv'),row.names=F) 

} else {
  
  sid=id
  run1 <- nrow(df %>% filter(run==1))
  run2 <- nrow(df %>% filter(run==2))
  check <- cbind(sid, run1, run2)
  check <- as.data.table(check)

}})

check_ids <- rbindlist(multiconds, fill=T)
multiconds <- check_ids %>% select(sid,run,name,onset,duration) %>% filter(!is.na(name)) %>%
  mutate(name=as.factor(name),run=as.factor(run))
check_ids <- check_ids %>% select(sid,run1,run2) %>% filter(!is.na(run1))

#check for subjects with missing events
summary_byRun <- multiconds %>% group_by(sid,run,name) %>% summarise(N = n()) %>% filter(name %in% c(5,6,7,8,9,10,11,12,13,14,15,16)) %>% group_by(run,name) %>% summarise(N = n(),missing=151-n())

levels(summary_byRun$name) <- c("Neutral_True","Neutral_False","Affect_True","Affect_False","Affect_Share_Loss","Affect_Share_Gain","Affect_Share_Nodiff","Affect_Private_Loss","Affect_Private_Gain","Affect_Private_Nodiff","Neutral_Share_Loss","Neutral_Share_Gain","Neutral_Share_Nodiff","Neutral_Private_Loss","Neutral_Private_Gain","Neutral_Private_Nodiff","Statement_Missing")
levels(summary_byRun$run) <- c("Run1","Run2")

summary_acrossRun <- multiconds %>% group_by(sid,name) %>% summarise(N = n()) %>% filter(name %in% c(5,6,7,8,9,10,11,12,13,14,15,16)) %>% group_by(name) %>% summarise(N = n(),missing=151-n())

levels(summary_acrossRun$name) <- c("Neutral_True","Neutral_False","Affect_True","Affect_False","Affect_Share_Loss","Affect_Share_Gain","Affect_Share_Nodiff","Affect_Private_Loss","Affect_Private_Gain","Affect_Private_Nodiff","Neutral_Share_Loss","Neutral_Share_Gain","Neutral_Share_Nodiff","Neutral_Private_Loss","Neutral_Private_Gain","Neutral_Private_Nodiff","Statement_Missing")

#number of missing conditions in subjects (filtering out those without any missing conditions)
summary_bySubj <- multiconds %>% group_by(sid,name) %>% summarise(N = n()) %>% filter(name %in% c(5,6,7,8,9,10,11,12,13,14,15,16)) %>% group_by(sid) %>% summarise(N = (12 - n())) %>% filter(!N==0) 

comp_IDS <- unique(multiconds$sid) 

#deal with collapsing across runs, or seperate input files for each run

missing <- ggplot(summary_byRun, aes(x = name, y = missing)) + geom_bar(stat = "identity") + facet_wrap(~run, ncol=1) + 
  theme(axis.line = element_line(colour = "black"),
        #panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x=element_blank())

missing2 <- ggplot(summary_acrossRun, aes(x = name, y = missing)) + geom_bar(stat = "identity") +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x=element_blank())

ggsave(filename='/Volumes/StorEDGE/WORK/DSN/TAG/DSD/missing_12conds.png', plot=missing, width = 6, height = 4.5)
ggsave(filename='/Volumes/StorEDGE/WORK/DSN/TAG/DSD/missing_12conds_acrossRuns.png', plot=missing2, width = 6, height = 4.5)

multiconds2 <- multiconds %>% filter(!name %in% c(1,2,3,4,17,18)) %>% 
  group_by(sid,run,name) %>%
  summarise(N=n()) %>%
  mutate(N=ifelse(name %in% c(5,6,8,9,11,12,14,15), 100*(N/7),
                  ifelse(name %in% c(7,10), 100*(N/7),
                         ifelse(name %in% c(13,16), 100*(N/6),NA)))) %>%
  ungroup() %>%
  mutate(sid=as.factor(sid),
         name=as.factor(name),
         run=as.factor(run)) %>%
  arrange(run,name,N)

indPlot <- ggplot(multiconds2, aes(x = sid, y = N, fill = name)) + geom_bar(stat = "identity") + facet_wrap(~run, ncol=1)

percDisc <- ggplot(multiconds2, aes(N)) + 
  geom_histogram(breaks=seq(0, 100, by = 20), 
                 col="grey") + 
  facet_grid( run ~ name) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())

```

#format two (2 statement and 4 disclosure conditions, with share.value as a pmod):
```{r}
multicondsDF <- lapply(X=ids, df=out_df, FUN=function(id, df) {
  
  df <- df %>% filter(sid==id)
  
  if(nrow(df %>% filter(run==1)) > 0 & nrow(df %>% filter(run==2)) > 0) {
  
    df <- df %>% mutate(statement.condition = ifelse(affective == FALSE, 1,
                                                     ifelse(affective == TRUE, 2, NA)),
                        disc.condition = ifelse(affective == FALSE & disclosed == FALSE, 1,
                                                ifelse(affective == FALSE & disclosed == TRUE, 2,
                                                       ifelse(affective == TRUE & disclosed == FALSE, 3,
                                                              ifelse(affective == TRUE & disclosed == TRUE, 4, NA))))) %>%
      select(sid,run,trial,statement.condition,statement.onset,disc.condition,disc.onset,share.value)

df_long <- df %>% 
  gather(v, value, statement.condition:disc.onset) %>% 
  separate(v, c("task", "v2")) %>% 
  arrange(sid) %>% 
  spread(v2, value) %>%
  arrange(run,trial,desc(task)) %>%
  mutate(name = ifelse(task == "disc" & condition == 1, 3,
                       ifelse(task == "disc" & condition == 2, 4,
                              ifelse(task == "disc" & condition == 3, 5,
                                     ifelse(task == "disc" & condition == 4, 6, condition))))) %>%
  mutate(name = ifelse(is.na(name), 7, name)) %>%
  group_by(run) %>%
  mutate(duration = lead(onset) - onset) %>%
  mutate(pmod = ifelse(task=="statement",NA,share.value)) %>%
  mutate(pmod = ifelse(pmod < 0, -1,
                       ifelse(pmod > 0, 1,
                              ifelse(pmod == 0, 0, NA)))) %>%
  select(sid,run,name,onset,duration,pmod) %>%
  mutate(duration = ifelse(is.na(duration),3,duration))

df_long

} else {
  
  sid=id
  run1 <- nrow(df %>% filter(run==1))
  run2 <- nrow(df %>% filter(run==2))
  check <- cbind(sid, run1, run2)
  check <- as.data.table(check) }
})

multicondsDF <- rbindlist(multicondsDF, fill=T)
multiconds <- multicondsDF %>% select(sid,run,name,onset,duration,pmod)

#IDs to check and run manually
check_ids <- multicondsDF %>% select(sid,run1,run2) %>% filter(!is.na(run1))

#complete subject list
comp_IDS <- unique(multiconds$sid) 

#check for subjects with missing events
summary_byRun <- multiconds %>% group_by(sid,run,name) %>% summarise(N = n()) %>% filter(name %in% c(3,4,5,6)) %>% group_by(run,name) %>% summarise(N = n())

summary_acrossRun <- multiconds %>% group_by(sid,name) %>% summarise(N = n()) %>% filter(name %in% c(3,4,5,6)) %>% group_by(name) %>% summarise(N = n())

#number of missing conditions in subjects (filtering out those without any missing conditions)
summary_byRun_bySubj <- multiconds %>% group_by(sid,run,name) %>% summarise(N = n()) %>% filter(name %in% c(3,4,5,6)) %>% group_by(sid,run) %>% summarise(N = (4 - n())) %>% filter(!N==0) 

summary_acrossRun_bySubj <- multiconds %>% group_by(sid,name) %>% summarise(N = n()) %>% filter(name %in% c(3,4,5,6)) %>% group_by(sid) %>% summarise(N = (4 - n())) %>% filter(!N==0) 

#distribution of trials across neutral vs. affective conditions by each share.value
summary_affect_byShareValue <- out_df %>%
  filter(sid==3 & wave ==1 & run ==1) %>%
  group_by(affective, share.value) %>%
  summarise(N=n())

#check for subjects who do not have missing events by each share.value (with 3 levels)
summary_acrossRun_byShareValue <- multiconds %>% 
  mutate(share.value = pmod) %>%
  mutate(name=as.factor(name)) %>%
  group_by(sid,run,name,share.value) %>% summarise(N = n()) %>% 
  filter(name %in% c(4,6)) %>% 
  group_by(name,share.value) %>%
  summarise(N = 100*(n()/312))

#check for subjects with more than 4 events for each share.value
summary_acrossRun_byShareValue_over3 <- multiconds %>% 
  mutate(share.value = pmod) %>%
  mutate(name=as.factor(name)) %>%
  group_by(sid,name,share.value) %>% summarise(N = n()) %>% 
  filter(name %in% c(4,6)) %>% 
  filter(N > 3) %>%
  group_by(name,share.value) %>%
  summarise(N = 100*(n()/156))

#of subjects with missing events across the share.values, most seem to have at least trials for two of the share.values: 
summary_acrossRun_byShareValue_v2 <- multiconds %>% 
  mutate(share.value = pmod) %>%
  mutate(name=as.factor(name)) %>%
  group_by(sid,name,share.value) %>% summarise(N = n()) %>% 
  filter(name %in% c(4,6)) %>% 
  group_by(sid,name) %>%
  summarise(N =n()) %>%
  filter(N < 3) %>%
  group_by(name,N) %>%
  summarise(num = n()) 

#plots
multicondsPlot <- multiconds %>% filter(!name==1) %>% filter(!name==2) %>%filter(!name==7) %>%
  group_by(sid,run,name) %>%
  summarise(N=n()) %>%
  mutate(N=ifelse(name %in% c(3,4), 100*(N/20),
                  ifelse(name %in% c(5,6), 100*(N/21),NA))) %>%
  ungroup() %>%
  mutate(sid=as.factor(sid),
         name=as.factor(name),
         run=as.factor(run)) %>%
  arrange(run,name,N)

levels(multicondsPlot$name) <- c("Neutral_Private", "Neutral_Share"
                              ,"Affect_Private", "Affect_Share")
levels(multicondsPlot$run) <- c("Run1","Run2")

indPlot <- ggplot(multicondsPlot, aes(x = sid, y = N, fill = name)) + geom_bar(stat = "identity") + facet_wrap(~run, ncol=1)

percDisc <- ggplot(multicondsPlot, aes(N)) + 
  geom_histogram(breaks=seq(0, 100, by = 20), 
                 col="grey") + 
  facet_grid( run ~ name) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())

levels(summary_acrossRun_byShareValue$name) <- c("Neutral_Statement","Affect_Statement",
                                                 "Neutral_Private", "Neutral_Share",
                                                 "Affect_Private", "Affect_Share", "Missing")
levels(summary_acrossRun_byShareValue_over3$name) <- c("Neutral_Statement","Affect_Statement",
                                                       "Neutral_Private", "Neutral_Share",
                                                       "Affect_Private", "Affect_Share","Missing")

shareValuePlot_1 <- ggplot(summary_acrossRun_byShareValue, aes(x=share.value, y=N)) + 
  geom_bar(stat = "identity") + facet_wrap(~name, ncol=2)
shareValuePlot_2 <- ggplot(summary_acrossRun_byShareValue_over3, aes(x=share.value, y=N)) + 
  geom_bar(stat = "identity") + facet_wrap(~name, ncol=2)

ggsave(filename='/Volumes/StorEDGE/WORK/DSN/TAG/DSD/indPlot.png', plot=indPlot, width = 9, height = 4.5)
ggsave(filename='/Volumes/StorEDGE/WORK/DSN/TAG/DSD/perDisclosure.png', plot=percDisc, width = 9, height = 3.5)
ggsave(filename='/Volumes/StorEDGE/WORK/DSN/TAG/DSD/shareValuePlot_1.png', plot=shareValuePlot_1, width = 5, height = 3.5)
ggsave(filename='/Volumes/StorEDGE/WORK/DSN/TAG/DSD/shareValuePlot_2.png', plot=shareValuePlot_2, width = 5, height = 3.5)
```


```{r}
#import dsd overview doc
dsd_overview <- read.csv('~/Desktop/dsd_overview.csv',header=T)
dsd_overview <- dsd_overview %>% 
  mutate(output_files = ifelse(SID %in% comp_IDS, 1, 0))

compIDS <- dsd_overview %>% #189
  filter(Withdrawn_W1==0) %>% #174
  filter(!check_mri_completed.2.partial.1.full.0.none.==0) %>% #164
  filter(dsd_completed == 2) %>% 
  filter(is.na(technical_missing)) %>%
  filter(is.na(participant_error))
  
multiconds <- multiconds %>% filter(sid %in% compIDS$SID)

#check for subjects with missing events
summary_byRun <- multiconds %>% group_by(sid,run,name) %>% summarise(N = n()) %>% filter(name %in% c(3,4,5,6)) %>% group_by(run,name) %>% summarise(N = n()) %>%
  mutate(missingN = nrow(compIDS) - N) %>%
  mutate(missingPerc = 100*(missingN/nrow(compIDS)))

summary_acrossRun <- multiconds %>% group_by(sid,name) %>% summarise(N = n()) %>% filter(name %in% c(3,4,5,6)) %>% group_by(name) %>% summarise(N = n()) %>%
    mutate(missingN = nrow(compIDS) - N) %>%
  mutate(missingPerc = 100*(missingN/nrow(compIDS)))

#number of missing conditions in subjects (filtering out those without any missing conditions)
summary_byRun_bySubj <- multiconds %>% group_by(sid,run,name) %>% summarise(N = n()) %>% filter(name %in% c(3,4,5,6)) %>% group_by(sid,run) %>% summarise(N = (4 - n())) %>% filter(!N==0) 

summary_acrossRun_bySubj <- multiconds %>% group_by(sid,name) %>% summarise(N = n()) %>% filter(name %in% c(3,4,5,6)) %>% group_by(sid) %>% summarise(N = (4 - n())) %>% filter(!N==0) 

#distribution of trials across neutral vs. affective conditions by each share.value
summary_affect_byShareValue <- out_df %>%
  filter(sid==3 & wave ==1 & run ==1) %>%
  group_by(affective, share.value) %>%
  summarise(N=n())

multicondsPlot <- multiconds %>% filter(!name==1) %>% filter(!name==2) %>% filter(!name==7) %>% 
  group_by(sid,run,name) %>%
  summarise(N=n()) %>%
  mutate(N=ifelse(name %in% c(3,4), 100*(N/20),
                  ifelse(name %in% c(5,6), 100*(N/21),NA))) %>%
  ungroup() %>%
  mutate(sid=as.factor(sid),
         name=as.factor(name),
         run=as.factor(run)) %>%
  arrange(run,name,N)

levels(multicondsPlot$name) <- c("Neutral_Private", "Neutral_Share"
                              ,"Affect_Private", "Affect_Share")
levels(multicondsPlot$run) <- c("Run1","Run2")

indPlot <- ggplot(multicondsPlot, aes(x = sid, y = N, fill = name)) + geom_bar(stat = "identity") + facet_wrap(~run, ncol=1)

percDisc <- ggplot(multicondsPlot, aes(N)) + 
  geom_histogram(breaks=seq(0, 100, by = 20), 
                 col="grey") + 
  facet_grid( run ~ name) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())

ggsave(filename='/Volumes/StorEDGE/WORK/DSN/TAG/DSD/indPlot.png', plot=indPlot, width = 9, height = 4.5)
ggsave(filename='/Volumes/StorEDGE/WORK/DSN/TAG/DSD/perDisclosure.png', plot=percDisc, width = 9, height = 3.5)
